---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---


#Libraries
```{r message=FALSE}
  library(tidyverse)
library(magrittr)
  library(OrgMassSpecR)
  library(tidymodels)
  tidymodels_prefer()
  library(ggpubr)
  options(tibble.width = Inf)
  library(MSnbase)
  library(peakPantheR)
  conflicted::conflicts_prefer(dplyr::first)
  library(limma)
  library(crmn)
```

#Vectors
```{r}
folder_alphapeptdeep <- "C:/Users/admin/alphapeptdeep/apd_110/prm/"
folder_raw <- "F:/2025_PRM_REVISION/"
folder_result <- "F:/2025_PRM_REVISION/results/"
folder_fragpipe <- "C:/FragPipe/FragPipe-23.1/"
fragpipe<- paste0(folder_fragpipe,"bin/fragpipe.bat")
project_name <- "revision_250826" ##edit!
folder_alphapeptdeep_model <- paste0(folder_alphapeptdeep,"models/")
python <- "C:/Users/admin/anaconda3/envs/apd_110/python.exe"
```

#PRTC Table >> table_prtc
objects for PRTCs: sequences, modifications, masses
```{r}
tibble(
  sequence = c(
    "SSAAPPPPPR",
    "GISNEGQNASIK",
    "HVLTSIGEK",
    "DIPVPKPK",
    "IGDYAGIK",
    "TASEFDSAIAQDK",
    "SAAGAFGPELSR",
    "ELGQSGVDTYLQTK",
    "GLILVGGYGTR",
    "GILFVGSGVSGGEEGAR",
    "SFANQPLEVVYSK",
    "LTILEELR",
    "NGFILDGFPR",
    "ELASGLSFPVGFK",
    "LSSEAPALFQFDLK"
  ),
  sequence2 = c(
    "SSAAPPPPPJ",
    "GISNEGQNASIB",
    "HVLTSIGEB",
    "DIPVPKPB",
    "IGDYAGIB",
    "TASEFDSAIAQDB",
    "SAAGAFGPELSJ",
    "ELGQSGVDTYLQTB",
    "GLILVGGYGTJ",
    "GILFVGSGVSGGEEGAJ",
    "SFANQPLEVVYSB",
    "LTILEELJ",
    "NGFILDGFPJ",
    "ELASGLSFPVGFB",
    "LSSEAPALFQFDLB"
  ),
  charge = rep(2L,15),
  gene_position=c(
    "PRTC01",
    "PRTC02",
    "PRTC03",
    "PRTC04",
    "PRTC05",
    "PRTC06",
    "PRTC07",
    "PRTC08",
    "PRTC09",
    "PRTC10",
    "PRTC11",
    "PRTC12",
    "PRTC13",
    "PRTC14",
    "PRTC15"
  ),
  mods= c(
    "Label:13C(6)15N(4)@R",
    "Label:13C(6)15N(2)@K",
    "Label:13C(6)15N(2)@K",
    "Label:13C(6)15N(2)@K",
    "Label:13C(6)15N(2)@K",
    "Label:13C(6)15N(2)@K",
    "Label:13C(6)15N(4)@R",
    "Label:13C(6)15N(2)@K",
    "Label:13C(6)15N(4)@R",
    "Label:13C(6)15N(4)@R",
    "Label:13C(6)15N(2)@K",
    "Label:13C(6)15N(4)@R",
    "Label:13C(6)15N(4)@R",
    "Label:13C(6)15N(2)@K",
    "Label:13C(6)15N(2)@K"
  ),
  mod_sites = as.character(c(
    10L,
    12L,
    9L,
    8L,
    8L,
    13L,
    12L,
    14L,
    11L,
    17L,
    13L,
    8L,
    10L,
    13L,
    14L
  )),
  index = c(
    2001:2015
  ),
  cleavage_type = c(
    rep("PRTC",15)
  ),
  mz = c(
    493.7683,
    613.3167,
    496.2867,
    451.2834,
    422.7364,
    695.8323,
    586.8002,
    773.8955,
    558.3259,
    801.4114,
    745.3924,
    498.8018,
    573.3024,
    680.3735,
    787.4212
  )
) -> table_prtc
```

#PRM Targets >> Manual
The function of this code is to allow for targets to be added by hand.
```{r}
read_tsv(
    "./export/natcomm_revision/table_arginylome_revision_targets_filterd.tsv"
  ) -> table_arginylome_revision
```

#PRM Targets
code for Nt-arg targets and string manipulations: digestion for tryptic peptides, length, charge 
```{r}

# read_tsv(
#   "arginylome_validation_matrix3_sequence_distinct_trinity_240401.tsv"
# )->table_arginylome
# 
# table_arginylome %>% write_tsv(
#   "./export/natcomm_revision/table_arginylome_natcomm_revision.tsv"
# )

# readxl::read_xlsx(
#   "./export/natcomm_revision/revision_targets.xlsx"
# ) -> table_arginylome_revision


table_arginylome_revision %>% 
    select(
      prot_pos_master,gene_position,cleavage_type,source_cleavage,gene,MOCK,MG132,MGTG,sequence,Sequence,protease,loc
    ) %>% 
    mutate(
      trypticpep = map2(
        sequence,
        Sequence,
        \(x,y) digest2(x) %>% bind_rows(digest2(y))
      )
    ) %>% 
    unnest(trypticpep) %>% 
    filter(
      start ==1
    ) %>% 
    filter(
      stop >5
    ) %>% 
    mutate(
      charge_predict = Peptides::charge(peptide,pH = 2,pKscale = "EMBOSS"),
      charge_predict_round =round(charge_predict)
    ) %>% 
    mutate(
      target_type = if_else(str_detect(peptide,"^R"),"arg","free"),
      target_index = paste0(gene_position,"_",target_type)
    ) %>% 
  distinct(
    target_index,.keep_all = TRUE
  )-> table_arginylome_revision_targets

table_arginylome_revision_targets %>% 
  select(
    -sequence
  ) %>% 
  rename(
    sequence = peptide
  ) %>% 
  pivot_longer(
    mz1:mz5,
    names_to = "charge_calc",
    values_to = "mz"
  ) %>% 
  mutate(
    charge = as.integer(str_extract(charge_calc,"[0-9]$")),
    matched_w_predictedcharge = if_else(abs(charge_predict_round-charge)<2,TRUE,FALSE)
  ) %>% 
  filter(
    matched_w_predictedcharge == TRUE &
    charge >1
  ) -> table_arginylome_revision_targets_filterd

table_arginylome_revision_targets_filterd %>% 
  write_tsv(
    "./export/natcomm_revision/table_arginylome_revision_targets_filterd_original.tsv"
  )
```

#PRM Targets
adding prtc info into the target tibble.
```{r}
table_arginylome_revision_targets_filterd %>% 
  mutate(
    index = 1:nrow(.)
  ) %>% 
  # filter(
  #   charge == 2
  # ) %>% 
  # filter(
  #   mz > 300 & mz < 1200
  # ) %>% 
  # filter(
  #   !is.na(cleavage_type)
  # )
  # select(
  #   sequence,index
  # ) %>% 
  mutate(
    cys = map(
      sequence,
      \(x) str_locate_all(x,"C") %>% deframe() %>% as_tibble
    )
  ) %>% 
  mutate(
    mod_sites = map_chr(
      cys,
      \(x) pull(x, start) %>% paste0(collapse =";")
    ),
    mods = str_replace_all(
      mod_sites,"[0-9]+","Carbamidomethyl@C"
    )
  ) %>% 
  select(-cys) -> table_arginylome_revision_targets_filterd
  
  ##ADD PRTC info
table_arginylome_revision_targets_filterd %>% 
  bind_rows(
    tibble(
      sequence = c(
        "SSAAPPPPPR",
        "GISNEGQNASIK",
        "HVLTSIGEK",
        "DIPVPKPK",
        "IGDYAGIK",
        "TASEFDSAIAQDK",
        "SAAGAFGPELSR",
        "ELGQSGVDTYLQTK",
        "GLILVGGYGTR",
        "GILFVGSGVSGGEEGAR",
        "SFANQPLEVVYSK",
        "LTILEELR",
        "NGFILDGFPR",
        "ELASGLSFPVGFK",
        "LSSEAPALFQFDLK"
      ),
      charge = rep(2L,15),
      gene_position=c(
        "PRTC01",
        "PRTC02",
        "PRTC03",
        "PRTC04",
        "PRTC05",
        "PRTC06",
        "PRTC07",
        "PRTC08",
        "PRTC09",
        "PRTC10",
        "PRTC11",
        "PRTC12",
        "PRTC13",
        "PRTC14",
        "PRTC15"
      ),
      index = c(
        2001:2015
      ),
      cleavage_type = c(
        rep("PRTC",15)
      ),
      mz = c(
        493.7683,
        613.3167,
        496.2867,
        451.2834,
        422.7364,
        695.8323,
        586.8002,
        773.8955,
        558.3259,
        801.4114,
        745.3924,
        498.8018,
        573.3024,
        680.3735,
        787.4212
      )
    )
  ) -> table_arginylome_revision_targets_filterd

table_arginylome_revision_targets_filterd %>% 
  write_tsv(
    paste0(folder_alphapeptdeep,"input/rt_testing.tsv")
  )
  
```



#SEARCH w/ FRAGPIPE
database searching with fragpipe search program.

## converting raw to mzml
```{r}

system(
  paste0(
    'powershell -Command \"',
    "cd ",
    folder_raw,
    "; ",
    "msconvert",
    " ",
    "*.raw",
    " ",
    "-c msconvert_config.txt"
  ),
  wait =TRUE,
  invisible = FALSE
)

```

## Fragpipe run
```{r}

files_raw <- dir(
  path = folder_raw,
  pattern = "mzML"
)

dir.create(
  paste0(folder_raw,"search/",project_name,"/")
)

#MANIFEST
tibble(
  file_name = files_raw,
  experiment = NA,
  repliceate = NA,
  type = "DDA"
) %>% 
  write_tsv(
    paste0(folder_raw,"search/",project_name,"/","default.fp-manifest"),
    na= "",
    col_names = FALSE
  )

#COPYING WORKFLOW
system(
  paste0(
    'powershell -Command \"',
    "cd ",
    folder_raw,
    "; ",
    "Copy-Item ",
    "-path ",
    paste0(folder_fragpipe,"workflows/ARGPRM_PRTC.workflow"),
    " ",
    "-destination ",
    ".\\search\\",project_name
  )
)

#MOVE SPECTRAL FILES
system(
  paste0(
    'powershell -Command \"',
    "cd ",
    folder_raw,
    "; ",
    "Move-Item ",
    "-path ",
    ".\\*.mzML",
    " ",
    "-destination ",
    ".\\search\\",project_name
  )
)

#SEARCH!
system(
  paste0(
    'powershell -Command \"',
    "cd ",
    paste0(folder_raw,"search/",project_name,"/"),
    "; ",
    fragpipe,
    " ",
    "--headless ",
    "--workflow ",
    "ARGPRM_PRTC.workflow",
    " ",
    "--manifest ",
    "default.fp-manifest",
    " ",
    "--workdir ",
    paste0(folder_raw,"search/",project_name,"/")
  ),
  wait =TRUE,
  invisible = FALSE
)

system(
  paste0(
    'powershell -Command \"',
    "cd ",
    folder_raw,
    "; ",
    "Move-Item ",
    "-path ",
    ".\\*.raw",
    " ",
    "-destination ",
    paste0(folder_raw,"search/",project_name,"/")
  )
)

```

## QC data >> RT training data
```{r}
#header: sequence, charge, spec_idx, irt, mods, mod_sites, nAA, rt_norm
read_tsv(
  paste0(folder_raw,"search/",project_name,"/","ion.tsv")
) -> result_qc_ion
  
result_qc_ion %>% #colnames()
  mutate(
    index = 1:nrow(.)
  ) %>% 
  rename(
    rt = `Apex Retention Time` ## this is target col
  ) %>% 
  select(
    `Peptide Sequence`,Charge,`Peptide Length`,index,rt, `Assigned Modifications`
  ) %>% 
  drop_na(
    rt
  ) %>% 
  rename(
    mods_original = `Assigned Modifications`,
    sequence = `Peptide Sequence`,
    charge = Charge,
    nAA =  `Peptide Length`
  ) %>% 
  separate_longer_delim(
    mods_original, ","
  ) %>% #distinct(mods_original) %>% print(n=Inf)
  mutate(
    mods_res = case_when(
      str_detect(mods_original,"N\\-")~"Any N-term",
      .default = str_extract(mods_original,"(?<=[0-9])[AC-IK-Z]")
    ),
    mods_name = case_when(
      str_extract(mods_original,"(?<=\\()[0-9\\.]+(?=\\))") == "15.9949" ~ "Oxidation",
      str_extract(mods_original,"(?<=\\()[0-9\\.]+(?=\\))") == "57.0215" ~ "Carbamidomethyl",
      str_extract(mods_original,"(?<=\\()[0-9\\.]+(?=\\))") == "42.0106" ~ "Acetyl",
      .default = NA
    )
  ) %>% #drop_na(mods_original) %>%  view()
  mutate(
    mods = if_else(!is.na(mods_res),paste0(mods_name,"@",mods_res),NA),
    mod_sites = case_when(
      str_detect(mods_original,"N\\-")~0,
      .default = as.integer(str_extract(mods_original,"^[0-9]+"))
    )
  ) %>% 
  arrange(
    index,mod_sites
  ) %>% 
  nest(
    mod = mods_original:mod_sites
  ) %>% 
  mutate(
    mods = map_chr(
      mod, \(x) paste0(pull(x,mods),collapse = ";")
    ),
    mod_sites = map_chr(
      mod, \(x) paste0(pull(x,mod_sites),collapse = ";")
    )
  ) -> table_qc_training
  
#header: sequence, charge, spec_idx, irt, mods, mod_sites, nAA, rt_norm
#6 min system rt
#gradient start 10 to 65 >> 16 to 71
table_qc_training %>% 
  rename(
    irt = rt
  ) %>% 
  mutate(
    irt = irt/60,
    mods = na_if(mods, "NA"),
    mod_sites = na_if(mod_sites, "NA"),
    rt_norm = (irt-rt_start)/rt_duration
  ) %>% 
  filter(
    rt_norm >= 0
  )-> table_qc_training

table_qc_training %>% 
  mutate(
    sequence = str_replace(sequence,"B$","K"),
    sequence = str_replace(sequence,"J$","R")
  ) -> table_qc_training

table_qc_training %>% 
  select(
    sequence, charge, index, irt, mods, mod_sites,nAA,rt_norm
  ) %>% 
  filter(
    !(sequence %in% table_prtc$sequence) 
  )-> table_qc_training_export

table_qc_training %>% 
  select(
    sequence, charge, index, irt, mods, mod_sites,nAA,rt_norm
  )-> table_qc_training_export2

table_qc_training_export %T>% 
  write_tsv(
    paste0("./export/natcomm_revision/",project_name,"_training_rt.tsv")
  ) %>% 
  write_tsv(
    paste0(folder_alphapeptdeep,"input/training_rt.tsv")
  )

table_qc_training_export2 %T>% 
  write_tsv(
    paste0("./export/natcomm_revision/",project_name,"_training_rt_for_test.tsv")
  ) %>% 
  write_tsv(
    paste0(folder_alphapeptdeep,"input/training_rt_for_test.tsv")
  )

table_qc_training %>% 
  ggplot(
    aes(x=irt)
  )+
  geom_histogram(
    binwidth = 2,
    color = "black",
    fill = "#E41A1C"
  )+
  theme_bw()
ggsave(
  paste0("./figures/natcomm_revision/rt_training_histogram_",project_name,".png"),width=10,height=10,dpi = 600,units="cm"
)

```


# TRAINING + INCLUSION LIST
## APD training
```{r}
dir.create(
  paste0(folder_alphapeptdeep,"output/",project_name)
)
dir.create(
  paste0(folder_alphapeptdeep_model,project_name)
)

c(
  "import pandas as pd",
  paste0(
    "precursor_df = pd.read_table('",
    paste0(folder_alphapeptdeep,"input/training_rt.tsv"),
    "',dtype={'mod_sites':'string'})"
  ),
  "precursor_df = precursor_df.fillna('')",
  "precursor_df['mod_sites'] = precursor_df['mod_sites'].astype('string')",
  "from peptdeep.pretrained_models import *",
  "model_mgr_rt = ModelManager(mask_modloss=False)",
  paste0(
    "model_mgr_rt.load_external_models(rt_model_file ='",
    folder_alphapeptdeep_model,
    "generic_v3/rt.pth",
    "')"
  ),
  "model_mgr_rt.epoch_to_train_rt_ccs = 100",
  "model_mgr_rt.train_rt_model(psm_df=precursor_df)",
  "output_training_rt_transfer=model_mgr_rt.predict_rt(precursor_df)",
  paste0(
    "output_training_rt_transfer.to_csv('",
    folder_alphapeptdeep,"output/",project_name,"/rt_training_output.csv",
    "')"
  ),
  paste0(
    "model_mgr_rt.save_models('",
    folder_alphapeptdeep_model,project_name,"/')"
  ),
  paste0(
    "precursor_df = pd.read_table('",
    paste0(folder_alphapeptdeep,"input/rt_testing.tsv"),
    "',dtype={'mod_sites':'string'})"
  ),
  "precursor_df = precursor_df.fillna('')",
  "precursor_df['mod_sites'] = precursor_df['mod_sites'].astype('string')",
  "from peptdeep.pretrained_models import *",
  "model_mgr_rt = ModelManager(mask_modloss=False)",
  paste0(
    "model_mgr_rt.load_external_models(rt_model_file ='",
    folder_alphapeptdeep_model,
    project_name,
    "/rt.pth",
    "')"
  ),
  "output_prediction_rt=model_mgr_rt.predict_rt(precursor_df)",
  paste0(
    "output_prediction_rt.to_csv('",
    folder_alphapeptdeep,"output/",project_name,"/rt_test_output.csv",
    "')"
  )
) %>% 
  write(
    paste0(
      folder_alphapeptdeep,project_name,".py"
    )
  )

script <- paste0(folder_alphapeptdeep,project_name,".py")

system(
  paste0(
    'powershell -Command \"',
    "cd ",folder_alphapeptdeep,"; ",
    python," ",
    script
  ),
  wait =TRUE,
  invisible = FALSE
)
```

## APD Result Reading:: QC statistics
<!-- table_qc_training >> table_qc_training_output >> table_qc_training_output_fit -->
<!-- fit_rt_training: linear model -->
<!-- table_qc_training_output+fit_rt_training >> table_qc_training_output_fit -->
<!-- table_qc_training_output_fit >> summary_rtprediction_t95 -->
<!-- table_qc_training_output_fit >> summary_rtprediction for MAE, RSQ, and RMSE -->
```{r}

table_qc_training_export %>% 
  bind_cols(
    read_csv(
      paste0(folder_alphapeptdeep,"output/",project_name,"/rt_training_output.csv")
    ) %>% select(rt_pred)
  ) %>% 
  mutate(
    irt_pred = rt_pred*rt_duration+rt_start
  ) -> table_qc_training_output
  
  
  
fit_rt_training <- lm(irt ~ irt_pred, data =table_qc_training_output)

table_qc_training_output %>% 
  bind_cols(
    predict(fit_rt_training, interval = "prediction", level =0.95, newdata = table_qc_training_output)
  ) -> table_qc_training_output_fit

#t95
table_qc_training_output_fit %>% 
  mutate(t95=upr-lwr) %>% 
  summarise(
    t95_mean = mean(t95)
  ) -> summary_rtprediction_t95
  
##mae rsq rmse
table_qc_training_output_fit %>% 
  metrics(
    truth = irt, estimate = irt_pred
  ) -> summary_rtprediction
```

## APD for QC Figure
<!-- table_qc_training_output_fit >> data_rt_plot -->
```{r}
table_qc_training_output_fit %>% 
  ggplot(aes(x=irt, y=irt_pred))+
  geom_point(size=0.5,alpha=0.5) +
  annotate(
    "text",x=-Inf,y=Inf,hjust=0,vjust=1.2,
    label=bquote(
      ~Delta*italic(t)[95*'%'] == .(str_sub(paste0(summary_rtprediction_t95[1,1]),1,5))*","~R^2==.(summary_rtprediction %>% filter(.metric =="rsq") %>% pull(.estimate) %>% round(3))
    ),size =4
  )+
  annotate(
    "text",x=-Inf,y=Inf,hjust=0,vjust=3.2,
    label=bquote(
      ~MAE==.(summary_rtprediction %>% filter(.metric =="mae") %>% pull(.estimate) %>% round(3))*","~N==.(table_qc_training_output %>% nrow())
    ),size =4
  )+
  geom_line(aes(x=lwr), color = "red", linetype = "dashed")+
  geom_line(aes(x=upr), color = "red", linetype = "dashed")+
  geom_smooth(method=lm, se=TRUE)+
  #lims(x=c(0,1),y=c(0,1))+
  labs(
    x="Observed RT (min)",
    y="Predicted RT (min)"
  )+
  theme_classic2()+
  theme(
    axis.text = element_text(color = "black",size=10),
    axis.title = element_text(color = "black",size=11)
  )
ggsave(
  paste0("./figures/natcomm_revision/rt_prediction_training_",project_name,".png"),width=10,height=10,dpi = 600,units="cm"
)
  
table_qc_training_output_fit %>% 
  filter(
    str_detect(sequence,"^R")
  ) -> data_rt_plot
  
data_rt_plot %>% 
  ggplot(aes(x=irt, y=irt_pred))+
  geom_point(size=0.5,alpha=0.5) +
  annotate(
    "text",x=-Inf,y=Inf,hjust=0,vjust=1.2,
    label=bquote(
      ~Delta*italic(t)[95*'%'] == .(str_sub(paste0(summary_rtprediction_t95[1,1]),1,5))*","~R^2==.(summary_rtprediction %>% filter(.metric =="rsq") %>% pull(.estimate) %>% round(3))
    ),size =4
  )+
  annotate(
    "text",x=-Inf,y=Inf,hjust=0,vjust=3.2,
    label=bquote(
      ~MAE==.(summary_rtprediction %>% filter(.metric =="mae") %>% pull(.estimate) %>% round(3))*","~N==.(data_rt_plot %>% nrow())
    ),size =4
  )+
  geom_line(aes(x=lwr), color = "red", linetype = "dashed")+
  geom_line(aes(x=upr), color = "red", linetype = "dashed")+
  #geom_smooth(method=lm, se=TRUE)+
  #lims(x=c(0,1),y=c(0,1))+
  labs(
    x="Observed RT (min)",
    y="Predicted RT (min)"
  )+
  theme_classic2()+
  theme(
    axis.text = element_text(color = "black",size=10),
    axis.title = element_text(color = "black",size=11)
  )
ggsave(
  paste0("./figures/natcomm_revision/rt_prediction_training_arg_",project_name,".png"),width=10,height=10,dpi = 600,units="cm"
)
```

## APD Result Reading:: for test set
<!-- Figures for Target RT histogram, PRTC RT deviation,  -->
<!-- table_arg_predicted -->
```{r}
  ##READ rt prediction ::run every QC

read_csv(
  paste0(folder_alphapeptdeep,"output/",project_name,"/rt_test_output.csv")
)->table_arg_predicted

table_arg_predicted %>% 
  mutate(
    irt_pred = rt_pred*rt_duration+rt_start
  ) -> table_arg_predicted
```

## APD Result Figure:: Targets RT histogram
<!-- table_arg_predicted -->
```{r}
table_arg_predicted %>% 
  distinct(sequence,.keep_all = TRUE) %>% 
  ggplot(
    aes(x=irt_pred)
  )+
  geom_histogram(
    binwidth = 1,
    color = "black",
    fill = "#377EB8"
  )+
  theme_bw()
ggsave(
  paste0("./figures/natcomm_revision/arg_prediction_histogram_",project_name,".png"),width=10,height=10,dpi = 600,units="cm"
)
```

## APD Result Figure:: PRTC RT deviations
<!-- table_arg_predicted -->
```{r}
table_arg_predicted %>% 
  filter(cleavage_type=="PRTC") %>% 
  select(
    gene_position,irt_pred
  ) %>% 
  left_join(
    table_qc_training %>% 
      filter(
        sequence %in% table_prtc$sequence
      ) %>% 
      left_join(
        table_prtc %>% select(sequence,gene_position)
      ) %>% 
      select(
        gene_position, irt
      )
  ) %>% 
  mutate(
    irt_irt_pred=irt-irt_pred
  ) %>% 
  ggplot(
    aes(x=gene_position, y=irt_irt_pred)
  )+
  geom_bar(
    stat= "identity"
  )+
  labs(x="PRTC",y="Observed RT - Predicted RT")+
  theme_bw()+
  theme(
    axis.text = element_text(color="black"),
    axis.text.x = element_text(angle=45,hjust =1),
  )
ggsave(
  paste0("./figures/natcomm_revision/rt_prediction_prtc_",project_name,".png"),width=20,height=10,dpi = 600,units="cm"
)
```

## Writing Inclusion List
<!-- table_arg_predicted >> inclusionlist.csv -->
<!-- time window = +_5 >> -2 to +8 -->
```{r}
##write inclusion list ##target type arg 240406
table_arg_predicted %>% 
  mutate(
    gene_position = paste0(gene_position,"|L")
  ) %>% 
  bind_rows(
    table_arg_predicted %>% 
      filter(
        !str_detect(gene_position,"PRTC")
      ) %>% 
      mutate(
        r_count = str_count(sequence,"R"),
        r_heavy_mass = 6.020129*r_count/charge,
        mz = mz + r_heavy_mass,
        gene_position = paste0(gene_position,"|H")
      )
  ) -> table_arg_predicted_final
  # mutate(
  #   passed = case_when(
  #     target_type == "arg" & charge == 3 ~ TRUE,
  #     target_type == "free" & charge == 2 ~ TRUE,
  #     .default = FALSE
  #   )
  # ) %>% 
  # filter(
  #   (passed == TRUE & cleavage_type %in% c("SP","mTP")) |
  #     (passed == TRUE & gene_position %in% vector_nucleus_arg)|
  #     (passed == TRUE & str_detect(cleavage_type,"C14")) |
  #     str_detect(gene_position,"PRTC")|
  #     (passed == TRUE & gene_position %in% vector_upr_protein)
  # ) %>% #view()

table_arg_predicted_final %>% 
  mutate(
    mz = round(mz,4)
  ) %>% 
  mutate(
    Comment = paste0(gene_position,"_",sequence,"_",charge)
  ) %>% 
  distinct(Comment,.keep_all = TRUE) %>% 
  select(
    mz,
    irt_pred,
    charge,
    Comment
  ) %>% 
  mutate(
    mz= as.character(mz),
    lwr = as.character(round(irt_pred,2)-2),
    upr = as.character(round(irt_pred,2)+8)
  ) %>% 
  rename(
    `Mass [m/z]` = mz,
    `Start [min]` = lwr,
    `End [min]` = upr
  ) %>% 
  mutate(
    `Formula [M]` = "",
    `Formula type` = "",
    `Species` = "",
    `CS [z]` = as.character(charge),
    Polarity = "Positive",
    `(N)CE` = "",
    `(N)CE type` = "",
    `MSX ID` = ""
  ) %>% 
  select(
    `Mass [m/z]`,
    `Formula [M]`,
    `Formula type`,
    `Species`,
    `CS [z]`,
    Polarity,
    `Start [min]`,
    `End [min]`,
    `(N)CE`,
    `(N)CE type`,
    `MSX ID`,
    Comment
  ) %>% 
  write_csv(
    paste0("./inclusionlist/incl_",project_name,".csv")
  )

```



