---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
# Libraries
```{r}
library(pROC)
library(tidyverse)
#library(ggridges)
library(devtools)
library(Biostrings)
library(Peptides)
library(ggpubr)
#library(VennDiagram)
library(RColorBrewer)
#library(hrbrthemes)
#library(hexbin)
library(ggseqlogo)
library(dagLogo)
#library(plotly)
library(wesanderson)
library(Rdisop)
library(conflicted)
library(broom)
#library(seqRFLP)
library(OrgMassSpecR) 
library(scales)
conflict_scout()
conflicts_prefer(dplyr::filter())
conflicts_prefer(dplyr::select())
conflicts_prefer(dplyr::rename())
conflicts_prefer(dplyr::first())
conflicts_prefer(dplyr::desc())
source("G:/Rcheatsheet/functions/FragmentPeptide3.R")
library(tidymodels)
library(ComplexHeatmap)
library(ggpointdensity)
library(viridis)
library(ggVennDiagram)
library(clusterProfiler)
library(org.Hs.eg.db)
Sys.setenv(R_LIBCURL_SSL_REVOKE_BEST_EFFORT=TRUE)
library(ReactomePA)
library(rrvgo)
library(UniProtKeywords)
library(org.Hs.eg.db)
library(ggrepel)
library(magrittr)
```


#Fig. 2a
```{r}
#left
output_prediction_comparison_trypsin_241009 %>%
  mutate(
    model = fct(model,levels=c("pretrained","built","finetuned","finetunedwoarg"))
  ) %>% 
  ggplot(aes(x=model,y=PCC))+
  geom_violin(aes(fill = model),linewidth = 0.1,scale = "width")+
  labs(y="PCC")+
  geom_boxplot(width = 0.1,outlier.shape = NA,linewidth = 0.1)+
  scale_x_discrete(labels =c("Pretrained","Built","Fine-tuned","Fine-tuned w/o\nR-starting peptides"))+
  scale_fill_manual(
    values = c("#4DAF4A","#377EB8","#E41A1C","#984EA3")
  )+
  scale_y_continuous(
    limits=c(0,1)
  )+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_text(color = "black",size = 7),
    axis.text.x = element_blank(),
    axis.text.y = element_text(color = "black",size = 7)
  )
ggsave("./figures/2_03_finetuning1.png",width =4.5, height = 4,dpi = 600,units = "cm")

#middle
output_prediction_comparison_trypsin_241009 %>% 
  mutate(
    model = fct(model,levels=c("pretrained","built","finetuned","finetunedwoarg"))
  ) %>% 
  filter(PCC >= 0.9) %>% 
  summarize(
    .by = model,
    count = n()
  ) %>% 
  mutate(
    perc = count/9569
  ) %>% 
  ggplot(aes(x=model,y=perc,fill=model))+
  geom_bar(stat = "identity")+
  geom_text(
    aes(label = scales::percent(perc,accuracy = 0.1)),vjust =-0.3,
    size =2
  )+
  labs(y="PCC \u2265 0.9")+
  scale_y_continuous(labels = scales::percent,breaks = seq(0,1,0.25),limits = c(0,1))+
  #scale_x_discrete(labels =c("Built","Pretrained","Fine-tuned","Fine-tuned w/o\nR-starting peptides"))+
  scale_fill_manual(
    values = c("#4DAF4A","#377EB8","#E41A1C","#984EA3")
  )+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_text(color = "black",size = 7),
    axis.text.x = element_blank(),
    axis.text.y = element_text(color = "black",size = 7)
  )
ggsave("./figures/2_03_finetuning2.png",width =4.5, height = 4,dpi = 600,units = "cm")


#right
read_rds(
  "./export/psm_17669.rds"
) -> psm_17669

psm_17669 %>% 
  filter(
    enzyme == "trypsin"
  ) %>% 
  mutate(
    index = 1:nrow(.)
  ) -> psm_9569

psm_9569 %>% 
  select(index,frag_df) %>% 
  unnest(frag_df) %>% 
  mutate(
    across(everything(),\(x) replace_na(x,0))
  ) %>% 
  bind_cols(
    read_tsv(
      "C:/Users/admin/alphapeptdeep/project/alphapeptdeep_115/alphapeptdeep/inrich/output/prediction_17669_predict_inten_df_pretrained_model_trypsin_231206.tsv"
    ) %>% select(
      b_z1,b_z2,y_z1,y_z2
    ) %>% 
      rename_with(
        .fn = \(x) paste0(x,"_pretrained")
      ),
    read_tsv(
      "C:/Users/admin/alphapeptdeep/project/alphapeptdeep_115/alphapeptdeep/inrich/output/prediction_17669_predict_inten_df_built_model_trypsin_231206.tsv"
    ) %>% select(
      b_z1,b_z2,y_z1,y_z2
    ) %>% 
      rename_with(
        .fn = \(x) paste0(x,"_built")
      ),
    read_tsv(
      "C:/Users/admin/alphapeptdeep/project/alphapeptdeep_115/alphapeptdeep/inrich/output/prediction_17669_predict_inten_df_finetuned_model_trypsin_231206.tsv"
    ) %>% select(
      b_z1,b_z2,y_z1,y_z2
    ) %>% 
      rename_with(
        .fn = \(x) paste0(x,"_finetuned")
      ),
    read_tsv(
      "C:/Users/admin/alphapeptdeep/project/alphapeptdeep_115/alphapeptdeep/inrich/output/prediction_9569_predicted_inten_df_311547woarg_model_trypsin_231213.tsv"
    ) %>% select(
      b_z1,b_z2,y_z1,y_z2
    ) %>% 
      rename_with(
        .fn = \(x) paste0(x,"_finetunedwoarg")
      )
  ) %>% 
  select(
    -c(frag_index,ion_num2)
  ) %>% 
  nest(
    data = c(b_z1,b_z2,y_z1,y_z2),
    pretrained = contains("pretrained"),
    built = contains("built"),
    finetuned = contains("finetuned"),
    finetunedwoarg = contains("finetunedwoarg")
  ) -> psm_9569_ionspecies_test_241010

psm_9569_ionspecies_test_241010 %>% #head() %>% pull(data)
  mutate(
    pretrained_pcc = map2_dbl(
      data,
      pretrained,
      \(x,y) cor(
        append(
          pull(x,b_z1),
          pull(x,b_z2)
        ) %>% append(
          pull(x,y_z1)
        ) %>% 
          append(
            pull(x,y_z2)
          )  ,
        append(
          pull(y,b_z1_pretrained),
          pull(y,b_z2_pretrained)
        ) %>% append(
          pull(y,y_z1_pretrained)
        ) %>% 
          append(
            pull(y,y_z2_pretrained)
          ),
        method = "pearson"
      )
    ),
    pretrained_pcc_b = map2_dbl(
      data,
      pretrained,
      \(x,y) cor(
        append(pull(x,b_z1),pull(x,b_z2)),
        append(pull(y,b_z1_pretrained),pull(y,b_z2_pretrained)),
        method = "pearson"
      )
    ),
    pretrained_pcc_y = map2_dbl(
      data,
      pretrained,
      \(x,y) cor(
        append(pull(x,y_z1),pull(x,y_z2)),
        append(pull(y,y_z1_pretrained),pull(y,y_z2_pretrained)),
        method = "pearson"
      )
    )
  ) %>% 
  mutate(
    built_pcc = map2_dbl(
      data,
      built,
      \(x,y) cor(
        append(
          pull(x,b_z1),
          pull(x,b_z2)
        ) %>% append(
          pull(x,y_z1)
        ) %>% 
          append(
            pull(x,y_z2)
          )  ,
        append(
          pull(y,b_z1_built),
          pull(y,b_z2_built)
        ) %>% append(
          pull(y,y_z1_built)
        ) %>% 
          append(
            pull(y,y_z2_built)
          ),
        method = "pearson"
      )
    ),
    built_pcc_b = map2_dbl(
      data,
      built,
      \(x,y) cor(
        append(pull(x,b_z1),pull(x,b_z2)),
        append(pull(y,b_z1_built),pull(y,b_z2_built)),
        method = "pearson"
      )
    ),
    built_pcc_y = map2_dbl(
      data,
      built,
      \(x,y) cor(
        append(pull(x,y_z1),pull(x,y_z2)),
        append(pull(y,y_z1_built),pull(y,y_z2_built)),
        method = "pearson"
      )
    )
  )%>% 
  mutate(
    finetuned_pcc = map2_dbl(
      data,
      finetuned,
      \(x,y) cor(
        append(
          pull(x,b_z1),
          pull(x,b_z2)
        ) %>% append(
          pull(x,y_z1)
        ) %>% 
          append(
            pull(x,y_z2)
          )  ,
        append(
          pull(y,b_z1_finetuned),
          pull(y,b_z2_finetuned)
        ) %>% append(
          pull(y,y_z1_finetuned)
        ) %>% 
          append(
            pull(y,y_z2_finetuned)
          ),
        method = "pearson"
      )
    ),
    finetuned_pcc_b = map2_dbl(
      data,
      finetuned,
      \(x,y) cor(
        append(pull(x,b_z1),pull(x,b_z2)),
        append(pull(y,b_z1_finetuned),pull(y,b_z2_finetuned)),
        method = "pearson"
      )
    ),
    finetuned_pcc_y = map2_dbl(
      data,
      finetuned,
      \(x,y) cor(
        append(pull(x,y_z1),pull(x,y_z2)),
        append(pull(y,y_z1_finetuned),pull(y,y_z2_finetuned)),
        method = "pearson"
      )
    )
  )%>% 
  mutate(
    finetunedwoarg_pcc = map2_dbl(
      data,
      finetunedwoarg,
      \(x,y) cor(
        append(
          pull(x,b_z1),
          pull(x,b_z2)
        ) %>% append(
          pull(x,y_z1)
        ) %>% 
          append(
            pull(x,y_z2)
          )  ,
        append(
          pull(y,b_z1_finetunedwoarg),
          pull(y,b_z2_finetunedwoarg)
        ) %>% append(
          pull(y,y_z1_finetunedwoarg)
        ) %>% 
          append(
            pull(y,y_z2_finetunedwoarg)
          ),
        method = "pearson"
      )
    ),
    finetunedwoarg_pcc_b = map2_dbl(
      data,
      finetunedwoarg,
      \(x,y) cor(
        append(pull(x,b_z1),pull(x,b_z2)),
        append(pull(y,b_z1_finetunedwoarg),pull(y,b_z2_finetunedwoarg)),
        method = "pearson"
      )
    ),
    finetunedwoarg_pcc_y = map2_dbl(
      data,
      finetunedwoarg,
      \(x,y) cor(
        append(pull(x,y_z1),pull(x,y_z2)),
        append(pull(y,y_z1_finetunedwoarg),pull(y,y_z2_finetunedwoarg)),
        method = "pearson"
      )
    )
  ) -> psm_9569_ionspecies_test_241010_done

psm_9569_ionspecies_test_241010_done

psm_9569_ionspecies_test_241010_done %>% 
  select(
    -c(data,pretrained,built,finetuned,finetunedwoarg)
  ) %>% 
  pivot_longer(
    cols = -c(index)
  ) -> psm_9569_ionspecies_test_241010_done

psm_9569_ionspecies_test_241010_done %>% 
  mutate(
    model = str_split_i(name,"_",1)
  ) %>% 
  filter(
    !str_detect(name,"pcc$")
  ) %>% 
  mutate(
    frag_series = str_split_i(name,"_",3)
  ) %>% 
  mutate(
    model = factor(model,levels=c("pretrained","built","finetuned","finetunedwoarg"),labels=c("Pretrained","Built","Fine-tuned","Fine-tuned w/o \n R-starting Peptides"))
  ) %>% 
  ggplot(aes(x=frag_series,y=value))+
  geom_violin(aes(fill = frag_series),linewidth = 0.1,scale = "width")+
  labs(y="PCC")+
  geom_boxplot(width = 0.25,outlier.shape = NA,linewidth = 0.1)+
  # scale_x_discrete(labels =c("Pretrained","Built","Fine-tuned","Fine-tuned w/o\nR-starting peptides"))+
  scale_fill_manual(
    values = c(wes_palette("Zissou1")[1],wes_palette("Zissou1")[5])
  )+
  scale_x_discrete(
    labels = c("b-ion","y-ion")
  )+
  scale_y_continuous(
    limits=c(0.5,1)
  )+
  facet_wrap(
    facets = vars(model),
    nrow = 1
  )+
  theme_classic2()+
  theme(
    legend.position = "none",
    strip.text = element_text(color = "black",size = 2),
    axis.title.x = element_blank(),
    axis.title.y = element_text(color = "black",size = 7),
    axis.text.x = element_blank(),
    axis.text.y = element_text(color = "black",size = 7),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    panel.spacing = unit(0.1, "cm"),
    axis.ticks.x = element_blank(),
    axis.line.x = element_blank(),
    plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
  )
ggsave("./figures/2_03_model_yions.png",width=4.5,height=3,dpi = 600,units="cm")

```

#Fig. 2b
```{r}
summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  mutate(
    histogram_color = case_when(
      PCC>=0.9 ~ fct("1",levels = c("1","2","3","4")),
      PCC<0.9 & PCC >=0.6 ~ fct("2",levels = c("1","2","3","4")),
      PCC<0.6 ~ fct("3",levels = c("1","2","3","4"))
    )
  ) %>% 
  gghistogram(
    x = "PCC", 
    add = "median", rug = TRUE,
    fill = "histogram_color", palette = c("#66C2A5", "#FC8D62","#8DA0CB"),
    binwidth = 0.025,
    #add_density = TRUE,
    position="stack",
    size = 0.1
  )+
  labs(x="PCC",y="Count")+
  scale_x_continuous(limits = c(-0.2,1))+
  theme(
    legend.position = "none",
    #axis.title.x = element_blank(),
    axis.title = element_text(color = "black",size = 7),
    #axis.text.x = element_blank(),
    axis.text = element_text(color = "black",size = 6),
    plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
  )
ggsave("./figures/2_03_pcc_summary.png",width=4.5,height=4.5, units = "cm",dpi = 600)

```

#Fig. 2c
```{r}
summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  select(
    prot_pos_reposition,PCC,bion_pcc,yion_pcc
  ) %>% 
  pivot_longer(cols=c(bion_pcc,yion_pcc)) %>% 
  mutate(
    group = case_when(
      PCC>=0.9 ~ fct("1",levels = c("1","2","3","4")),
      PCC<0.9 & PCC >=0.6 ~ fct("2",levels = c("1","2","3","4")),
      PCC<0.6 ~ fct("3",levels = c("1","2","3","4"))
    )
  ) %>% 
  ggplot(
    aes(y=value,x=group,fill=name)
  )+
  geom_boxplot(
    size = 0.2,
    outlier.size = 0.2,
  )+
  annotate(
    "text",
    x=1:3,
    y = 1.08,
    label = paste("N = ",c(194,446,577)),
    size = 2
  )+
  scale_x_discrete(
    limits = c("3","2","1"),
    labels = c(expression("PCC"<"0.6", paste("0.6"<="","PCC",""<"0.9"),"0.9"<="PCC"))
  )+
  scale_fill_manual(labels = c("b-ion","y-ion"),values = c(wes_palette("Zissou1")[1],wes_palette("Zissou1")[5]))+
  labs(y="PCC")+
  theme_classic()+
  theme(
    legend.position = "none",
    legend.title = element_blank(),
    text= element_text(color = "black", size = 7),
    axis.text.y = element_text(color = "black", size = 7, hjust=1),
    axis.text.x = element_text(color = "black", size = 7,angle = 20, hjust =1),
    axis.title.x = element_blank(),
    plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
  )
ggsave("./figures/2_pcc_ions.png",width=4.5,height=4,dpi = 600,units="cm")
```

#Fig. 2d
```{r}
#from bidding_pcc_fdr.R
ggroc(
  list(
    PCC=roc(response=fdr_pcc_negative_set8$true_set,predictor = fdr_pcc_negative_set8$PCC), ##0.6105
    SA=roc(response=fdr_pcc_negative_set8$true_set,predictor = fdr_pcc_negative_set8$SA), ##0.6083
    SPC=roc(response=fdr_pcc_negative_set8$true_set,predictor = fdr_pcc_negative_set8$SPC), ## 0.5263
    specFDR=roc(response=fdr_pcc_negative_set8$true_set,predictor = fdr_pcc_negative_set8$spec_FDR), #0.5015
    specFNR=roc(response=fdr_pcc_negative_set8$true_set,predictor = fdr_pcc_negative_set8$spec_FNR), ##0.481
    percolator=roc(response=fdr_pcc_negative_set8$true_set,predictor = fdr_pcc_negative_set8$percolator_score) #0.4979
  )
)+
  scale_color_manual(
    values =c("#E41A1C","#377EB8","#4DAF4A","#984EA3","#FF7F00","#F781BF","#1d91c0")
  )+
  theme_classic()+
  theme(
    #legend.position = "none",
    legend.title = element_blank(),
    text= element_text(color = "black", size = 10),
    axis.text.y = element_text(color = "black", size = 10, hjust=1),
    axis.text.x = element_text(color = "black", size = 10),
    #axis.title.x = element_blank()
  )
ggsave("./figures/fdr_roc_v5.png",width=5,height=5,dpi = 600,units="cm")
```


#Fig. 2e
```{r}
#pcc_fdr2.R
fdr_pcc_negative_set7_trypsin %>% 
  arrange(desc(PCC)) %>% 
  mutate(
    PCC_index = 1:nrow(.)
  ) %>% 
  mutate(
    FDR1 = cummean(fdr)
  ) %>% 
  arrange(desc(percolator_score)) %>% 
  mutate(
    pecolator_index = 1:nrow(.)
  ) %>% 
  mutate(
    FDR2 = cummean(fdr)
  ) %>% 
  mutate(
    fdr = if_else(true_set =="true",0,1)
  ) %>% 
  ggplot(
  )+
  geom_point(
    aes(x=PCC_index,y=FDR1),color="#FF0000",size=0.05,alpha = 0.1
  )+
  geom_point(
    aes(x=pecolator_index,y=FDR2),color="#00A08A",size=0.05,alpha = 0.1
  )+
  geom_hline(yintercept = 0.01,linetype = 2)+
  labs(
    x="Index",
    y="FDR"
  )+
  scale_y_continuous(
    labels = scales::percent,
    breaks = seq(0,0.05,0.01),
    limits = c(0,0.05)
  )+
  scale_x_reverse()+
  theme_classic2()+
  theme(
    legend.position = "none",
    #axis.title.x = element_blank(),
    text= element_text(color = "black", size = 8),
    axis.text.y = element_text(color = "black", size = 7, hjust=1),
    axis.text.x = element_text(color = "black", size = 7),
    #axis.title.x = element_blank()
    plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
  )
ggsave("./figures/2_06_new_fdrcurve.png",width=4.5,height=4.5,dpi = 600,units="cm")


```

#Fig. 2f
```{r}
summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  select(
    index,prot_pos_reposition,PCC,bion_pcc,yion_pcc,pcc_check
  ) %>% 
  pivot_longer(cols=c(bion_pcc,yion_pcc)) %>% 
  mutate(
    group = case_when(
      pcc_check==1 ~ fct("1",levels = c("1","0")),
      pcc_check==0 ~ fct("0",levels = c("1","0"))
    )
  ) %T>% 
  write_tsv(
    "./figures/fig2f.tsv"
  ) %>% 
  ggplot(
    aes(y=value,x=group,fill=name)
  )+
  geom_boxplot(
    size = 0.2,
    outlier.size = 0.2,
  )+
  annotate(
    "text",
    x=1:2,
    y = 1.08,
    label = paste("N = ",c(594,623)),
    size = 2
  )+
  scale_x_discrete(
    limits = c("0","1"),
    labels = c(expression("FDR">"1%", "FDR"<="1%"))
  )+
  scale_fill_manual(labels = c("b-ion","y-ion"),values = c(wes_palette("Zissou1")[1],wes_palette("Zissou1")[5]))+
  labs(y="PCC")+
  theme_classic()+
  theme(
    legend.position = "none",
    legend.title = element_blank(),
    text= element_text(color = "black", size = 7),
    axis.text.y = element_text(color = "black", size = 7, hjust=1),
    axis.text.x = element_text(color = "black", size = 7),
    axis.title.x = element_blank(),
    plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
  )
ggsave("./figures/2_07_fdr_ions.png",width=4.5,height=4,dpi = 600,units="cm")
```


#Fig. 2g
```{r}
output_prediction_rt_train_result
summary_rtprediction_t95 %>% 
  write_tsv(
    "./figures/summary_rtprediction_t95.tsv"
  )
summary_rtprediction%>% 
  write_tsv(
    "./figures/summary_rtprediction.tsv"
  )

output_prediction_rt_test_result %>% filter(file_series==1) 

i=1

output_prediction_rt_train_result %>% 
  filter(file_series == i) %T>% 
  write_tsv(
    "./figures/2_08_rt_prediction_training_set_mainfigure1.tsv"
  ) %>% 
  ggplot(aes(x=rt_observed, y=rt_predicted))+
  geom_point(size=0.1,alpha=0.25) +
  annotate(
    "text",x=-Inf,y=Inf,hjust=0,vjust=1.2,
    label=bquote(
      ~Delta*italic(t)[95*'%'] == .(str_sub(paste0(summary_rtprediction_t95[i,3]),1,5))*","~R^2==.(summary_rtprediction %>% filter(file_series==i,.metric =="rsq") %>% pull(.estimate) %>% round(3))
    ),size =2
  )+
  annotate(
    "text",x=-Inf,y=Inf,hjust=0,vjust=3.2,
    label=bquote(
      ~MAE==.(summary_rtprediction %>% filter(file_series==i,.metric =="mae") %>% pull(.estimate) %>% round(3))*","~N==.(output_prediction_rt_train_result %>% filter(file_series==i) %>% nrow())
    ),size =2
  )+
  geom_line(aes(x=rt_lwr), color = "red", linetype = "dashed",size =0.5)+
  geom_line(aes(x=rt_upr), color = "red", linetype = "dashed",size =0.5)+
  geom_smooth(method=lm, se=TRUE, size = 0.5)+
  #lims(x=c(0,1),y=c(0,1))+
  labs(
    x="Observed RT (min)",
    y="Predicted RT (min)"
  )+
  theme_classic2()+
  theme(
    legend.position = "none",
    #axis.title.x = element_blank(),
    axis.title = element_text(color = "black",size = 7),
    #axis.text.x = element_blank(),
    axis.text = element_text(color = "black",size = 6),
    plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
  )
ggsave(
  paste0("./figures/2_08_rt_prediction_training_set_mainfigure",i,".png"),width=4.5,height=4.5,dpi = 600,units="cm"
)
```

# Fig. 2h
```{r paged.print=FALSE}
output_prediction_rt_train_result

##original code, for rt model inspection using arg-starting peptides
for (i in 1L:12L){
  output_prediction_rt_train_result %>% 
    filter(file_series == i) %>% 
    ggplot(aes(x=rt_observed, y=rt_predicted))+
    geom_point(size=0.5,alpha=0.5) +
    annotate(
      "text",x=-Inf,y=Inf,hjust=0,vjust=1.2,
      label=bquote(
        ~Delta*italic(t)[95*'%'] == .(str_sub(paste0(summary_rtprediction_t95[i,3]),1,5))*","~R^2==.(summary_rtprediction %>% filter(file_series==i,.metric =="rsq") %>% pull(.estimate) %>% round(3))
      ),size =4
    )+
    annotate(
      "text",x=-Inf,y=Inf,hjust=0,vjust=3.2,
      label=bquote(
        ~MAE==.(summary_rtprediction %>% filter(file_series==i,.metric =="mae") %>% pull(.estimate) %>% round(3))*","~N==.(output_prediction_rt_train_result %>% filter(file_series==i) %>% nrow())
      ),size =4
    )+
    geom_line(aes(x=rt_lwr), color = "red", linetype = "dashed")+
    geom_line(aes(x=rt_upr), color = "red", linetype = "dashed")+
    geom_smooth(method=lm, se=TRUE)+
    #lims(x=c(0,1),y=c(0,1))+
    labs(
      x="Observed RT (min)",
      y="Predicted RT (min)"
    )+
    theme_classic2()+
    theme(
      axis.text = element_text(color = "black",size=10),
      axis.title = element_text(color = "black",size=11)
    )
  ggsave(
    paste0("./figures/rt/rt_prediction_training_set",i,".png"),width=10,height=10,dpi = 600,units="cm"
  )
}

##for rt model inspection using arg-starting peptides >>> R into GV
psm_563516 %>% 
  filter(str_detect(strip_seq,"^R") & str_detect(nmod,"Acetyl\\:")) -> psm_17669_fig2h

psm_17669_fig2h %>% 
  dplyr::rename(
    spec_idx = index
  ) %>% 
  select(
    strip_seq,spec_idx,mods,mod_sites,nAA,nce,instrument,rt_norm,left_time,right_time,nt_arg,file_id_series
  ) %>% 
  dplyr::rename(
    sequence = strip_seq
  ) %>% 
  mutate(
    sequence = str_replace(sequence,"^R","GV"),
    nAA = nAA+1
  ) %>%
  separate_rows(
    mod_sites,sep = ";"
  ) %>% 
  mutate(
    mod_sites = as.integer(mod_sites),
    mod_sites = if_else(mod_sites == 0,0,mod_sites+1)
  ) %>% 
  nest(
    data = mod_sites
  ) %>% #head() %>% pull(data)
  mutate(
    mod_sites = map_chr(
      data,
      \(x) pull(x,mod_sites) %>% paste0(collapse = ";")
    )
  ) %>% 
  select(
    sequence,spec_idx,mods,mod_sites,nAA,nce,instrument,rt_norm,left_time,right_time,nt_arg,file_id_series
  ) -> psm_17669_fig2h

file_raw_index2
i=1
for (i in 1:length(unique(psm_17669_fig2h$file_id_series))){
  psm_563516 %>% 
    filter(file_id_series == file_raw_index2$set[i]) %>% 
    dplyr::rename(
        spec_idx = index 
      ) %>% 
      select(
        strip_seq,spec_idx,mods,mod_sites,nAA,nce,instrument,rt_norm,left_time,right_time,nt_arg
      ) %>% 
      dplyr::rename(
        sequence = strip_seq
      ) %>% 
    write_tsv(
      paste0(folder_alphapeptdeep,"input_rt_training_gv_fig2h_",i,".tsv")
    )
}


for (i in 1:length(unique(psm_17669_fig2h$file_id_series))){
  psm_17669_fig2h %>% 
    filter(file_id_series == file_raw_index2$set[i]) %>% 
    select(
      sequence,spec_idx,mods,mod_sites,nAA,nce,instrument,rt_norm,left_time,right_time,nt_arg
    ) %>% 
    write_tsv(
      paste0(folder_alphapeptdeep,"input_rt_testing_gv_fig2h_",i,".tsv")
    )
}
unique(psm_563516$file_id_series)


# Fig 2h GV, APD runs ###anaconda :: peptdeep231207 
{
  folder_alphapeptdeep
  i=1
  output_prediction_rt_train_result <- tibble()
  output_prediction_rt_test_result <- tibble()
  for (i in 1:12){
    output_prediction_rt_training <- read_tsv(
      paste0(folder_alphapeptdeep,"output_rt_training_gv_fig2h_",i,".tsv")
    )[,-1] %>% 
      arrange(rt_norm) %>% 
      mutate(file_series= i) %>% 
      filter(str_detect(sequence,"^R")) %>% 
      filter(
        str_detect(mods, "Acetyl\\:2H\\(3\\)@Any")
      )
    
    output_prediction_rt_test <- read_tsv(
      paste0(folder_alphapeptdeep,"output_rt_testing_gv_fig2h_",i,".tsv")
    )[,-1] %>% 
      arrange(rt_norm) %>%
      mutate(file_series = i)
    
    fit_rt_training <- lm(rt_norm ~ rt_pred, data =output_prediction_rt_training)
    
    output_prediction_rt_training %>%
      bind_cols(
        predict(fit_rt_training, interval = "prediction", level =0.95, newdata = output_prediction_rt_training)
      )->output_prediction_rt_training
    
    
    output_prediction_rt_test %>% 
      bind_cols(
        predict(fit_rt_training, interval = "prediction", level =0.95, newdata = output_prediction_rt_test)
      )->output_prediction_rt_test
    
    
    output_prediction_rt_train_result %>% 
      bind_rows(
        output_prediction_rt_training
      ) -> output_prediction_rt_train_result
    
    output_prediction_rt_test_result %>% 
      bind_rows(
        output_prediction_rt_test
      ) -> output_prediction_rt_test_result
  }
  output_prediction_rt_train_result %>% 
    arrange(
      spec_idx
    ) ->output_prediction_rt_train_result
  
  output_prediction_rt_test_result %>% 
    arrange(
      spec_idx
    ) ->output_prediction_rt_test_result
  
  output_prediction_rt_test_result %>% 
    mutate(
      rt_test = if_else(rt_norm > lwr & rt_norm < upr, 1, 0)
    ) ->output_prediction_rt_test_result
  
  output_prediction_rt_train_result %>% 
    left_join(
      file_raw_index2 %>% select(-c(left_time,right_time)),
      join_by(file_series)
    ) -> output_prediction_rt_train_result
  
  output_prediction_rt_train_result %>% 
    mutate(
      rt_observed = rt_norm*(right_time-left_time)+left_time,
      rt_predicted = rt_pred*(right_time-left_time)+left_time,
      rt_fit = fit*(right_time-left_time)+left_time,
      rt_lwr = lwr*(right_time-left_time)+left_time,
      rt_upr = upr*(right_time-left_time)+left_time
    ) -> output_prediction_rt_train_result
  
  output_prediction_rt_test_result %>% 
    left_join(
      file_raw_index2,
      join_by(file_series)
    ) ->output_prediction_rt_test_result
  
  output_prediction_rt_test_result %>% 
    select(
      -c(left_time.x,right_time.x)
    ) %>% 
    rename(
      left_time = left_time.y,
      right_time = right_time.y
    ) -> output_prediction_rt_test_result
  
  output_prediction_rt_test_result %>% 
    mutate(
      rt_observed = rt_norm*(right_time-left_time)+left_time,
      rt_predicted = rt_pred*(right_time-left_time)+left_time,
      rt_fit = fit*(right_time-left_time)+left_time,
      rt_lwr = lwr*(right_time-left_time)+left_time,
      rt_upr = upr*(right_time-left_time)+left_time
    ) ->output_prediction_rt_test_result
  
  
  output_prediction_rt_train_result
  output_prediction_rt_test_result
  
  
  ##R, MAE, T90
  {
    
    output_prediction_rt_train_result 
    output_prediction_rt_test_result 
    
    
    output_prediction_rt_train_result %>% 
      filter(file_series==1)
    
    fit_rt_training <- lm(
      rt_observed~ rt_predicted, 
      data =output_prediction_rt_train_result %>% 
        filter(file_series==1))
    
    fit_rt_training %>% tidy()
    
    output_prediction_rt_train_result %>% 
      mutate(t95=rt_upr-rt_lwr) %>% 
      summarise(
        .by = c(set,file_series),
        t95_mean = mean(t95)
      ) -> summary_rtprediction_t95
    summary_rtprediction_t95 %>% write_tsv(
      "./figures/rt/rt_t95.tsv"
    )
    
    summary_rtprediction <- tibble()
    for (i in 1L:12L){
      summary_rtprediction %>% 
        bind_rows(
          output_prediction_rt_train_result %>% 
            filter(file_series==i) %>% 
            metrics(
              truth = rt_observed, estimate = rt_predicted
            ) %>% 
            mutate(
              file_series =i
            )
        )->summary_rtprediction
    }
    summary_rtprediction %>% write_tsv("./figures/rt/summary_rtprediction_250210.tsv")
    
    output_prediction_rt_train_result %>% 
      filter(file_series==i) %>% 
      metrics(
        truth = rt_observed, estimate = rt_predicted
      ) %>% 
      mutate(
        file_series =i
      )
    
  }
  
}

i=1
for (i in 1L:12L){
  output_prediction_rt_train_result %>% 
    filter(file_series == i) %>% 
    ggplot(aes(x=rt_observed, y=rt_predicted))+
    geom_point(size=0.5,alpha=0.5) +
    annotate(
      "text",x=-Inf,y=Inf,hjust=0,vjust=1.2,
      label=bquote(
        ~Delta*italic(t)[95*'%'] == .(str_sub(paste0(summary_rtprediction_t95[i,3]),1,5))*","~R^2==.(summary_rtprediction %>% filter(file_series==i,.metric =="rsq") %>% pull(.estimate) %>% round(3))
      ),size =4
    )+
    annotate(
      "text",x=-Inf,y=Inf,hjust=0,vjust=3.2,
      label=bquote(
        ~MAE==.(summary_rtprediction %>% filter(file_series==i,.metric =="mae") %>% pull(.estimate) %>% round(3))*","~N==.(output_prediction_rt_train_result %>% filter(file_series==i) %>% nrow())
      ),size =4
    )+
    geom_line(aes(x=rt_lwr), color = "red", linetype = "dashed")+
    geom_line(aes(x=rt_upr), color = "red", linetype = "dashed")+
    geom_smooth(method=lm, se=TRUE)+
    #lims(x=c(0,1),y=c(0,1))+
    labs(
      x="Observed RT (min)",
      y="Predicted RT (min)"
    )+
    theme_classic2()+
    theme(
      axis.text = element_text(color = "black",size=10),
      axis.title = element_text(color = "black",size=11)
    )
  ggsave(
    paste0("./figures/rt/rt_prediction_training_set",i,".png"),width=10,height=10,dpi = 600,units="cm"
  )
}
  
  i=1
  
{
  i=1
  output_prediction_rt_train_result %>% 
    filter(file_series == i) %>% 
    ggplot(aes(x=rt_observed, y=rt_predicted))+
    geom_point(size=0.1,alpha=0.25) +
    annotate(
      "text",x=-Inf,y=Inf,hjust=0,vjust=1.2,
      label=bquote(
        ~Delta*italic(t)[95*'%'] == .(str_sub(paste0(summary_rtprediction_t95[i,3]),1,5))*","~R^2==.(summary_rtprediction %>% filter(file_series==i,.metric =="rsq") %>% pull(.estimate) %>% round(3))
      ),size =2
    )+
    annotate(
      "text",x=-Inf,y=Inf,hjust=0,vjust=3.2,
      label=bquote(
        ~MAE==.(summary_rtprediction %>% filter(file_series==i,.metric =="mae") %>% pull(.estimate) %>% round(3))*","~N==.(output_prediction_rt_train_result %>% filter(file_series==i) %>% nrow())
      ),size =2
    )+
    geom_line(aes(x=rt_lwr), color = "red", linetype = "dashed",size =0.5)+
    geom_line(aes(x=rt_upr), color = "red", linetype = "dashed",size =0.5)+
    geom_smooth(method=lm, se=TRUE, size = 0.5)+
    #lims(x=c(0,1),y=c(0,1))+
    labs(
      x="Observed RT (min)",
      y="Predicted RT (min)"
    )+
    theme_classic2()+
    theme(
      legend.position = "none",
      #axis.title.x = element_blank(),
      axis.title = element_text(color = "black",size = 7),
      #axis.text.x = element_blank(),
      axis.text = element_text(color = "black",size = 6),
      plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
    )
  ggsave(
    paste0("./figures/rt/rt_prediction_training_set_mainfigure",i,".png"),width=4.5,height=4.5,dpi = 600,units="cm"
  )
}

output_prediction_rt_test_result %>%
  filter(
    rt_test ==1
  )
  
i=1
for (i in 1L:12L){
  output_prediction_rt_test_result %>% 
    filter(file_series == i) %>% 
    filter(
      rt_test == 1
    ) %>% nrow() -> rt_passed_string
  
  output_prediction_rt_test_result %>% 
    filter(file_series == i) %>% nrow() -> rt_total_string
  
  output_prediction_rt_test_result %>% 
    filter(file_series == i) %>% 
    ggplot(aes(x=rt_observed, y=rt_predicted))+
    geom_point(size=0.1,alpha=0.25) +
    geom_line(aes(x=rt_lwr), color = "red", linetype = "dashed",size =0.5)+
    geom_line(aes(x=rt_upr), color = "red", linetype = "dashed",size =0.5)+
    annotate(
      "text",x=-Inf,y=Inf,hjust=-0.1,vjust=1.1,
      label=bquote(
        .(rt_passed_string)*"/"*.(rt_total_string)
      ),size =2
    )+
    geom_smooth(method=lm, se=TRUE, size = 0.5)+
      #lims(x=c(0,1),y=c(0,1))+
      labs(
        x="Observed RT (min)",
        y="Predicted RT (min)"
      )+
      theme_classic2()+
      theme(
        legend.position = "none",
        #axis.title.x = element_blank(),
        axis.title = element_text(color = "black",size = 7),
        #axis.text.x = element_blank(),
        axis.text = element_text(color = "black",size = 6),
        plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
      )
  ggsave(
    paste0("./figures/rt/rt_prediction_testing_set_fig2h_",i,".png"),width=4.5,height=4.5,dpi = 600,units="cm"
  )
}
```

#Fig. 2i
## Fig 2i + K, SA, DG, > psm_17669_K, psm_17669_SA, psm_17669_DG
```{r paged.print=FALSE}
psm_563516 %>% 
  filter(str_detect(strip_seq,"^R") & str_detect(nmod,"Acetyl\\:")) %>% 
  dplyr::rename(
    spec_idx = index
  ) %>% 
  select(
    strip_seq,spec_idx,mods,mod_sites,nAA,nce,instrument,rt_norm,left_time,right_time,nt_arg,file_id_series
  ) %>% 
  dplyr::rename(
    sequence = strip_seq
  ) %>% 
  mutate(
    sequence = str_replace(sequence,"^R","K")
  ) %>%
  select(
    sequence,spec_idx,mods,mod_sites,nAA,nce,instrument,rt_norm,left_time,right_time,nt_arg,file_id_series
  ) -> psm_17669_K

psm_563516 %>% 
  filter(str_detect(strip_seq,"^R") & str_detect(nmod,"Acetyl\\:")) %>% 
  dplyr::rename(
    spec_idx = index
  ) %>% 
  select(
    strip_seq,spec_idx,mods,mod_sites,nAA,nce,instrument,rt_norm,left_time,right_time,nt_arg,file_id_series
  ) %>% 
  dplyr::rename(
    sequence = strip_seq
  ) %>% 
  mutate(
    sequence = str_replace(sequence,"^R","SA"),
    nAA = nAA+1
  ) %>%
  separate_rows(
    mod_sites,sep = ";"
  ) %>% 
  mutate(
    mod_sites = as.integer(mod_sites),
    mod_sites = if_else(mod_sites == 0,0,mod_sites+1)
  ) %>% 
  nest(
    data = mod_sites
  ) %>% #head() %>% pull(data)
  mutate(
    mod_sites = map_chr(
      data,
      \(x) pull(x,mod_sites) %>% paste0(collapse = ";")
    )
  ) %>% 
  select(
    sequence,spec_idx,mods,mod_sites,nAA,nce,instrument,rt_norm,left_time,right_time,nt_arg,file_id_series
  ) -> psm_17669_SA

psm_563516 %>% 
  filter(str_detect(strip_seq,"^R") & str_detect(nmod,"Acetyl\\:")) %>% 
  dplyr::rename(
    spec_idx = index
  ) %>% 
  select(
    strip_seq,spec_idx,mods,mod_sites,nAA,nce,instrument,rt_norm,left_time,right_time,nt_arg,file_id_series
  ) %>% 
  dplyr::rename(
    sequence = strip_seq
  ) %>% 
  mutate(
    sequence = str_replace(sequence,"^R","DG"),
    nAA = nAA+1
  ) %>%
  separate_rows(
    mod_sites,sep = ";"
  ) %>% 
  mutate(
    mod_sites = as.integer(mod_sites),
    mod_sites = if_else(mod_sites == 0,0,mod_sites+1)
  ) %>% 
  nest(
    data = mod_sites
  ) %>% #head() %>% pull(data)
  mutate(
    mod_sites = map_chr(
      data,
      \(x) pull(x,mod_sites) %>% paste0(collapse = ";")
    )
  ) %>% 
  select(
    sequence,spec_idx,mods,mod_sites,nAA,nce,instrument,rt_norm,left_time,right_time,nt_arg,file_id_series
  ) -> psm_17669_DG
```

## Fig 2i + K, SA, DG, > psm_17669_K, psm_17669_SA, psm_17669_DG > test input file for APD
```{r paged.print=FALSE}
for (i in 1:length(unique(psm_17669_K$file_id_series))){
  psm_17669_K %>% 
    filter(file_id_series == file_raw_index2$set[i]) %>% 
    select(
      sequence,spec_idx,mods,mod_sites,nAA,nce,instrument,rt_norm,left_time,right_time,nt_arg
    ) %>% 
    write_tsv(
      paste0(folder_alphapeptdeep,"input_rt_testing_k_",i,".tsv")
    )
}

for (i in 1:length(unique(psm_17669_SA$file_id_series))){
  psm_17669_SA %>% 
    filter(file_id_series == file_raw_index2$set[i]) %>% 
    select(
      sequence,spec_idx,mods,mod_sites,nAA,nce,instrument,rt_norm,left_time,right_time,nt_arg
    ) %>% 
    write_tsv(
      paste0(folder_alphapeptdeep,"input_rt_testing_sa_",i,".tsv")
    )
}

for (i in 1:length(unique(psm_17669_DG$file_id_series))){
  psm_17669_DG %>% 
    filter(file_id_series == file_raw_index2$set[i]) %>% 
    select(
      sequence,spec_idx,mods,mod_sites,nAA,nce,instrument,rt_norm,left_time,right_time,nt_arg
    ) %>% 
    write_tsv(
      paste0(folder_alphapeptdeep,"input_rt_testing_dg_",i,".tsv")
    )
}
```

## Fig 2i + K, SA, DG, > output_prediction_rt_test_k_result, output_prediction_rt_test_sa_result, output_prediction_rt_test_dg_result
```{r paged.print=FALSE}
#K
{
  i=1
  output_prediction_rt_test_k_result <- tibble()
  for (i in 1:12){
    output_prediction_rt_test_k <- read_tsv(
      paste0(folder_alphapeptdeep,"output_rt_testing_k_",i,".tsv")
    )[,-1] %>% 
      arrange(rt_norm) %>%
      mutate(file_series = i)
    
    fit_rt_training <- lm(rt_norm ~ rt_pred, data =output_prediction_rt_training)
    
    output_prediction_rt_test_k %>% 
      bind_cols(
        predict(fit_rt_training, interval = "prediction", level =0.95, newdata = output_prediction_rt_test_k)
      )->output_prediction_rt_test_k
    
    
    output_prediction_rt_test_k_result %>% 
      bind_rows(
        output_prediction_rt_test_k
      ) -> output_prediction_rt_test_k_result
  }
  
  output_prediction_rt_test_k_result %>% 
    arrange(
      spec_idx
    ) %>% 
    mutate(
      rt_test = if_else(rt_norm > lwr & rt_norm < upr, 1, 0)
    ) %>% 
    left_join(
      file_raw_index2,
      join_by(file_series)
    ) %>% 
    select(
      -c(left_time.x,right_time.x)
    ) %>% 
    rename(
      left_time = left_time.y,
      right_time = right_time.y
    ) %>% 
    mutate(
      rt_observed = rt_norm*(right_time-left_time)+left_time,
      rt_predicted = rt_pred*(right_time-left_time)+left_time,
      rt_fit = fit*(right_time-left_time)+left_time,
      rt_lwr = lwr*(right_time-left_time)+left_time,
      rt_upr = upr*(right_time-left_time)+left_time
    ) ->output_prediction_rt_test_k_result
}

#SA
{
  i=1
  output_prediction_rt_test_sa_result <- tibble()
  for (i in 1:12){
    output_prediction_rt_test_sa <- read_tsv(
      paste0(folder_alphapeptdeep,"output_rt_testing_sa_",i,".tsv")
    )[,-1] %>% 
      arrange(rt_norm) %>%
      mutate(file_series = i)
    
    fit_rt_training <- lm(rt_norm ~ rt_pred, data =output_prediction_rt_training)
    
    output_prediction_rt_test_sa %>% 
      bind_cols(
        predict(fit_rt_training, interval = "prediction", level =0.95, newdata = output_prediction_rt_test_sa)
      )->output_prediction_rt_test_sa
    
    
    output_prediction_rt_test_sa_result %>% 
      bind_rows(
        output_prediction_rt_test_sa
      ) -> output_prediction_rt_test_sa_result
  }
  
  output_prediction_rt_test_sa_result %>% 
    arrange(
      spec_idx
    ) %>% 
    mutate(
      rt_test = if_else(rt_norm > lwr & rt_norm < upr, 1, 0)
    ) %>% 
    left_join(
      file_raw_index2,
      join_by(file_series)
    ) %>% 
    select(
      -c(left_time.x,right_time.x)
    ) %>% 
    rename(
      left_time = left_time.y,
      right_time = right_time.y
    ) %>% 
    mutate(
      rt_observed = rt_norm*(right_time-left_time)+left_time,
      rt_predicted = rt_pred*(right_time-left_time)+left_time,
      rt_fit = fit*(right_time-left_time)+left_time,
      rt_lwr = lwr*(right_time-left_time)+left_time,
      rt_upr = upr*(right_time-left_time)+left_time
    ) ->output_prediction_rt_test_sa_result
}

#DG
{
  i=1
  output_prediction_rt_test_dg_result <- tibble()
  for (i in 1:12){
    output_prediction_rt_test_dg <- read_tsv(
      paste0(folder_alphapeptdeep,"output_rt_testing_dg_",i,".tsv")
    )[,-1] %>% 
      arrange(rt_norm) %>%
      mutate(file_series = i)
    
    fit_rt_training <- lm(rt_norm ~ rt_pred, data =output_prediction_rt_training)
    
    output_prediction_rt_test_dg %>% 
      bind_cols(
        predict(fit_rt_training, interval = "prediction", level =0.95, newdata = output_prediction_rt_test_dg)
      )->output_prediction_rt_test_dg
    
    
    output_prediction_rt_test_dg_result %>% 
      bind_rows(
        output_prediction_rt_test_dg
      ) -> output_prediction_rt_test_dg_result
  }
  
  output_prediction_rt_test_dg_result %>% 
    arrange(
      spec_idx
    ) %>% 
    mutate(
      rt_test = if_else(rt_norm > lwr & rt_norm < upr, 1, 0)
    ) %>% 
    left_join(
      file_raw_index2,
      join_by(file_series)
    ) %>% 
    select(
      -c(left_time.x,right_time.x)
    ) %>% 
    rename(
      left_time = left_time.y,
      right_time = right_time.y
    ) %>% 
    mutate(
      rt_observed = rt_norm*(right_time-left_time)+left_time,
      rt_predicted = rt_pred*(right_time-left_time)+left_time,
      rt_fit = fit*(right_time-left_time)+left_time,
      rt_lwr = lwr*(right_time-left_time)+left_time,
      rt_upr = upr*(right_time-left_time)+left_time
    ) ->output_prediction_rt_test_dg_result
}
```

## Fig 2i + K, SA, DG, > summary, figure
```{r paged.print=FALSE}
output_prediction_rt_train_result %>% 
  mutate(
    aa_replace = "R"
  ) %>% 
  bind_rows(
    output_prediction_rt_test_result %>% 
      mutate(
        aa_replace = "GV"
      ),
    output_prediction_rt_test_k_result %>% 
      mutate(
        aa_replace = "K"
      ),
    output_prediction_rt_test_sa_result %>% 
      mutate(
        aa_replace = "SA"
      ),
    output_prediction_rt_test_dg_result %>% 
      mutate(
        aa_replace = "DG"
      )
  ) -> output_prediction_rt_test_merged_result

output_prediction_rt_test_merged_result %>% 
  mutate(
    fit_dev = rt_upr-rt_fit,
    pred_dev = rt_observed-rt_predicted,
    pred_fit_dev = pred_dev - rt_fit,
    aa_replace = fct(aa_replace, levels = c("R","K","SA","DG","GV"))
  ) %>% 
  summarise(
    mean_fit_dev=mean(fit_dev)
  ) %>% pull(mean_fit_dev) -> mean_fit_Dev

output_prediction_rt_test_merged_result %>% 
  mutate(
    fit_dev = upr-fit,
    pred_dev = rt_pred-rt_norm,
    pred_fit_dev = pred_dev - fit,
    aa_replace = fct(aa_replace, levels = c("R","K","SA","DG","GV"))
  ) %>% 
  write_tsv(
    "./export/output_prediction_rt_test_merged_result_aa_replace.tsv"
  )

output_prediction_rt_test_merged_result %>% 
  mutate(
    fit_dev = upr-fit,
    pred_dev = rt_pred-rt_norm,
    pred_fit_dev = pred_dev - fit,
    aa_replace = fct(aa_replace, levels = c("R","K","SA","DG","GV"))
  ) %>% 
  filter(
    pred_dev >= fit_dev
  ) %>% 
  summarize(
    .by = aa_replace,
    count = n()
  ) %>% 
  mutate(
    count2 = 17669 - count
  )%>% 
  write_tsv(
    "./export/output_prediction_rt_test_merged_result_aa_replace_summary.tsv"
  )

output_prediction_rt_test_merged_result %>% 
  mutate(
    fit_dev = rt_upr-rt_fit,
    pred_dev = rt_observed-rt_predicted,
    pred_fit_dev = pred_dev - rt_fit,
    aa_replace = fct(aa_replace, levels = c("R","K","SA","DG","GV"))
  ) %T>% 
  # ) select(
  #   fit_dev, pred_dev, pred_fit_dev, aa_replace
  # )% T>% 
  write_tsv(
    "./figures/fig2i.tsv"
  ) %>% 
  ggplot(
    aes(x= pred_dev, color = aa_replace)
  )+
  stat_ecdf(
    #alpha = 0.95
  )+
  geom_vline(
    aes(xintercept = -mean_fit_Dev),
    color = "black", linetype = "dashed"
  )+
  scale_color_manual(
    values = c(
      "R"=RColorBrewer::brewer.pal(9,"Set1")[1],
      "K"=RColorBrewer::brewer.pal(9,"Set1")[2],
      "SA"=RColorBrewer::brewer.pal(9,"Set1")[3],
      "DG"=RColorBrewer::brewer.pal(9,"Set1")[4],
      "GV"=RColorBrewer::brewer.pal(9,"Set1")[5]
    )
  )+
  labs(
    x=expression(paste(italic(Delta),RT,"(Obs.-Pred.) (min)")),
    y="Cumulative Distribution",
    Color = "AA Replaced"
  )+
  theme_classic()+
  theme(
    #legend.position = "none",
    legend.title = element_blank(),
    text= element_text(color = "black", size = 7),
    axis.text.y = element_text(color = "black", size = 7, hjust=1),
    axis.text.x = element_text(color = "black", size = 7),
    axis.title = element_text(size=7),
    plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm"),
    legend.position=c(.8,.25),
    legend.margin = margin(unit = "pt"),
    legend.key.height = unit(-5.0,unit= "pt"),
    legend.key.spacing =unit(-1.0,unit= "pt")
  )
ggsave(paste0("./figures/rt_aa_replace.png"), width=4.5, height = 4.5, units = "cm", dpi = 600)
  
  summarize(
    .by = aa_replace,
    avg_fit_dev = mean(pred_dev)
  )
  
  wes_palette("AsteroidCity1",n=5)
  wes_palette()
  RColorBrewer::display.brewer.all()
  RColorBrewer::brewer.pal(9,"Set1")
```

#Fig. 2j
```{r}
summaryfile_psm_for_testing3_pcc_rt_hfsm %>% 
  distinct(set) %>% pull(set) -> set_vector

summaryfile_psm_for_testing3_pcc_rt_hfsm %>% 
  summarize(
    .by = set,
    experiment = first(experiment),
    replicate = first(replicate),
    enzyme = first(enzyme),
    count = n(),
    rt_check = sum(rt_check)
  )

summaryfile_psm_for_testing3_pcc_rt_hfsm %>% 
  summarize(
    .by = set,
    experiment = first(experiment),
    replicate = first(replicate),
    enzyme = first(enzyme),
    count = n(),
    rt_check = sum(rt_check)
  ) %>% pull(set) -> set_vector

i=1 



paste0(
  summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
    summarize(
      .by = set,
      experiment = first(experiment),
      replicate = first(replicate),
      enzyme = first(enzyme),
      count = n(),
      rt_check = sum(rt_check)
    ) %>% 
    filter(
      set == set_vector[i]
    ) %>% 
    pull(rt_check),
  "/",
  summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
    summarize(
      .by = set,
      experiment = first(experiment),
      replicate = first(replicate),
      enzyme = first(enzyme),
      count = n(),
      rt_check = sum(rt_check)
    ) %>% 
    filter(
      set == set_vector[i]
    ) %>% 
    pull(count)
) -> count_for_rt

summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  filter(
    set == set_vector[1]
  ) %>% 
  mutate(
    rt_norm = (right_time - left_time)* rt_norm + left_time,
    rt_pred = (right_time - left_time)* rt_pred + left_time,
    fit = (right_time - left_time)* fit + left_time,
    lwr = (right_time - left_time)* lwr + left_time,
    upr = (right_time - left_time)* upr + left_time
  ) %>%
  ggplot(aes(x=rt_norm, y=rt_pred))+
  geom_point(
    aes(color = fct(as.character(rt_check),levels =c("0","1"))),
    size=0.1
  )+
  annotate(
    "text",x=-Inf,y=Inf,hjust=-0.2,vjust=2,
    label=paste0("Passed = ",count_for_rt),size =2
  )+
  geom_line(aes(x=lwr), color = "red", linetype = "dashed")+
  geom_line(aes(x=upr), color = "red", linetype = "dashed")+
  #geom_smooth(method=lm, se=TRUE)+
  #lims(x=c(0,1),y=c(0,1))+
  scale_color_manual(
    values = c("black","red")
  )+
  labs(
    x="Observed RT (min)",
    y="Predicted RT (min)"
  )+
  #lims(x=c(30,140),y=c(30,140))+
  theme_classic2()+
  theme(
  legend.position = "none",
  #axis.title.x = element_blank(),
  axis.title = element_text(color = "black",size = 7),
  #axis.text.x = element_blank(),
  axis.text = element_text(color = "black",size = 7),
  plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
)
ggsave(
  paste0("./figures/fig2j.png"),width=4.5,height=4.5,dpi = 600,units="cm"
)

```

#Fig. 2k
```{r}
summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  mutate(
    rt_deviation = rt_norm-rt_pred,
    rt_deviation = rt_deviation*(right_time- left_time),
    rt_test = case_when(
      rt_deviation > 0 & rt_norm > upr ~ "increase",
      rt_deviation < 0 & rt_norm < lwr ~ "decrease",
      .default = "under_t95"
    )
  ) %>% 
  select(
    index, rt_deviation, rt_test
  ) %T>% 
  write_tsv(
    "./figures/fig2k.tsv"
  ) %>% 
  ggpubr::gghistogram(
    x = "rt_deviation",
    #add="median",
    fill = "rt_test",
    position = "stack",
    size = 0.1
  )+
  labs(
    x=expression(paste(italic(Delta),RT,"(Obs.-Pred.) (min)")),
    y="PSM count",
    fill = "RT prediction"
    #color = "RT prediction"
  )+
  scale_fill_manual(
    labels = c("Decrease","Increase",expression(" "*Under~Delta*t[95*"%"])),
    values = c("grey","grey","red")
  )+
  theme(
    legend.position = "none",
    axis.title = element_text(color = "black",size = 7),
    axis.text = element_text(color = "black",size = 7),
    plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
  )
ggsave("./figures/fig2k.png",width =4.5,height = 4.5, dpi = 600, units = "cm")
```

#Fig. 2l
```{r}
summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered %>% 
  filter(
    pcc_check ==1
  ) %>%
  select(
    index,`Delta M in ppm`,rt_check
  ) %>% filter(
    rt_check  == 1
  ) %T>% 
  write_tsv(
    "./figures/fig2l_rt_passed.tsv"
  ) %>% 
  pull(`Delta M in ppm`) -> a

summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered %>% 
  filter(
    pcc_check ==1
  ) %>%
  select(
    index,`Delta M in ppm`,rt_check
  ) %>% filter(
    rt_check  == 0
  ) %T>% 
  write_tsv(
    "./figures/fig2l_rt_failed.tsv"
  ) %>% 
  pull(`Delta M in ppm`) -> b

# KS test
ks.test(a,b)

summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered %>% 
  # dplyr::filter(
  #   !(gene_position %in% str_replace(table_gene_position$gene_position,"\\|","_"))
  # ) %>%
  filter(
    pcc_check ==1
  ) %>%
  select(
    `Delta M in ppm`,rt_check
  ) %>%
  mutate(
    rt_check = fct(as.character(rt_check))
  ) %>% 
  ggplot(
    aes(x=`Delta M in ppm`,color=rt_check)
  )+
  stat_ecdf()+
  #wes_palette("AsteroidCity1",n=5)[3]
  # geom_boxplot(width = 0.5,linewidth = 0.2, outlier.size = 0.2,color = "black")+
  scale_color_manual(
    values = c("1"=wes_palette("AsteroidCity1",n=5)[3],"0"=wes_palette("AsteroidCity1",n=5)[1]),
  )+
  # stat_compare_means(
  #     #comparisons = list(c("rt_check")),
  #     method = "t.test",
  #     method.args = list(var.equal = TRUE),
  #     label.y = 1,
  #     size = 2
  #   )+
  labs(
    x=expression(paste(Precursor," ",italic(Delta),Mass," (ppm)")),
    y="Cumulative Distribution"
  )+
  theme_classic()+
  theme(
    legend.position = "none",
    legend.title = element_blank(),
    text= element_text(color = "black", size = 7),
    axis.text.y = element_text(color = "black", size = 7, hjust=1),
    axis.text.x = element_text(color = "black", size = 7),
    axis.title = element_text(size=7),
    plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
  )
ggsave(paste0("./figures/2_rt_rt_vs_pcc_kstest.png"), width=4.5, height = 4.5, units = "cm", dpi = 600)
```


#Fig. 2m
```{r}
summaryfile_psm_for_testing3_pcc_rt_hfsm %>% 
  mutate(
    b_ion_errors = map_dbl(b_ion_errors,\(x) mean(x)),
    y_ion_errors = map_dbl(y_ion_errors,\(x) mean(x))
  ) %>% 
  select(
    index,b_ion_errors,y_ion_errors
  ) %T>% 
  write_tsv(
    "./figures/fig2m.tsv"
  ) %>% 
  ggplot(
    aes(x=b_ion_errors*1000,y=y_ion_errors*1000)
  )+
  geom_pointdensity(adjust=5,size = 0.25)+
  scale_color_viridis()+
  scale_y_continuous(
    limits = c(-50,50)
  )+
  scale_x_continuous(
    limits = c(-50,50)
  )+
  labs(
    x="b-ion Errors (mDa)",
    y="y-ion Errors (mDa)",
    color = "Number of Neighbors"
  )+
  theme_bw()+
  theme(
    legend.frame = element_rect(linewidth = 0.2),
    legend.position = c(.5,.85),
    legend.direction = "horizontal",
    legend.title.position = "top",
    legend.text = element_text(color="black",size=7),
    legend.title = element_text(color="black",size=7),
    axis.text = element_text(color="black",size=7),
    axis.title = element_text(size=7)
  )
ggsave("./figures/fig2m.png",width=4.5,height=4.5,dpi = 600,units="cm")
```
#Fig. 2o
```{r}
summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>%
  mutate(
    b_y_ttest_check = fct(as.character(b_y_ttest_check)),
  ) %>% 
  select(
    index,b_y_ttest,b_y_ttest_check
  ) %T>% 
  write_tsv(
    "./figures/fig2o.tsv"
  ) %>% 
  gghistogram(
    x = "b_y_ttest", 
    add = "median", rug = TRUE,
    fill = "b_y_ttest_check", palette = c("#9E0142", "#5E4FA2"),
    binwidth = 0.025,
    position = "stack",
    size = 0.25
  )+
  labs(x=expression(italic(P)-value),y="Count")+
  #scale_x_continuous(limits = c(-0.05,0.05))+
  theme(
    legend.position = "none",
    #axis.title.x = element_blank(),
    axis.title = element_text(color = "black",size = 7),
    #axis.text.x = element_blank(),
    axis.text = element_text(color = "black",size = 7),
    plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
  )
ggsave("./figures/2_05_masserror_all.png",width=4.5,height=4.5, units = "cm",dpi = 600)
```


#Fig. 3a
```{r}
summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered %>% 
  select(
    gene_position,index,pcc_check,rt_check,b_y_ttest_check
  ) %>% 
  write_tsv(
    "./figures/fig3a.tsv"
  )

ggVennDiagram(
  list(
    # A=summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
    #   filter(p1r_check ==1 | p2gv_check ==1) %>% 
    #   pull(index),
    B=summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered %>% 
      filter(pcc_check == 1) %>% 
      pull(index),
    C=summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered %>% 
      filter(rt_check == 1) %>% 
      pull(index),
    D=summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered %>% 
      filter(b_y_ttest_check == 1) %>% 
      pull(index)
  ),
  category.names = c("MS2","RT","MET"),
  set_size = 4
)+
  theme_void() +
  scale_fill_distiller(palette = "Reds",direction=1)+
  scale_color_manual(
    values = c("black","black","black")
  )+
  coord_sf(clip="off")+
  theme(
    legend.position = "none",
    plot.margin = margin(rep(0.5,4),unit="cm")
  )
ggsave("./figures/3_01_venn.png",width = 10, height = 10, units = "cm",dpi=600)
```

#Fig. 3b
```{r}
arginylome_validation_matrix3_sequence_distinct %>% 
  mutate(
    trinity = if_else(score_sum==3,TRUE,FALSE)
  ) %>% 
  select(
    prot_pos_reposition,Sequence,pcc_check,rt_check,,score_sum,MOCK,MG132,MGTG
  )
  write_tsv(
    "./figures/fig3b.tsv"
  ) %>% 
  dplyr::select(trinity,MOCK,MG132,MGTG) %>% 
  pivot_longer(c(MOCK,MG132,MGTG)) %>% 
  summarise(
    .by = c(name,trinity),
    count = sum(value)
  ) %>% 
  ggplot(
    aes(x=fct(name,level = c("MOCK","MG132","MGTG")),y=count,fill=trinity)
  )+
  geom_bar(stat="identity",color="black")+
  geom_text(aes(label=count),position = position_stack(vjust=0.5),size=3)+
  scale_x_discrete(
    label = c("MOCK","MG132","MG132 + TG")
  )+
  scale_fill_manual(
    values = c(wesanderson::wes_palette("Royal1")[2],wesanderson::wes_palette("Royal1")[3])
  )+
  labs(x="Experiment",y="PSM Count",fill="TrinityNmod")+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.text = element_text(color="black")
  )
ggsave("./figures/3_02_removed_arg_drug_model.png",width=8,height=8, units = "cm",dpi = 600)
```



#Fig. 3d
```{r}
summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  mutate(
    trinity = if_else(dl_score == 3,1,0)
  ) %>% 
  mutate(
    trinity_failed = if_else(dl_score != 3,1,0)
  ) %>%
  select(
    index,diagnostic_ion_int_relative,trinity_failed,pcc_check,rt_check,b_y_ttest_check,trinity
  ) %>% 
  mutate(
    diagnostic_ion_int_relative = replace_na(diagnostic_ion_int_relative,0)
  ) %>% 
  pivot_longer(
    trinity_failed:trinity
  ) %>% 
  filter(value == 1) %T>% 
  write_tsv(
    "./figures/3_05_diagnostic_tests.tsv"
  ) %>% 
  ggplot(
    aes(x=fct(name,levels = c("trinity_failed","pcc_check","rt_check","b_y_ttest_check","trinity")),y=diagnostic_ion_int_relative)
  )+
  geom_violin(
    scale = "width",
    aes(fill = fct(name,levels = c("trinity_failed","pcc_check","rt_check","b_y_ttest_check","trinity"))),
    linewidth = 0.25
  )+
  geom_boxplot(width = 0.2,outlier.size = 0.25,linewidth = 0.25)+
  scale_y_continuous(labels=label_percent())+
  scale_x_discrete(
    labels = c("None","PCC","RT","MET","All")
  )+
  scale_fill_manual(
    values = wes_palette("Darjeeling1",5,type="discrete")
  )+
  stat_compare_means(
    comparisons = list(c("pcc_check","trinity"),c("rt_check","trinity"),c("b_y_ttest_check","trinity")), label.y = c(0.9,0.8,0.7),
    p.adjust.methods="fdr",
    size = 2
  )+
  labs(
    x="Filtering Module",y="Diagnostic Ion Intensity %"
  )+
  scale_y_continuous(
    breaks = c(0,0.25,0.5,0.75,1),
    limits = c(0,1)
  )+
  theme_classic2()+
  theme(
    legend.position = "none",
    #axis.title.x = element_blank(),
    axis.title = element_text(color = "black",size = 7),
    #axis.text.x = element_blank(),
    axis.text = element_text(color = "black",size = 7),
    plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
  )
ggsave("./figures/3_05_diagnostic_tests.png",width = 4.5, height = 4.5, units = "cm",dpi=600)
```

#Fig. 3e
```{r}
summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered %>% 
  distinct(Sequence,.keep_all = TRUE) %>% #339
  filter(
    score_sum == 3
  ) %>% 
  mutate(
    p5p5prime = str_replace(p5p5prime,"(?<=.....).","X")
  ) %>% 
  select(
    index,p5p5prime
  ) %T>% 
  write_tsv(
    "./figures/figure3e.tsv"
  ) %>% 
  pull(p5p5prime) %>% 
  ggseqlogo(
  )+
  theme(
    legend.position = "none"
  ) -> fig_logo
  
fig_logo$scales$scales[[1]]$labels <- c("P5","P4","P3","P2","P1","P1'","P2'","P3'","P4'","P5'")
fig_logo
ggsave("./figures/figure3e.png",width = 8,height = 8, units = "cm", dpi = 600)
  
summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered %>% 
  distinct(Sequence,.keep_all = TRUE) %>% #339
  filter(
    score_sum != 3
  ) %>% 
  mutate(
    p5p5prime = str_replace(p5p5prime,"(?<=.....).","X")
  ) %>% 
  select(
    index,p5p5prime
  ) %>% 
  write_tsv(
    "./figures/figure3e_2.tsv"
  ) %>%
  pull(p5p5prime) %>% 
  ggseqlogo(
  )+
  theme(
    legend.position = "none"
  ) -> fig_logo
  
fig_logo$scales$scales[[1]]$labels <- c("P5","P4","P3","P2","P1","P1'","P2'","P3'","P4'","P5'")
fig_logo
ggsave("./figures/figure3e_2.png",width = 8,height = 8, units = "cm", dpi = 600)
```


#Fig. 3f
```{r}
alphafold_fetched_tidied2 %>% 
  write_tsv(
    "./figures/alphafold.tsv"
  )

alphafold_fetched_tidied2 %>% 
  dplyr::filter(score_sum == 3) %>% 
  write_tsv(
    "./figures/3_02_alphafold_mlfitered.tsv"
  ) %>% 
  ggplot(
    aes(
      x=fct(as.character(mod_position)),
      y=prediction_score,
      fill = fct(as.character(mod_position))
    )
  )+
  geom_boxplot(
    linewidth = 0.25
  )+
  lims(y=c(20,100))+
  labs(
    x = "Arginylation Position", y = "AlphaFold pLDDT score"
  )+
  scale_x_discrete(
    labels = c(
      "-10","",
      "-8","",
      "-6","",
      "-4","",
      "-2","",
      "0","",
      "2","",
      "4","",
      "6","",
      "8","",
      "10"
    )
  )+
  theme_classic()+
  theme( 
    legend.position = "none",
    axis.title = element_blank(),
    #axis.title = element_text(color = "black",size = 7),
    #axis.text.x = element_blank(),
    axis.text = element_text(color = "black",size = 7),
    plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
  )
ggsave("./figures/3_02_alphafold_mlfitered.png",width=4.5,height=4.5,dpi = 600,units="cm")

alphafold_fetched_tidied2 %>% 
  dplyr::filter(score_sum != 3) %>% 
  write_tsv(
    "./figures/3_02_alphafold_mlfitered_not.tsv"
  ) %>% 
  ggplot(
    aes(
      x=fct(as.character(mod_position)),
      y=prediction_score,
      fill = fct(as.character(mod_position))
    )
  )+
  geom_boxplot(
    linewidth = 0.25,
    outlier.size = 0.25
  )+
  lims(y=c(20,100))+
  labs(
    x = "Arginylation Position", y = "AlphaFold pLDDT score"
  )+
  scale_x_discrete(
    labels = c(
      "-10","",
      "-8","",
      "-6","",
      "-4","",
      "-2","",
      "0","",
      "2","",
      "4","",
      "6","",
      "8","",
      "10"
    )
  )+
  theme_classic()+
  theme( 
    legend.position = "none",
    axis.title = element_blank(),
    #axis.title = element_text(color = "black",size = 7),
    #axis.text.x = element_blank(),
    axis.text = element_text(color = "black",size = 7),
    plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
  )
ggsave("./figures/3_02_alphafold_mlfitered_not.png",width=4.5,height=4.5,dpi = 600,units="cm")

```
# Fig. 4a
```{r}
arginylome_validation_matrix3_sequence_distinct %>% 
  filter(score_sum == 3) %>%
  select(
    prot_pos_master,prot_pos_reposition,MOCK,MG132,MGTG,score_sum
  ) %>% 
  write_tsv(
    "./figures/fig4a.tsv"
  )
  
ggVennDiagram(
  list(
    # A=summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
    #   filter(p1r_check ==1 | p2gv_check ==1) %>% 
    #   pull(index),
    B=arginylome_validation_matrix3_sequence_distinct %>% 
      filter(MOCK >0 & score_sum == 3) %>% pull(prot_pos_master),
    C=arginylome_validation_matrix3_sequence_distinct %>% 
      filter(MG132 >0 & score_sum == 3) %>% pull(prot_pos_master),
    D=arginylome_validation_matrix3_sequence_distinct %>% 
      filter(MGTG >0 & score_sum == 3) %>% pull(prot_pos_master)
  ),
  category.names = c("MOCK","MG132","MGTG"),
  set_size = 4
)+
  theme_void() +
  scale_fill_distiller(palette = "Reds",direction=1)+
  scale_color_manual(
    values = c("black","black","black")
  )+
  coord_sf(clip="off")+
  theme(
    legend.position = "none",
    plot.margin = margin(rep(0.5,4),unit="cm")
  )
ggsave("./figures/3_01_venn_sites.png",width = 10, height = 10, units = "cm",dpi=600)
```


# Fig. 4b
```{r}
arginylome_validation_matrix3_sequence_distinct_trinity %>% 
  filter(MOCK >0) %>% pull(gene) -> go_input
as_tibble(AnnotationDbi::select(org.Hs.eg.db,keys=go_input, columns=c("SYMBOL","ENTREZID"),keytype="SYMBOL")) %>% 
  pull(ENTREZID) -> pa_input

enrichPathway(
  pa_input,
  readable = TRUE,
  pvalueCutoff = 0.05
) %>% .@result %>%  arrange(qvalue) -> pa_enriched_mock

arginylome_validation_matrix3_sequence_distinct_trinity %>% 
  filter(MG132 >0) %>% pull(gene) -> go_input
as_tibble(AnnotationDbi::select(org.Hs.eg.db,keys=go_input, columns=c("SYMBOL","ENTREZID"),keytype="SYMBOL")) %>% 
  pull(ENTREZID) -> pa_input

enrichPathway(
  pa_input,
  readable = TRUE,
  pvalueCutoff = 0.05
) %>% .@result %>%  arrange(qvalue) -> pa_enriched_mg

arginylome_validation_matrix3_sequence_distinct_trinity %>% 
  filter(MGTG >0) %>% pull(gene) -> go_input
as_tibble(AnnotationDbi::select(org.Hs.eg.db,keys=go_input, columns=c("SYMBOL","ENTREZID"),keytype="SYMBOL")) %>% 
  pull(ENTREZID) -> pa_input

enrichPathway(
  pa_input,
  readable = TRUE,
  pvalueCutoff = 0.05
) %>% .@result %>%  arrange(qvalue) -> pa_enriched_mgtg

pa_enriched_mock %>% 
  mutate(
    experiment = "MOCK"
  ) %>% 
  bind_rows(
    pa_enriched_mg %>% 
      mutate(
        experiment = "MG132"
      )
  )%>% 
  bind_rows(
    pa_enriched_mgtg %>% 
      mutate(
        experiment = "MGTG"
      )
  ) -> pa_enriched_all

pa_enriched_all %>% 
  mutate(
    Description = str_replace(Description,"(?<=.{10}[:blank:]in)[:blank:]","\n"),
    Description = str_replace(Description,"(?<=.{15}[:blank:]by)[:blank:]","\n"),
    Description = str_replace(Description,"\\(ATF6\\-alpha\\)[:blank:]",""),
  ) %>% 
  select(ID,Description,experiment,pvalue) %>% 
  pivot_wider(
    id_cols = c(ID,Description),
    names_from = experiment,
    values_from = pvalue
  ) %>% 
  mutate(
    all = MOCK*MG132*MGTG
  ) %>% 
  arrange(all) %>% 
  slice_head(n=10) %>% pull(Description) -> pa_description

pa_enriched_all %>% 
  mutate(
    Description = str_replace(Description,"(?<=.{10}[:blank:]in)[:blank:]","\n"),
    Description = str_replace(Description,"(?<=.{15}[:blank:]by)[:blank:]","\n"),
    Description = str_replace(Description,"\\(ATF6\\-alpha\\)[:blank:]",""),
  ) %>%
  select(ID,Description,experiment,pvalue) %>% 
  pivot_wider(
    id_cols = c(ID,Description),
    names_from = experiment,
    values_from = pvalue
  ) %>%
  filter(
    Description %in% pa_description
  ) %>%
  pivot_longer(
    MOCK:MGTG
  ) %>% 
  arrange(value) -> pa_enriched_all_fig

pa_enriched_all_fig %T>% 
  write_tsv(
    "./figures/4_11_tile_RA_all_main_legend.tsv"
  ) %>% 
  ggplot(
    aes(x=fct(name,levels=c("MOCK","MG132","MGTG")),y=fct(Description,levels = rev(pa_description)),fill = -log(value,10))
  )+
  geom_tile()+
  scale_fill_distiller(
    palette = "YlOrRd",
    direction = 1,
    na.value = "grey80"
  )+
  labs(
    x="Experiment",
    y="Reactome",
    fill = "Q value"
  )+
  theme_bw()+
  theme(
    axis.text.x = element_text(color = "black",size= 7,angle = 45, hjust=1),
    axis.text.y =element_text(color = "black",size= 6),
    axis.title = element_text(color = "black",size= 7),
    plot.title = element_text(color = "black",size= 7),
    legend.position = "none",
    axis.ticks = element_line(color = "black"),
    legend.title = element_text(color = "black",size= 7),
    legend.text = element_text(color = "black",size= 7)
  )
ggsave(
  "./figures/4_11_tile_RA_all_main_legend.png",height = 5, width =6,dpi = 600,units = "cm"
)


```


# Fig. 4d
```{r}
peptide_lfq_trinity %>% 
  pivot_longer(MG132_1_Free:MOCK_2_Arg) %>% 
  drop_na(value) %>% 
  mutate(
    experiment = str_split_i(name,"_",1),
    arg = str_split_i(name,"_",3),
    protease = if_else(!is.na(cleavage_type),"T","F")
  ) %>% 
  pivot_wider(
    id_cols = c(Sequence:cleavage_name,arg,protease),
    names_from = experiment,
    values_from = value,
    values_fn = \(x) mean(x)
  ) %>% 
  mutate(
    MGTG_MOCK = MGTG-MOCK,
    MGTG_MG132 = MGTG-MG132
  ) %>% 
  select(-c(MG132,MGTG,MOCK)) %>% 
  pivot_longer(
    MGTG_MOCK:MGTG_MG132
  ) %>% 
  filter(
    name == "MGTG_MG132"
  ) %T>% 
  write_tsv(
    "./figures/fig4d.tsv"
  ) %>% 
  ggplot(
    aes(x=protease,y=value,fill=protease)
  )+
  geom_violin(linewidth = 0.2,scale="width")+
  geom_boxplot(width = 0.1,linewidth = 0.2,outlier.size = 0)+
  # facet_grid(
  #   cols=vars(protease),
  #   rows = vars(arg)
  # )+
  
  scale_fill_manual(
    values =c(wesanderson::wes_palette(4,name="GrandBudapest1",type="discrete")[c(1,2)])
  )+
  scale_x_discrete(
    labels = c("False","True")
  )+
  labs(x="Cleavage", y=bquote(~Delta*Z-Score~(MGTG-MG132)))+
  stat_compare_means(
    comparisons = list(c("T","F")),
    label = "p.format",
    method="t.test",
    #label.y = c(4,4.8,4.3),
    size = 2.5
  )+
  lims(
    y=c(-2,2.5)
  )+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.title = element_text(size=7),
    axis.text = element_text(size=6,color = "black"),
    strip.text = element_text(size=6)
  )
ggsave(
  "./figures/fig4d.png",width=4,height=4,dpi = 600,units="cm"
)
  
peptide_lfq_trinity %>% 
  pivot_longer(MG132_1_Free:MOCK_2_Arg) %>% 
  drop_na(value) %>%
  mutate(
    experiment = str_split_i(name,"_",1),
    arg = str_split_i(name,"_",3),
    protease = if_else(!is.na(cleavage_type),TRUE,FALSE)
  ) %>% 
  filter(arg == "Arg") %>% 
  filter(protease == FALSE) %>% 
  ggplot(
    aes(x= factor(experiment, levels = c("MOCK","MG132","MGTG")), y = value, fill = factor(experiment, levels = c("MOCK","MG132","MGTG")))
  )+
  geom_violin(linewidth = 0.2,scale="width")+
  geom_boxplot(width = 0.1,linewidth = 0.2,outlier.size = 0)+
  labs(x="Experiments", y="Z-score",fill="name")+
  stat_compare_means(
    comparisons = list(c("MOCK","MG132"),c("MOCK","MGTG"),c("MG132","MGTG")),
    label = "p.signif",
        method="t.test",
        #label.y = c(2,2.7,3.4),
        size = 2
  )+
  scale_fill_manual(
    values =c(wesanderson::wes_palette(5,name="Zissou1",type="discrete")[c(1,3,5)]),
    labels = c("MOCK","MG132","MGTG")
  )+
  lims(
    y=c(-3.1,5.5)
  )+
  theme_classic2()+
  labs(x="Experiments", y="Z-score")+
  theme(
    legend.position = "none",
    axis.title = element_text(size=7),
    axis.text = element_text(size=6,color = "black"),
    strip.text = element_text(size=6)
  )


```

# Fig. 4e-g
```{r}
peptide_lfq_trinity_distinct_arg %>% 
  mutate(
    signal = if_else(gene_position %in% gene_position_signal, TRUE, FALSE),
    caspase3 = if_else(gene_position %in% gene_position_casp3, TRUE, FALSE),
    transit = if_else(gene_position %in% gene_position_transit, TRUE, FALSE),
  ) %>% 
  write_tsv(
    "./figures/fig4e_g.tsv"
  )
```

##caspase-3
```{r}
peptide_lfq_trinity_distinct_arg %>% 
  filter(
    gene_position %in% gene_position_casp3
  ) %>% 
  pivot_longer(MG132:MOCK) %>% 
  ggplot()+
  aes(x= factor(name, levels = c("MOCK","MG132","MGTG")), y = value, fill = factor(name, levels = c("MOCK","MG132","MGTG")))+
  geom_violin(linewidth = 0.2)+
  geom_boxplot(width = 0.1,linewidth = 0.2,outlier.size = 0)+
  stat_compare_means(
    comparisons = list(c("MOCK","MG132"),c("MG132","MGTG"),c("MOCK","MGTG")),
    label = "p.signif",
    method="t.test",
    #label.y = c(2,2.7,3.4),
    size = 2
  )+
  labs(x="Experiments", y="Z-score")+
  scale_fill_manual(values =c(wes_palette("Zissou1",5)[c(1,3,5)]))+
  lims(y = c(-2,3))+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.title = element_text(size=7),
    axis.text = element_text(size=6,color = "black"),
    strip.text = element_text(size=6)
  )
ggsave("./figures/4_06_cleavage_violin_casp3.png",width=4,height=4,dpi = 600,units="cm")
```

## signal
```{r}
peptide_lfq_trinity_distinct_arg %>% 
  filter(
    gene_position %in% gene_position_signal
  ) %>% 
  pivot_longer(MG132:MOCK) %>% 
  ggplot()+
  aes(x= factor(name, levels = c("MOCK","MG132","MGTG")), y = value, fill = factor(name, levels = c("MOCK","MG132","MGTG")))+
  geom_violin(linewidth = 0.2)+
  geom_boxplot(width = 0.1,linewidth = 0.2,outlier.size = 0)+
  stat_compare_means(
    comparisons = list(c("MOCK","MG132"),c("MG132","MGTG"),c("MOCK","MGTG")),
    label = "p.signif",
    method="t.test",
    #label.y = c(2,2.7,3.4),
    size = 2
  )+
  labs(x="Experiments", y="Z-score")+
  scale_fill_manual(values =c(wes_palette("Zissou1",5)[c(1,3,5)]))+
  lims(y = c(-2,3))+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.title = element_text(size=7),
    axis.text = element_text(size=6,color = "black"),
    strip.text = element_text(size=6)
  )
ggsave("./figures/4_06_cleavage_violin_signal.png",width=4,height=4,dpi = 600,units="cm")
```

##transit
```{r}
peptide_lfq_trinity_distinct_arg %>% 
  filter(
    gene_position %in% gene_position_transit
  ) %>% 
  pivot_longer(MG132:MOCK) %>% 
  ggplot()+
  aes(x= factor(name, levels = c("MOCK","MG132","MGTG")), y = value, fill = factor(name, levels = c("MOCK","MG132","MGTG")))+
  geom_violin(linewidth = 0.2)+
  geom_boxplot(width = 0.1,linewidth = 0.2,outlier.size = 0)+
  stat_compare_means(
    comparisons = list(c("MOCK","MG132"),c("MG132","MGTG"),c("MOCK","MGTG")),
    label = "p.signif",
    method="t.test",
    #label.y = c(2,2.7,3.4),
    size = 2
  )+
  labs(x="Experiments", y="Z-score")+
  scale_fill_manual(values =c(wes_palette("Zissou1",5)[c(1,3,5)]))+
  lims(y = c(-2,3))+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.title = element_text(size=7),
    axis.text = element_text(size=6,color = "black"),
    strip.text = element_text(size=6)
  )
ggsave("./figures/4_06_cleavage_violin_transit.png",width=4,height=4,dpi = 600,units="cm")

peptide_lfq_trinity_distinct_arg %>% 
  filter(
    gene_position %in% gene_position_casp6
  ) %>% 
  pivot_longer(MG132:MOCK) %>% 
  ggplot()+
  aes(x= factor(name, levels = c("MOCK","MG132","MGTG")), y = value, fill = factor(name, levels = c("MOCK","MG132","MGTG")))+
  geom_violin(linewidth = 0.2)+
  geom_boxplot(width = 0.1,linewidth = 0.2,outlier.size = 0)+
  stat_compare_means(
    comparisons = list(c("MOCK","MG132"),c("MG132","MGTG"),c("MOCK","MGTG")),
    label = "p.signif",
    method="t.test",
    #label.y = c(2,2.7,3.4),
    size = 2
  )+
  labs(x="Experiments", y="Z-score")+
  scale_fill_manual(values =c(wes_palette("Zissou1",5)[c(1,3,5)]))+
  lims(y = c(-2,3))+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.title = element_text(size=7),
    axis.text = element_text(size=6,color = "black"),
    strip.text = element_text(size=6)
  )
ggsave("./figures/4_06_cleavage_violin_casp6.png",width=4,height=4,dpi = 600,units="cm")
```


# Fig. 4i
##SHMT2
```{r}
#SHMT2
j=125

summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered_trinity$index[j] -> target_scan
summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered_trinity |> 
  dplyr::filter(
    index == target_scan
  ) -> spectrum_file_plot

spectrum_file_plot$sequence_for_fragspec -> title1
spectrum_file_plot$index -> subtitle1 ##index!
round(spectrum_file_plot$PCC,3) -> title2 ##pcc
spectrum_file_plot$`MHplus in Da` -> spec_plot_xmax
spectrum_file_plot$gene_position -> title3

spectrum_file_plot %>% select(peak_table_for_graph) %>%
  unnest(cols=peak_table_for_graph) %>% filter(
    !is.na(matches)
  ) %>% 
  arrange(desc(frag)) %>% 
  slice_head(n=1) %>% 
  pull(frag)->graph_frag_max

spectrum_file_plot %>% select(peak_table_for_graph) %>%
  unnest(cols=peak_table_for_graph) %>% filter(
    !is.na(matches)
  ) %>% 
  arrange(desc(`m/z`)) %>% 
  slice_head(n=1) %>% 
  pull(`m/z`) -> spec_plot_xmax
#summary_filtered_PRM_table_final_DL_library_merged_spec_DLspec_crossed$pearson_correl_coeff[j] |> round(digits = 4) -> subtitle2
#summary_filtered_PRM_table_final_DL_library_merged_spec_DLspec_crossed$cosine_similarity [j] |> round(digits = 4) -> subtitle3
spectrum_file_plot %>% select(peak_table_for_graph) %>%
  unnest(cols=peak_table_for_graph) %>% 
  mutate(
    frag = if_else(frag>=0,frag/graph_frag_max,frag)
  ) %T>% 
  write_tsv(
    "./figures/fig4i_shmt2.tsv"
  ) %>% 
  ggplot( 
    aes(x=`m/z`,y=frag, label = series)
  )+
  geom_bar(stat="identity",width = 0.2)+
  geom_col(aes(fill = series),width = spec_plot_xmax/1000)+
  geom_text(aes(y=if_else(frag<0,frag-0.28,frag),label=ion_type,color= series),angle=90,hjust=-0.05,vjust=0.5,size=1.1, na.rm = TRUE)+
  # ggrepel::geom_text_repel(
  #   size=2,
  #   alpha = 0.2,
  #   color = "black",
  #   angle= 90,
  #   nudge_x = 10,
  #   #nudge_y = 1000,
  #   box.padding = 0.1,
  #   na.rm = TRUE,
  #   direction = "x",
  #   min.segment.length = 0.5,
  #   ylim = c(0.4,0.8)
  # )+
  geom_hline(yintercept = 0, color = "black")+
  scale_fill_manual(
    values = c("b"=RColorBrewer::brewer.pal(n=9,"Set1")[1],"y"=RColorBrewer::brewer.pal(n=9,"Set1")[2]),
    na.value = NA
  )+
  scale_color_manual(
    values = c("b"=RColorBrewer::brewer.pal(n=9,"Set1")[1],"y"=RColorBrewer::brewer.pal(n=9,"Set1")[2]),
    na.value = NA
  )+
  scale_x_continuous(limits=c(0, spec_plot_xmax+100),expand=c(0,0))+ #limits=c(250,800),
  scale_y_continuous(breaks = c(1,0.5,0,-0.5,-1),labels = scales::percent(c(1,0.5,0,0.5,1)), limits=c(-1.4,1.4),expand=c(0,0))+
  theme_classic()+
  labs(x="m/z",y="Normalized Intensity", fill = "Ion Type", color = "Ion Type", title = paste0(title1,"  PCC=",title2))+
  theme(
    legend.position = "none",
    plot.subtitle = element_text(size=8, color="black"),
    axis.text.x = element_text(color = "black",size= 7),
    axis.text.y =element_text(color = "black",size= 7),
    axis.title = element_text(color = "black",size= 8),
    axis.title.y = element_blank(),
    plot.title = element_text(color = "black",size= 7),
    axis.ticks = element_line(color = "black"),
    legend.title = element_text(color = "black",size= 8),
    legend.text = element_text(color = "black",size= 8),
    plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
  )
ggsave(paste0("./figures/shmt2.png"), width=10, height = 3, units = "cm", dpi = 600)
```

##MTHFD2
```{r}
j=323

summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered_trinity$index[j] -> target_scan
summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered_trinity |> 
  dplyr::filter(
    index == target_scan
  ) -> spectrum_file_plot

spectrum_file_plot$sequence_for_fragspec -> title1
spectrum_file_plot$index -> subtitle1 ##index!
round(spectrum_file_plot$PCC,3) -> title2 ##pcc
spectrum_file_plot$`MHplus in Da` -> spec_plot_xmax
spectrum_file_plot$gene_position -> title3

spectrum_file_plot %>% select(peak_table_for_graph) %>%
  unnest(cols=peak_table_for_graph) %>% filter(
    !is.na(matches)
  ) %>% 
  arrange(desc(frag)) %>% 
  slice_head(n=1) %>% 
  pull(frag)->graph_frag_max

spectrum_file_plot %>% select(peak_table_for_graph) %>%
  unnest(cols=peak_table_for_graph) %>% filter(
    !is.na(matches)
  ) %>% 
  arrange(desc(`m/z`)) %>% 
  slice_head(n=1) %>% 
  pull(`m/z`) -> spec_plot_xmax
#summary_filtered_PRM_table_final_DL_library_merged_spec_DLspec_crossed$pearson_correl_coeff[j] |> round(digits = 4) -> subtitle2
#summary_filtered_PRM_table_final_DL_library_merged_spec_DLspec_crossed$cosine_similarity [j] |> round(digits = 4) -> subtitle3
spectrum_file_plot %>% select(peak_table_for_graph) %>%
  unnest(cols=peak_table_for_graph) %>% 
  mutate(
    frag = if_else(frag>=0,frag/graph_frag_max,frag)
  ) %T>% 
  write_tsv(
    "./figures/fig4i_mthfd2.tsv"
  ) %>% 
  ggplot( 
    aes(x=`m/z`,y=frag, label = series)
  )+
  geom_bar(stat="identity",width = 0.2)+
  geom_col(aes(fill = series),width = spec_plot_xmax/1000)+
  geom_text(aes(y=if_else(frag<0,frag-0.28,frag),label=ion_type,color= series),angle=90,hjust=-0.05,vjust=0.5,size=1.1, na.rm = TRUE)+
  # ggrepel::geom_text_repel(
  #   size=2,
  #   alpha = 0.2,
  #   color = "black",
  #   angle= 90,
  #   nudge_x = 10,
  #   #nudge_y = 1000,
  #   box.padding = 0.1,
  #   na.rm = TRUE,
  #   direction = "x",
  #   min.segment.length = 0.5,
  #   ylim = c(0.4,0.8)
  # )+
  geom_hline(yintercept = 0, color = "black")+
  scale_fill_manual(
    values = c("b"=RColorBrewer::brewer.pal(n=9,"Set1")[1],"y"=RColorBrewer::brewer.pal(n=9,"Set1")[2]),
    na.value = NA
  )+
  scale_color_manual(
    values = c("b"=RColorBrewer::brewer.pal(n=9,"Set1")[1],"y"=RColorBrewer::brewer.pal(n=9,"Set1")[2]),
    na.value = NA
  )+
  scale_x_continuous(limits=c(0, spec_plot_xmax+100),expand=c(0,0))+ #limits=c(250,800),
  scale_y_continuous(breaks = c(1,0.5,0,-0.5,-1),labels = scales::percent(c(1,0.5,0,0.5,1)), limits=c(-1.4,1.4),expand=c(0,0))+
  theme_classic()+
  labs(x="m/z",y="Normalized Intensity", fill = "Ion Type", color = "Ion Type", title = paste0(title1,"  PCC=",title2))+
  theme(
    legend.position = "none",
    plot.subtitle = element_text(size=8, color="black"),
    axis.text.x = element_text(color = "black",size= 7),
    axis.text.y =element_text(color = "black",size= 7),
    axis.title = element_text(color = "black",size= 8),
    axis.title.y = element_blank(),
    plot.title = element_text(color = "black",size= 7),
    axis.ticks = element_line(color = "black"),
    legend.title = element_text(color = "black",size= 8),
    legend.text = element_text(color = "black",size= 8),
    plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
  )
ggsave(paste0("./figures/mthfd2.png"), width=10, height = 3, units = "cm", dpi = 600)

```



#Supplement Fig. 2
```{r}
#a
summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  distinct(Sequence,.keep_all = TRUE) %>%
  select(
    Sequence,p5p5prime
  ) %T>% 
  write_tsv(
    "./figures/sfig2a.tsv"
  ) %>% 
  pull(p5p5prime) %>% 
  ggseqlogo(
  )+
  theme(
    legend.position = "none"
  )
ggsave("./figures/1_02_logo1_ednq_p5p5prime_all.png",width = 8,height = 8, units = "cm", dpi = 600)

#b
 
prepareProteomeByFTP(
  source = NULL, 
  species = "Homo sapiens",
  fastaFile="UP000005640_9606_2301.fasta"
) -> logo_proteome

summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  distinct(Sequence,.keep_all = TRUE) %>% 
  select(
    Sequence,p5p1
  ) %T>% 
  write_tsv(
    "./figures/sfig2b.tsv"
  ) %>%
  pull(p5p1)

formatSequence(
  seq = summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% distinct(Sequence,.keep_all = TRUE) %>% pull(p5p1),
  proteome = logo_proteome, 
  upstreamOffset = 5,
  downstreamOffset = 1
) -> dag_seq2


bg_fisher2 <- buildBackgroundModel(dag_seq2, background = "wholeProteome",proteome = logo_proteome, testType = "fisher")

png("./figures/1_02_dag_heatmap_all.png", width = 10, height = 10, units = "cm", res = 600)
dagHeatmap(
  testDAU(dag_seq2, dagBackground = bg_fisher2),
  type="diff",
  labels_col = c("P5","P4","P3","P2","P1"),
  display_numbers = TRUE
)
dev.off()

#c
summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  distinct(Sequence,.keep_all = TRUE) %>% #339
  filter(p1r_check==1) %>% 
  filter(enzyme =="trypsin") %>% 
  select(
    Sequence,p1r_check,p5p1
  ) %T>% 
  write_tsv(
    "./figures/sfig2c.tsv"
  ) %>%
  pull(p5p1) %>% 
  ggseqlogo(
  )+
  theme(
    legend.position = "none"
  )->fig_logo

fig_logo$scales$scales[[1]]$labels <- c("P5","P4","P3","P2","P1")

fig_logo

ggsave("./figures/1_02_logo2_p1r.png",width = 8,height = 8, units = "cm", dpi = 600)


#d
summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered %>% 
  distinct(Sequence,.keep_all = TRUE) %>% #339
  mutate(
    p5p5prime = str_replace(p5p5prime,"(?<=.....).","X")
  ) %>% 
  select(
    Sequence,p5p5prime
  ) %T>% 
  write_tsv(
    "./figures/sfig2c.tsv"
  ) %>%
  pull(p5p5prime) %>% 
  ggseqlogo(
  )+
  theme(
    legend.position = "none"
  )
ggsave("./figures/1_02_logo2_ednq_p5p5prime_p1r_p2gv_removed_enlarged.png",width = 8,height = 8, units = "cm", dpi = 600)

#e
formatSequence(
  seq = summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered %>% distinct(Sequence,.keep_all = TRUE) %>% pull(p5p1),
  proteome = logo_proteome, 
  upstreamOffset = 5,
  downstreamOffset = 1
) -> dag_seq3


bg_fisher3 <- buildBackgroundModel(dag_seq3, background = "wholeProteome", proteome = logo_proteome, testType = "fisher")

png("./figures/1_02_dag_heatmap_p2gv_removed.png", width = 10, height = 10, units = "cm", res = 600)

dagHeatmap(
  testDAU(dag_seq3, dagBackground = bg_fisher3),
  type="diff",
  labels_col = c("P5","P4","P3","P2","P1"),
  display_numbers = TRUE
)

dev.off()

```


#Supplement Fig. 3
```{r}

#c
psm_563516 %>% filter(
  P1prime == "R" & nmod =="Acetyl:2H(3" & enzyme == "trypsin"
) %>% select(Sequence,Modifications,RT,P1prime,nmod, enzyme,bion_int_perc,yion_int_perc) %T>% 
   write_tsv(
     "./figures/2_02_ion_series_9570.tsv"
   ) %>% 
  select(bion_int_perc,yion_int_perc) %>% 
  pivot_longer(everything()) %>% 
  ggplot(
  )+ 
  geom_histogram(
    aes(x=value,color = name),
    fill = "white",alpha=0.5,binwidth = 0.01
  )+
  geom_vline(
    data = psm_563516 %>% 
      filter(
        P1prime == "R" & nmod =="Acetyl:2H(3" & enzyme == "trypsin"
      ) %>% 
      select(bion_int_perc,yion_int_perc) %>% 
      pivot_longer(everything()) %>% 
      drop_na() %>% 
      summarise(
        .by = name,
        grp_mean = mean(value)
      ),
    aes(xintercept = grp_mean),color="#4DAF4A", linetype="dashed"
  )+
  scale_color_manual(values = c("#377EB8","#E41A1C"))+
  scale_x_continuous(labels = scales::label_percent())+
  labs(x="Area Percentage",y="PSM count")+
  theme_classic2()+
  theme(legend.position = "none")+
  facet_grid(name ~.)
ggsave("./figures/2_02_ion_series_9570.png",width =4, height = 4,dpi = 600)

#d
psm_563516 %>% filter(
  P1prime != "R" & nmod =="Acetyl:2H(3" & enzyme == "trypsin"
) %>% select(Sequence,Modifications,RT,P1prime,nmod, enzyme,bion_int_perc,yion_int_perc) %T>% 
   write_tsv(
     "./figures/2_02_ion_series_156125.tsv"
   ) %>% 
  select(bion_int_perc,yion_int_perc) %>% 
  pivot_longer(everything()) %>% 
  ggplot(
  )+ 
  geom_histogram(
    aes(x=value,color = name),
    fill = "white",alpha=0.5,binwidth = 0.01
  )+
  geom_vline(
    data = psm_563516 %>% 
      filter(
        P1prime != "R" & nmod =="Acetyl:2H(3" & enzyme == "trypsin"
      ) %>% 
      select(bion_int_perc,yion_int_perc) %>% 
      pivot_longer(everything()) %>% 
      drop_na() %>% 
      summarise(
        .by = name,
        grp_mean = mean(value)
      ),
    aes(xintercept = grp_mean),color="#4DAF4A", linetype="dashed"
  )+
  scale_color_manual(values = c("#377EB8","#E41A1C"))+
  scale_x_continuous(labels = scales::label_percent())+
  labs(x="Area Percentage",y="PSM count")+
  theme_classic2()+
  theme(legend.position = "none")+
  facet_grid(name ~.)
ggsave("./figures/2_02_ion_series_156125.png",width =4, height = 4,dpi = 600)

#e
 psm_563516 %>% filter(
  nmod =="Acetyl:2H(3" & enzyme == "trypsin"
) %>% 
  mutate(
    p1prime = if_else(P1prime =="R","R","Others")
  ) %>% 
  select(Sequence,Modifications,RT,nmod, enzyme,p1prime,rt_norm) %T>% 
   write_tsv(
     "./figures/2_02_rt.tsv"
   ) %>% 
  ggplot()+
  geom_density(aes(x=rt_norm,fill = p1prime),alpha = 0.5)+
  labs(x="Normalized RT",y="Density")+
  theme_classic2()+
  theme(legend.position = "none")
ggsave("./figures/2_02_rt.png",width =4, height = 4,dpi = 600)

```


#Supplement Fig. 4a-b
```{r}
output_prediction_comparison_chymotrypsin %>% 
  write_tsv(
    "./figures/sfig4.tsv"
  )

#a

 output_prediction_comparison_chymotrypsin %>%
  mutate(
    model = fct(model,levels=c("built","pretrained","finetuned"))
  ) %>% 
  ggplot(aes(x=model,y=PCC))+
  geom_violin(aes(fill = model),linewidth = 0.1,scale = "width")+
  labs(y="PCC")+
  geom_boxplot(width = 0.1,outlier.shape = NA,linewidth = 0.1)+
  scale_x_discrete(labels =c("Built","Pretrained","Fine-tuned"))+
  scale_fill_manual(
    values = c("#4DAF4A","#377EB8","#E41A1C")
  )+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.text.x = element_text(color = "black",size = 9,angle = 45,hjust=1),
    axis.text.y = element_text(color = "black",size = 9)
  )
ggsave("./figures/2_03_finetuning3.png",width =5, height = 8,dpi = 600,units = "cm")

#b
output_prediction_comparison_chymotrypsin %>% 
  mutate(
    model = fct(model,levels=c("built","pretrained","finetuned"))
  ) %>% 
  filter(PCC >= 0.9) %>% 
  summarize(
    .by = model,
    count = n()
  ) %>% 
  mutate(
    perc = count/9569
  ) %>% 
  ggplot(aes(x=model,y=perc,fill=model))+
  geom_bar(stat = "identity")+
  geom_text(
    aes(label = scales::percent(perc,accuracy = 0.1)),vjust =-0.3,
    size =3
  )+
  labs(y="PCC \u2265 0.9")+
  scale_y_continuous(labels = scales::percent,breaks = seq(0,1,0.1),limits = c(0,1))+
  scale_x_discrete(labels =c("Built","Pretrained","Fine-tuned"))+
  scale_fill_manual(
    values = c("#4DAF4A","#377EB8","#E41A1C")
  )+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.text.x = element_text(color = "black",size = 9,angle = 45,hjust=1),
    axis.text.y = element_text(color = "black",size = 9)
  )
ggsave("./figures/2_03_finetuning4.png",width =5, height = 8,dpi = 600,units = "cm")

```

#Supplement Fig. 4c-e
```{r}
###figure generation
summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  filter(
    index==1028
  ) %>% 
  pull(peak_table_for_graph) %>% 
  .[[1]] %>% 
  write_tsv(
    "./figures/sfig4c.tsv"
  )

summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  filter(
    index==336
  ) %>% 
  pull(peak_table_for_graph) %>% 
  .[[1]] %>% 
  write_tsv(
    "./figures/sfig4d.tsv"
  )

summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  filter(
    index==267
  ) %>% 
  pull(peak_table_for_graph) %>% 
  .[[1]] %>% 
  write_tsv(
    "./figures/sfig4e.tsv"
  )


for (j in 1:nrow(summaryfile_psm_for_testing3_pcc_rt_hfsm2)){
  summaryfile_psm_for_testing3_pcc_rt_hfsm2$index[j] -> target_scan #1 >> j
  summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
    dplyr::filter(
      index == target_scan
    ) -> spectrum_file_plot
  
  spectrum_file_plot$sequence_for_fragspec -> title1
  spectrum_file_plot$index -> subtitle1 ##index!
  round(spectrum_file_plot$PCC,3) -> title2 ##pcc
  spectrum_file_plot$`MHplus in Da` -> spec_plot_xmax
  spectrum_file_plot$prot_pos_reposition -> title3
  spectrum_file_plot %>% select(peak_table_for_graph) %>%
    unnest(cols=peak_table_for_graph) %>% 
    ggplot( 
      aes(x=`m/z`,y=frag, label = ion_type)
    )+
    geom_bar(stat="identity",width = 0.2)+
    geom_col(aes(fill = series),width = spec_plot_xmax/1000)+
    geom_text(aes(y=if_else(frag<0,frag-0.08,frag),label=ion_type,color= series),angle=90,hjust=-0.05,vjust=0,size=2, na.rm = TRUE)+
  geom_hline(yintercept = 0, color = "black")+
    scale_fill_manual(
      values = c("b"=RColorBrewer::brewer.pal(n=9,"Set1")[2],"y"=RColorBrewer::brewer.pal(n=9,"Set1")[1]),
      na.value = NA
    )+
    scale_color_manual(
      values = c("b"=RColorBrewer::brewer.pal(n=9,"Set1")[2],"y"=RColorBrewer::brewer.pal(n=9,"Set1")[1]),
      na.value = NA
    )+
    scale_x_continuous(limits=c(0, spec_plot_xmax),expand=c(0,0))+ #limits=c(250,800),
    scale_y_continuous(breaks = c(1,0.5,0,-0.5,-1),labels = scales::percent(c(1,0.5,0,0.5,1)), limits=c(-1.2,1.2),expand=c(0,0))+
    theme_classic()+
    labs(x="m/z",y="Normalized Intensity", fill = "Ion Type", color = "Ion Type", title = paste0(title1,"  ",title3), subtitle = paste0("PCC = ",title2,"  index: ",subtitle1))+
    theme(
      legend.position = "none",
      plot.subtitle = element_text(size=10, color="black")
    )->mirror_plot1
  
  
  spectrum_file_plot %>% select(peak_table_for_graph) %>%
    unnest(cols=peak_table_for_graph) %>% 
    filter(!is.na(ms2error)) %>% 
    ggplot(
      aes(x=`m/z`,y=ms2error,color = series)
    )+
    geom_point(size=1)+
    geom_hline(yintercept = 0, color = "black")+
    scale_color_manual(
      values = c("b"=RColorBrewer::brewer.pal(n=9,"Set1")[2],"y"=RColorBrewer::brewer.pal(n=9,"Set1")[1])
    )+
    scale_x_continuous(
      limits=c(0, spec_plot_xmax),expand=c(0,0)
    )+
    scale_y_continuous(
      limits = c(-0.05,0.05),
      labels = \(x) x*1000
    )+
    labs(
      y="Mass error (mDa)"
    )+
    theme_bw()+
    theme(
      legend.position = "none"
    )->mirror_plot2
  ggarrange(
    mirror_plot1,mirror_plot2,
    ncol=1,
    heights = c(2,1),
    align = "v"
  )
  ggsave(paste0("./ms2figures/",j,".png"), width=20, height = 12, units = "cm", dpi = 600)
}
```


# Supplement Fig. 4f
```{r}
summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  mutate(
    enzyme = fct(enzyme,levels = c("trypsin","chymotrypsin","All"))
  ) %>% 
  bind_rows(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% mutate(
      enzyme = fct(c("All"),levels = c("trypsin","chymotrypsin","All"))
    )
  ) %>% 
  select(
    index,enzyme,PCC
  ) %T>% 
  write_tsv(
    "./figures/sfig4f.tsv"
  ) %>% 
  ggplot(
    aes(x=enzyme,y=PCC,fill = enzyme)
  )+
  geom_boxplot()+
  scale_x_discrete(
    labels = c("Trypsin","Chymotrypsin","All")
  )+
  labs(
    x="Protease"
  )+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.text = element_text(color="black")
  )
ggsave("./figures/sfig4f.png",width=8,height=8,dpi = 600,units="cm")

```

#Supplement Fig. 5
```{r}
#From bidding_pcc_fdr.R


fdr_pcc_negative_set8 %>% 
  write_tsv(
    "./figures/sfig5.tsv"
  )

#b
fdr_pcc_negative_set7 %>%
  filter(enzyme == "trypsin") %>% 
  summarize(
    .by=fdr,
    count =n(),
    percol_score= mean(percolator_score),
    #.by = moddb_result
  )
fdr_pcc_negative_set7 %>% 
  filter(enzyme == "trypsin") %>% 
  select(
    fdr, percolator_score
  ) %>% 
  ggplot(
    aes(x=as.character(fdr),y=percolator_score,fill=as.character(fdr))
  )+
  geom_boxplot()+
  stat_compare_means(
    aes(label = paste0("p= ",after_stat(p.format))),
    comparisons = list(c("1","0")),
    method="t.test",
    p.adjust.methods="BH"
  )+
  labs(y="Percolator Score")+
  scale_x_discrete(
    labels= c("TRUE","FALSE")
  )+
  ylim(c(-2.5,5.5))+
  scale_fill_manual(
    values = c("#4DAF4A","#E41A1C")
  )+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.text.x = element_text(color = "black",size = 8),
    axis.text.y = element_text(color = "black",size = 8)
  )
ggsave(
  "./figures/sfig5b.png",width=8,height=8, units = "cm",dpi = 600
)

#c
tibble(
    PCC=as.numeric(auc(roc(response=fdr_pcc_negative_set8$true_set,predictor = fdr_pcc_negative_set8$PCC))),
    SA=as.numeric(auc(roc(response=fdr_pcc_negative_set8$true_set,predictor = fdr_pcc_negative_set8$SA))),
                   SPC=as.numeric(auc(roc(response=fdr_pcc_negative_set8$true_set,predictor = fdr_pcc_negative_set8$SPC))), ## 0.5263
                   specFPR=as.numeric(auc(roc(response=fdr_pcc_negative_set8$true_set,predictor = fdr_pcc_negative_set8$spec_FDR))), #0.5015
                   specFNR=as.numeric(auc(roc(response=fdr_pcc_negative_set8$true_set,predictor = fdr_pcc_negative_set8$spec_FNR))), ##0.481
                   percolator=as.numeric(auc(roc(response=fdr_pcc_negative_set8$true_set,predictor = fdr_pcc_negative_set8$percolator_score))) #0.4979
  ) %>% 
    pivot_longer(everything()) %>% 
    ggplot(
      aes(x=fct(name,levels=c("PCC","SA","SPC","specFNR","specFPR","percolator")),y=value)
    )+
    geom_bar(stat="identity",fill="black",width = 0.4)+
    geom_text(aes(label = round(value,3)),hjust=-0.1, size =3,angle =90)+
    labs(y="AUC of ROC")+
    scale_y_continuous(limits = c(0,0.7))+
    theme_classic2()+
    theme(
      legend.position = "none",
      axis.title.x = element_blank(),
      text= element_text(color = "black", size = 8),
      axis.text.y = element_text(color = "black", size = 8, hjust=1),
      axis.text.x = element_text(color = "black", size = 8, angle=45,hjust=1),
      #axis.title.x = element_blank()
    )
  ggsave("./figures/sfig5c.png",width=8,height=8,dpi = 600,units="cm")
```


#Supplement Fig. 6
```{r}
for (i in 1:12){
  summaryfile_psm_for_training_result$set %>% unique -> set_names
  set_names[i]->set_name
  summaryfile_psm_for_training_result %>% 
    filter(set == set_name) %>% 
    ggplot(aes(x=rt_norm, y=rt_pred))+
    geom_point(size=0.5,alpha=0.5) +
    geom_line(aes(y=lwr), color = "red", linetype = "dashed")+
    geom_line(aes(y=upr), color = "red", linetype = "dashed")+
    geom_smooth(method=lm, se=TRUE)+
    lims(x=c(0,1),y=c(0,1))+
    labs(
      x="Observed Normalized RT",
      y="Predicted Normalized RT"
    )+
    theme_classic()
  ggsave(
    paste0("./figure2/rt_prediction_training_set",set_name,".png"),width=10,height=10,dpi = 600,units="cm"
  )
}

summaryfile_psm_for_training_result %>% 
  write_tsv(
    "./figures/sfig6.tsv"
  )
```


#Supplement Fig. 7
```{r}
{
  folder_alphapeptdeep
  i=1
  output_prediction_rt_train_result <- tibble()
  output_prediction_rt_test_result <- tibble()
  for (i in 1:12){
    output_prediction_rt_training <- read_tsv(
      paste0(folder_alphapeptdeep,"output_rt_training_gv_fig2h_",i,".tsv")
    )[,-1] %>% 
      arrange(rt_norm) %>% 
      mutate(file_series= i) %>% 
      filter(str_detect(sequence,"^R")) %>% 
      filter(
        str_detect(mods, "Acetyl\\:2H\\(3\\)@Any")
      )
    
    output_prediction_rt_test <- read_tsv(
      paste0(folder_alphapeptdeep,"output_rt_testing_gv_fig2h_",i,".tsv")
    )[,-1] %>% 
      arrange(rt_norm) %>%
      mutate(file_series = i)
    
    fit_rt_training <- lm(rt_norm ~ rt_pred, data =output_prediction_rt_training)
    
    output_prediction_rt_training %>%
      bind_cols(
        predict(fit_rt_training, interval = "prediction", level =0.95, newdata = output_prediction_rt_training)
      )->output_prediction_rt_training
    
    
    output_prediction_rt_test %>% 
      bind_cols(
        predict(fit_rt_training, interval = "prediction", level =0.95, newdata = output_prediction_rt_test)
      )->output_prediction_rt_test
    
    
    output_prediction_rt_train_result %>% 
      bind_rows(
        output_prediction_rt_training
      ) -> output_prediction_rt_train_result
    
    output_prediction_rt_test_result %>% 
      bind_rows(
        output_prediction_rt_test
      ) -> output_prediction_rt_test_result
  }
  output_prediction_rt_train_result %>% 
    arrange(
      spec_idx
    ) ->output_prediction_rt_train_result
  
  output_prediction_rt_test_result %>% 
    arrange(
      spec_idx
    ) ->output_prediction_rt_test_result
  
  output_prediction_rt_test_result %>% 
    mutate(
      rt_test = if_else(rt_norm > lwr & rt_norm < upr, 1, 0)
    ) ->output_prediction_rt_test_result
  
  output_prediction_rt_train_result %>% 
    left_join(
      file_raw_index2 %>% select(-c(left_time,right_time)),
      join_by(file_series)
    ) -> output_prediction_rt_train_result
  
  output_prediction_rt_train_result %>% 
    mutate(
      rt_observed = rt_norm*(right_time-left_time)+left_time,
      rt_predicted = rt_pred*(right_time-left_time)+left_time,
      rt_fit = fit*(right_time-left_time)+left_time,
      rt_lwr = lwr*(right_time-left_time)+left_time,
      rt_upr = upr*(right_time-left_time)+left_time
    ) -> output_prediction_rt_train_result
  
  output_prediction_rt_test_result %>% 
    left_join(
      file_raw_index2,
      join_by(file_series)
    ) ->output_prediction_rt_test_result
  
  output_prediction_rt_test_result %>% 
    select(
      -c(left_time.x,right_time.x)
    ) %>% 
    rename(
      left_time = left_time.y,
      right_time = right_time.y
    ) -> output_prediction_rt_test_result
  
  output_prediction_rt_test_result %>% 
    mutate(
      rt_observed = rt_norm*(right_time-left_time)+left_time,
      rt_predicted = rt_pred*(right_time-left_time)+left_time,
      rt_fit = fit*(right_time-left_time)+left_time,
      rt_lwr = lwr*(right_time-left_time)+left_time,
      rt_upr = upr*(right_time-left_time)+left_time
    ) ->output_prediction_rt_test_result
  
  
  output_prediction_rt_train_result
  output_prediction_rt_test_result
  
  
  ##R, MAE, T90
  {
    
    output_prediction_rt_train_result 
    output_prediction_rt_test_result 
    
    
    output_prediction_rt_train_result %>% 
      filter(file_series==1)
    
    fit_rt_training <- lm(
      rt_observed~ rt_predicted, 
      data =output_prediction_rt_train_result %>% 
        filter(file_series==1))
    
    fit_rt_training %>% tidy()
    
    output_prediction_rt_train_result %>% 
      mutate(t95=rt_upr-rt_lwr) %>% 
      summarise(
        .by = c(set,file_series),
        t95_mean = mean(t95)
      ) -> summary_rtprediction_t95
    summary_rtprediction_t95 %>% write_tsv(
      "./figures/rt/rt_t95.tsv"
    )
    
    summary_rtprediction <- tibble()
    for (i in 1L:12L){
      summary_rtprediction %>% 
        bind_rows(
          output_prediction_rt_train_result %>% 
            filter(file_series==i) %>% 
            metrics(
              truth = rt_observed, estimate = rt_predicted
            ) %>% 
            mutate(
              file_series =i
            )
        )->summary_rtprediction
    }
    summary_rtprediction %>% write_tsv("./figures/rt/summary_rtprediction_250210.tsv")
    
    output_prediction_rt_train_result %>% 
      filter(file_series==i) %>% 
      metrics(
        truth = rt_observed, estimate = rt_predicted
      ) %>% 
      mutate(
        file_series =i
      )
    
  }
  
}

i=1
for (i in 1L:12L){
  output_prediction_rt_train_result %>% 
    filter(file_series == i) %>% 
    ggplot(aes(x=rt_observed, y=rt_predicted))+
    geom_point(size=0.5,alpha=0.5) +
    annotate(
      "text",x=-Inf,y=Inf,hjust=0,vjust=1.2,
      label=bquote(
        ~Delta*italic(t)[95*'%'] == .(str_sub(paste0(summary_rtprediction_t95[i,3]),1,5))*","~R^2==.(summary_rtprediction %>% filter(file_series==i,.metric =="rsq") %>% pull(.estimate) %>% round(3))
      ),size =4
    )+
    annotate(
      "text",x=-Inf,y=Inf,hjust=0,vjust=3.2,
      label=bquote(
        ~MAE==.(summary_rtprediction %>% filter(file_series==i,.metric =="mae") %>% pull(.estimate) %>% round(3))*","~N==.(output_prediction_rt_train_result %>% filter(file_series==i) %>% nrow())
      ),size =4
    )+
    geom_line(aes(x=rt_lwr), color = "red", linetype = "dashed")+
    geom_line(aes(x=rt_upr), color = "red", linetype = "dashed")+
    geom_smooth(method=lm, se=TRUE)+
    #lims(x=c(0,1),y=c(0,1))+
    labs(
      x="Observed RT (min)",
      y="Predicted RT (min)"
    )+
    theme_classic2()+
    theme(
      axis.text = element_text(color = "black",size=10),
      axis.title = element_text(color = "black",size=11)
    )
  ggsave(
    paste0("./figures/rt/rt_prediction_training_set",i,".png"),width=10,height=10,dpi = 600,units="cm"
  )
}
  
{
  i=1
  output_prediction_rt_train_result %>% 
    filter(file_series == i) %>% 
    ggplot(aes(x=rt_observed, y=rt_predicted))+
    geom_point(size=0.1,alpha=0.25) +
    annotate(
      "text",x=-Inf,y=Inf,hjust=0,vjust=1.2,
      label=bquote(
        ~Delta*italic(t)[95*'%'] == .(str_sub(paste0(summary_rtprediction_t95[i,3]),1,5))*","~R^2==.(summary_rtprediction %>% filter(file_series==i,.metric =="rsq") %>% pull(.estimate) %>% round(3))
      ),size =2
    )+
    annotate(
      "text",x=-Inf,y=Inf,hjust=0,vjust=3.2,
      label=bquote(
        ~MAE==.(summary_rtprediction %>% filter(file_series==i,.metric =="mae") %>% pull(.estimate) %>% round(3))*","~N==.(output_prediction_rt_train_result %>% filter(file_series==i) %>% nrow())
      ),size =2
    )+
    geom_line(aes(x=rt_lwr), color = "red", linetype = "dashed",size =0.5)+
    geom_line(aes(x=rt_upr), color = "red", linetype = "dashed",size =0.5)+
    geom_smooth(method=lm, se=TRUE, size = 0.5)+
    #lims(x=c(0,1),y=c(0,1))+
    labs(
      x="Observed RT (min)",
      y="Predicted RT (min)"
    )+
    theme_classic2()+
    theme(
      legend.position = "none",
      #axis.title.x = element_blank(),
      axis.title = element_text(color = "black",size = 7),
      #axis.text.x = element_blank(),
      axis.text = element_text(color = "black",size = 6),
      plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
    )
  ggsave(
    paste0("./figures/rt/rt_prediction_training_set_mainfigure",i,".png"),width=4.5,height=4.5,dpi = 600,units="cm"
  )
}

output_prediction_rt_test_result %>%
  filter(
    rt_test ==1
  )
  
i=1
for (i in 1L:12L){
  output_prediction_rt_test_result %>% 
    filter(file_series == i) %>% 
    filter(
      rt_test == 1
    ) %>% nrow() -> rt_passed_string
  
  output_prediction_rt_test_result %>% 
    filter(file_series == i) %>% nrow() -> rt_total_string
  
  output_prediction_rt_test_result %>% 
    filter(file_series == i) %>% 
    ggplot(aes(x=rt_observed, y=rt_predicted))+
    geom_point(size=0.1,alpha=0.25) +
    geom_line(aes(x=rt_lwr), color = "red", linetype = "dashed",size =0.5)+
    geom_line(aes(x=rt_upr), color = "red", linetype = "dashed",size =0.5)+
    annotate(
      "text",x=-Inf,y=Inf,hjust=-0.1,vjust=1.1,
      label=bquote(
        .(rt_passed_string)*"/"*.(rt_total_string)
      ),size =2
    )+
    geom_smooth(method=lm, se=TRUE, size = 0.5)+
      #lims(x=c(0,1),y=c(0,1))+
      labs(
        x="Observed RT (min)",
        y="Predicted RT (min)"
      )+
      theme_classic2()+
      theme(
        legend.position = "none",
        #axis.title.x = element_blank(),
        axis.title = element_text(color = "black",size = 7),
        #axis.text.x = element_blank(),
        axis.text = element_text(color = "black",size = 6),
        plot.margin = unit(c(0.1,0.1,0.1,0.1), "cm")
      )
  ggsave(
    paste0("./figures/rt/rt_prediction_testing_set_fig2h_",i,".png"),width=4.5,height=4.5,dpi = 600,units="cm"
  )
}

output_prediction_rt_test_result %>% 
  write_tsv(
    "./figures/sfig7.tsv"
  )
```


# Supplement Fig. 8
```{r}
summaryfile_psm_for_testing3_pcc_rt_hfsm %>% 
  distinct(set) %>% pull(set) -> set_vector

summaryfile_psm_for_testing3_pcc_rt_hfsm %>% 
  summarize(
    .by = set,
    experiment = first(experiment),
    replicate = first(replicate),
    enzyme = first(enzyme),
    count = n(),
    rt_check = sum(rt_check)
  )

summaryfile_psm_for_testing3_pcc_rt_hfsm %>% 
  summarize(
    .by = set,
    experiment = first(experiment),
    replicate = first(replicate),
    enzyme = first(enzyme),
    count = n(),
    rt_check = sum(rt_check)
  ) %>% pull(set) -> set_vector

i=1 

summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% filter(
  rt_check==1
)
for (i in 1:12){
  paste0(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      summarize(
        .by = set,
        experiment = first(experiment),
        replicate = first(replicate),
        enzyme = first(enzyme),
        count = n(),
        rt_check = sum(rt_check)
      ) %>% 
      filter(
        set == set_vector[i]
      ) %>% 
      pull(rt_check),
    "/",
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      summarize(
        .by = set,
        experiment = first(experiment),
        replicate = first(replicate),
        enzyme = first(enzyme),
        count = n(),
        rt_check = sum(rt_check)
      ) %>% 
      filter(
        set == set_vector[i]
      ) %>% 
      pull(count)
  ) -> count_for_rt

  summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
    filter(
      set == set_vector[i]
    ) %>% 
    mutate(
      rt_norm = (right_time - left_time)* rt_norm + left_time,
      rt_pred = (right_time - left_time)* rt_pred + left_time,
      fit = (right_time - left_time)* fit + left_time,
      lwr = (right_time - left_time)* lwr + left_time,
      upr = (right_time - left_time)* upr + left_time
    ) %>% 
    ggplot(aes(x=rt_norm, y=rt_pred))+
    geom_point(
      aes(color = fct(as.character(rt_check),levels =c("0","1"))),
      size=0.5,alpha=0.5
    )+
    annotate(
      "text",x=-Inf,y=Inf,hjust=-0.2,vjust=2,
      label=paste0("Passed = ",count_for_rt),size =4
    )+
    geom_line(aes(x=lwr), color = "red", linetype = "dashed")+
    geom_line(aes(x=upr), color = "red", linetype = "dashed")+
    #geom_smooth(method=lm, se=TRUE)+
    #lims(x=c(0,1),y=c(0,1))+
    scale_color_manual(
      values = c("black","red")
    )+
    labs(
      x="Observed RT (min)",
      y="Predicted RT (min)"
    )+
    lims(x=c(30,140),y=c(30,140))+
    theme_classic2()+
    theme(
      legend.position = "none",
      axis.text = element_text(color = "black",size=10),
      axis.title = element_text(color = "black",size=11)
    )
  ggsave(
    paste0("./figures/rt/rt_prediction_test3_set",i,".png"),width=10,height=10,dpi = 600,units="cm"
  )
}

summaryfile_psm_for_testing3_pcc_rt_hfsm %>% 
  write_tsv(
    "./figures/supple8.tsv"
  )


```

#Supplement Fig. 9a-b
```{r}
##A
summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  select(
    b_ion_errors
  ) %>% 
  unnest(b_ion_errors) %T>% #pull(b_ion_errors) %>% sd() #-0.001370094 sd 0.01418807
  write_tsv(
    "./figures/met_b_error_dist_rev.tsv"
  )->supple9a

supple9a %>% 
  ggplot(
    aes(x=b_ion_errors)
  )+
  geom_histogram(
    binwidth = 0.001,
    fill = "#377EB8",
    color = "black",
    linewidth = 0.1
  )+
  geom_vline(
    aes(xintercept = mean(b_ion_errors)),
    linetype = "dashed",
    color = "black"
  )+
  scale_x_continuous(expand = c(0, 0))+
  scale_y_continuous(expand = c(0, 0))+
  labs(
    x="b-ion errors (Da)",
    y="Count"
  )+
  theme_pubr()+
  theme(
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 8)
  )
ggsave("./figures/met_b_error_dist_rev.png",width=9,height=6,dpi = 600,units="cm")
      
##B
summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  select(
    y_ion_errors
  ) %>% 
  unnest(y_ion_errors) %T>% #pull(b_ion_errors) %>% sd() #-0.001370094 sd 0.01418807
  write_tsv(
    "./figures/met_y_error_dist_rev.tsv"
  ) %>% 
  ggplot(
    aes(x=y_ion_errors)
  )+
  geom_histogram(
    binwidth = 0.001,
    fill = "#E41A1C",
    color = "black",
    linewidth = 0.1
  )+
  geom_vline(
    aes(xintercept = mean(y_ion_errors)),
    linetype = "dashed",
    color = "black"
  )+
  scale_x_continuous(expand = c(0, 0))+
  scale_y_continuous(expand = c(0, 0))+
  labs(
    x="b-ion errors (Da)",
    y="Count"
  )+
  theme_pubr()+
  theme(
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 8)
  )
ggsave("./figures/met_y_error_dist_rev.png",width=9,height=6,dpi = 600,units="cm")

# Data
summaryfile_psm_for_testing3_pcc_rt_hfsm2%>% 
  select(
    index,b_ion_errors
  ) %>% 
  unnest(b_ion_errors) %>% 
  write_tsv(
    "./figures/met_b_error_dist_rev.tsv"
  )

summaryfile_psm_for_testing3_pcc_rt_hfsm2%>% 
  select(
    index,y_ion_errors
  ) %>% 
  unnest(y_ion_errors) %>% 
  write_tsv(
    "./figures/met_y_error_dist_rev.tsv"
  )


```

# Supplement Fig. 9c-d
```{r}

#
summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  mutate(
    b_ion_errors = map_dbl(b_ion_errors,\(x) mean(x)),
    y_ion_errors = map_dbl(y_ion_errors,\(x) mean(x))
  ) %>% 
  filter(
    pcc_check ==1
  ) %>% 
  select(index,b_ion_errors,y_ion_errors) %T>% 
  write_tsv(
    "./figures/sfig9c.tsv"
  ) %>% 
  ggplot(
    aes(x=b_ion_errors,y=y_ion_errors)
  )+
  geom_point(
    data = summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      mutate(
        b_ion_errors = map_dbl(b_ion_errors,\(x) mean(x)),
        y_ion_errors = map_dbl(y_ion_errors,\(x) mean(x))
      ) %>% 
      filter(
        pcc_check ==0
      ) %>% 
      select(b_ion_errors,y_ion_errors),
    colour = "grey",
    alpha = 0.8
  )+
  geom_pointdensity(adjust=0.005)+
  scale_color_viridis()+
  scale_y_continuous(
    limits = c(-0.05,0.05)
  )+
  scale_x_continuous(
    limits = c(-0.05,0.05)
  )+
  labs(
    x="b-ion Errors (Da)",
    y="y-ion Errors (Da)",
    color = "Number of Neighbors"
  )+
  theme_bw()+
  theme(
    legend.frame = element_rect(linewidth = 0.2),
    legend.position = c(.5,.85),
    legend.direction = "horizontal",
    legend.title.position = "top",
    legend.text = element_text(color="black",size=9),
    axis.text = element_text(color="black",size=10),
    axis.title = element_text(size=12)
  )
ggsave("./figures/sfig9c.png",width=10,height=10,dpi = 600,units="cm")

summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  mutate(
    b_ion_errors = map_dbl(b_ion_errors,\(x) mean(x)),
    y_ion_errors = map_dbl(y_ion_errors,\(x) mean(x))
  ) %>% 
  filter(
    rt_check ==1
  ) %>% 
  select(index,b_ion_errors,y_ion_errors) %T>% 
  write_tsv(
    "./figures/sfig9d.tsv"
  ) %>% 
  ggplot(
    aes(x=b_ion_errors,y=y_ion_errors)
  )+
  geom_point(
    data = summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      mutate(
        b_ion_errors = map_dbl(b_ion_errors,\(x) mean(x)),
        y_ion_errors = map_dbl(y_ion_errors,\(x) mean(x))
      ) %>% 
      filter(
        rt_check ==0
      ) %>% 
      select(b_ion_errors,y_ion_errors),
    colour = "grey",
    alpha = 0.8
  )+
  geom_pointdensity(adjust=0.005)+
  scale_color_viridis()+
  scale_y_continuous(
    limits = c(-0.05,0.05)
  )+
  scale_x_continuous(
    limits = c(-0.05,0.05)
  )+
  labs(
    x="b-ion Errors (Da)",
    y="y-ion Errors (Da)",
    color = "Number of Neighbors"
  )+
  theme_bw()+
  theme(
    legend.position = c(.5,.85),
    legend.direction = "horizontal",
    legend.title.position = "top",
    axis.text = element_text(color="black",size=10),
    axis.title = element_text(size=12)
  )
ggsave("./figures/sfig9d_legend.png",width=10,height=10,dpi = 600,units="cm")

```

#Supplement Fig. 9e-h
```{r}
summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  unnest(b_ion_errors) %>% 
  summarize(
    .by = pcc_check,
    b_mean = mean(b_ion_errors),
    b_sd = sd(b_ion_errors)
  ) %>% 
  bind_cols(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      unnest(y_ion_errors) %>% 
      summarize(
        .by = pcc_check,
        y_mean = mean(y_ion_errors),
        y_sd = sd(y_ion_errors)
      ) %>% select(y_mean,y_sd)
  )->table1

summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  unnest(b_ion_errors) %>% 
  summarize(
    .by = rt_check,
    b_mean = mean(b_ion_errors),
    b_sd = sd(b_ion_errors)
  ) %>% 
  bind_cols(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      unnest(y_ion_errors) %>% 
      summarize(
        .by = rt_check,
        y_mean = mean(y_ion_errors),
        y_sd = sd(y_ion_errors)
      ) %>% select(y_mean,y_sd)
  )->table2

summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  unnest(b_ion_errors) %>% 
  summarize(
    .by = b_y_ttest_check,
    b_mean = mean(b_ion_errors),
    b_sd = sd(b_ion_errors)
  ) %>% 
  bind_cols(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      unnest(y_ion_errors) %>% 
      summarize(
        .by = b_y_ttest_check,
        y_mean = mean(y_ion_errors),
        y_sd = sd(y_ion_errors)
      ) %>% select(y_mean,y_sd)
  )->table3

bind_rows(
  table1,
  table2,
  table3
) %>% 
  mutate(
    result = case_when(
      pcc_check == 1 ~ "pcc_passed",
      pcc_check == 0 ~ "pcc_failed",
      rt_check == 1 ~ "rt_passed",
      rt_check == 0 ~ "rt_failed",
      b_y_ttest_check == 1 ~ "smert_passed",
      b_y_ttest_check == 0 ~ "smert_failed"
    )
  ) %>% 
  select(result, b_mean,b_sd,y_mean,y_sd) -> table_smert_result


remove(table1,table2, table3)


table_smert_result %>% 
  pivot_longer(
    cols = c(b_mean,y_mean)
  ) %>% 
  filter(
    str_detect(result, "passed")
  ) %>% 
  mutate(
    sd = if_else(str_detect(name,"^b"),b_sd,y_sd)
  ) %T>% 
  write_tsv(
    "./figures/2_05_masserror_mean.tsv"
  ) %>% 
  ggplot(
    aes(x=result, y=value,fill=name)
  )+
  geom_bar(
    stat="identity",
    position = "dodge"
  )+
  geom_hline(
    aes(yintercept = 0)
  )+
  scale_y_continuous(
    labels = \(x) x*1000
  )+
  scale_x_discrete(
    labels = c("MS2 model\n passed", "RT model\n passed", "MET\n passed")
  )+
  scale_fill_discrete(
    labels = c("b-ion","y-ion")
  )+
  labs(
    y="Average Mass Error (mDa)"
  )+
  theme_bw()+
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "top",
    axis.text = element_text(color = "black")
  )
ggsave("./figures/2_05_masserror_mean.png",width=10,height=10, units = "cm",dpi = 600)

summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  unnest(
    b_ion_errors
  ) %>% 
  filter(
    pcc_check == 1
  ) %>% 
  select(index,b_ion_errors) %>% 
  mutate(
    ion = "b"
  ) %>% 
  rename(error=b_ion_errors) %>% 
  bind_rows(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      unnest(
        y_ion_errors
      ) %>% 
      filter(
        pcc_check == 1
      ) %>% 
      select(index,y_ion_errors) %>% 
      mutate(
        ion = "y"
      ) %>% 
      rename(error=y_ion_errors)
  ) %T>% 
  write_tsv(
    "./figures/2_05_pcc_error_ttest.tsv"
  ) %>% 
  ggplot(
    aes(x=ion, y=error,fill=ion)
  )+
  geom_boxplot()+
  stat_compare_means(
    method = "t.test",
    hjust = -0.5,
    label.y = 0.06
  )+
  scale_y_continuous(limits = c(-0.05,0.06),breaks = seq(-0.05,0.05,0.025))+
  labs(
    y="Average Mass Error (mDa)"
  )+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.text = element_text(color="black",size = 12),
    axis.title.x = element_blank()
  )
ggsave("./figures/2_05_pcc_error_ttest.png",width=10,height=10, units = "cm",dpi = 600)

summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  unnest(
    b_ion_errors
  ) %>% 
  filter(
    rt_check == 1
  ) %>% 
  select(index,b_ion_errors) %>% 
  mutate(
    ion = "b"
  ) %>% 
  rename(error=b_ion_errors) %>% 
  bind_rows(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      unnest(
        y_ion_errors
      ) %>% 
      filter(
        rt_check == 1
      ) %>% 
      select(index,y_ion_errors) %>% 
      mutate(
        ion = "y"
      ) %>% 
      rename(error=y_ion_errors)
  ) %T>% 
  write_tsv(
    "./figures/2_05_rt_error_ttest.tsv"
  ) %>% 
  ggplot(
    aes(x=ion, y=error,fill=ion)
  )+
  geom_boxplot()+
  stat_compare_means(
    method = "t.test",
    hjust = -0.5,
    label.y = 0.06
  )+
  scale_y_continuous(limits = c(-0.05,0.06),breaks = seq(-0.05,0.05,0.025))+
  labs(
    y="Average Mass Error (mDa)"
  )+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.text = element_text(color="black",size = 12),
    axis.title.x = element_blank()
  )
ggsave("./figures/2_05_rt_error_ttest.png",width=10,height=10, units = "cm",dpi = 600)

summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  unnest(
    b_ion_errors
  ) %>% 
  filter(
    b_y_ttest_check == 1
  ) %>% 
  select(index,b_ion_errors) %>% 
  mutate(
    ion = "b"
  ) %>% 
  rename(error=b_ion_errors) %>% 
  bind_rows(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      unnest(
        y_ion_errors
      ) %>% 
      filter(
        b_y_ttest_check == 1
      ) %>% 
      select(index,y_ion_errors) %>% 
      mutate(
        ion = "y"
      ) %>% 
      rename(error=y_ion_errors)
  ) %T>% 
  write_tsv(
    "./figures/2_05_smert_error_ttest.tsv"
  ) %>% 
  ggplot(
    aes(x=ion, y=error,fill=ion)
  )+
  geom_boxplot()+
  stat_compare_means(
    method = "t.test",
    hjust = -0.5,
    label.y = 0.06
  )+
  scale_y_continuous(limits = c(-0.05,0.06),breaks = seq(-0.05,0.05,0.025))+
  labs(
    y="Average Mass Error (mDa)"
  )+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.text = element_text(color="black",size = 12),
    axis.title.x = element_blank()
  )
ggsave("./figures/2_05_smert_error_ttest.png",width=10,height=10, units = "cm",dpi = 600)
```


#Supplement Fig. 10
```{r}
read_rds(
  "./export/psm_563516.rds"
) -> psm_563516

chisq.test(
  matrix(
    c(8506,1063,3296,298682),nrow=2,ncol=2
  ),correct =FALSE
)

chisq.test(
  matrix(
    c(7159,941,3301,240568),nrow=2,ncol=2
  ),correct =FALSE
)


psm_563516 %>% 
  select(
    index,enzyme,artefact_arg,diagnostic_ion_int_relative,peak_table
  ) %>% 
  filter(artefact_arg == TRUE) %>% 
  mutate(
    peak_table_diag = map(
      peak_table,
      \(x) mutate(x,rel_i = i/max(i)) %>% filter(`m/z`>202.128331 & `m/z`<202.148331)
    )
  ) %>% 
  select(-peak_table) %>% 
  unnest(peak_table_diag) ->psm_563516_diag

#b
psm_563516_diag %>% 
  filter(enzyme == "trypsin") %T>% 
  write_tsv(
    "./figures/2_06_diagnostic_ions_mz_trypsin.tsv"
  ) %>% 
  ggplot(
    aes(x=`m/z`)
  )+
  geom_histogram(
    aes(y=after_stat(density)),
    binwidth = 0.0001,
    fill="black",
    color="white",
    alpha = 0.5,
    linewidth = 0.1
  )+
  geom_density(
    color="red"
  )+
  geom_vline(
    aes(xintercept = 202.143331),linetype="dashed"
  )+
  geom_vline(
    aes(xintercept = 202.133331),linetype="dashed"
  )+
  scale_x_continuous(
    limits = c(202.128331,202.148331),expand=c(0,0),
    breaks= seq(202.123331,202.148331,0.005),
    labels = scales::number_format(accuracy = 0.000001)
    )+
  scale_y_continuous(expand=c(0,0))+
  labs(y="PSM Count")+
  theme_bw()+
  theme(
    axis.text.y = element_text(color = "black",size=8),
    axis.text.x = element_text(color = "black",size=8,angle=45,hjust=1),
    axis.title = element_text(color = "black",size=8)
  )
ggsave(
  "./figures/2_06_diagnostic_ions_mz_trypsin.png",width =6, height =6,dpi = 600, units ="cm"
)


#c
psm_563516 %>% 
  mutate(
    diagnostic_ion_int_relative = if_else(is.na(diagnostic_ion_int_relative),0,diagnostic_ion_int_relative)
  ) %>% 
  filter(
    artefact_arg==TRUE
  ) %>% 
  select(
    enzyme, diagnostic_ion_int_relative
  ) %>% 
  mutate(
    set = "training"
  ) %T>%
  write_tsv(
    "./figures/3_07_diagnostic_ion_int_protease.tsv"
  ) %>% 
  ggplot(
    aes(y=diagnostic_ion_int_relative,x=enzyme,fill = enzyme)
  )+
  geom_boxplot(
    outlier.size = 0.25
  )+
  scale_x_discrete(
    limits = c("trypsin","chymotrypsin"),
    labels = c("Trypsin","Chymotrypsin")
  )+
  scale_y_continuous(
    labels = \(x) scales::percent(x)
  )+
  labs(
    x="Protease",
    y="Relative b1-ion intensity (%)",
    fill = "Protease"
  )+
  theme_classic2()+
  theme(
    axis.text.y = element_text(color = "black",size=8),
    axis.text.x = element_text(color = "black",size=8),
    axis.title = element_text(color = "black",size=8),
    legend.position = "none",
    legend.just = "left"
  )
ggsave("./figures/3_07_diagnostic_ion_int_protease.png",width = 6, height = 6, units = "cm",dpi=600)

```

#!Supplement Fig. 11
```{r}
#ML-filtered DAU
#a
summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered %>% 
  filter(
    score_sum == 3
  ) %>% 
  distinct(Sequence,.keep_all = TRUE) %>% #339
  select(
    index,p5p1
  ) %T>% 
  write_tsv(
    "./figures/3_02_dag_heatmap_mlfiltered.tsv"
  ) %>% 
  pull(p5p1) -> seq_logo_mlfiltered

prepareProteomeByFTP(
    source = NULL, species = "Homo sapiens",
    fastaFile="UP000005640_9606_2301.fasta"
  )-> logo_proteome

{
  formatSequence(
    seq = seq_logo_mlfiltered,
    proteome = logo_proteome, upstreamOffset = 5,
    downstreamOffset = 1
  ) -> dag_seq
  
  buildBackgroundModel(
    dag_seq, 
    background = "wholeProteome",
    proteome = logo_proteome, 
    testType = "fisher"
  ) ->  bg_fisher
  
  png("./figures/3_02_dag_heatmap_mlfiltered.png", width = 10, height = 10, units = "cm", res = 600)
  dagHeatmap(
    testDAU(dag_seq, dagBackground = bg_fisher),
    type="diff",
    labels_col = c("P5","P4","P3","P2","P1"),
    display_numbers = TRUE
  )
  dev.off()
}

#b

summaryfile_psm_for_testing3_pcc_rt_hfsm2_basic_filtered %>% 
  distinct(Sequence,.keep_all = TRUE) %>% #339
  filter(
    score_sum != 3
  ) %>% 
  select(
    index,p5p1
  ) %T>% 
  write_tsv(
    "./figures/3_02_dag_heatmap_not_mlfiltered.tsv"
  ) %>%
  pull(p5p1) -> seq_logo_not_mlfiltered

{
  formatSequence(
    seq = seq_logo_not_mlfiltered,
    proteome = logo_proteome, upstreamOffset = 5,
    downstreamOffset = 1
  ) -> dag_seq
  
  buildBackgroundModel(
    dag_seq, 
    background = "wholeProteome",
    proteome = logo_proteome, 
    testType = "fisher"
  ) ->  bg_fisher
  
  png("./figures/3_02_dag_heatmap_not_mlfiltered.png", width = 10, height = 10, units = "cm", res = 600)
  dagHeatmap(
    testDAU(dag_seq, dagBackground = bg_fisher),
    type="diff",
    labels_col = c("P5","P4","P3","P2","P1"),
    display_numbers = TRUE
  )
  dev.off()
}


```

#Supplement Fig. 12a
```{r}
keyref <- keys(org.Hs.eg.db, keytype = "SYMBOL")
AnnotationDbi::select(
  org.Hs.eg.db, 
  keys=keyref,   ###gene name vector
  columns=c("SYMBOL","ENTREZID","GENENAME"),
  keytype="SYMBOL"
) -> gene_refs


peptide_lfq_trinity_distinct_arg %>% 
  mutate(
    MGTG_MG132 = MGTG-MG132
  ) %>%
  left_join(
    arginylome_validation_matrix3_sequence_distinct_trinity %>% 
      select(gene_position,loc,gene),
    join_by(gene_position == gene_position)
  ) %>% 
  select(gene,MGTG_MG132) %>% 
  arrange(desc(MGTG_MG132)) %>% 
  distinct(gene,.keep_all = TRUE) %>% 
  left_join(
    gene_refs,
    join_by(gene == SYMBOL)
  ) %>% 
  drop_na()-> temp_data

temp_data %>% pull(MGTG_MG132)->temp1
temp_data %>% pull(ENTREZID)->temp2
  
names(temp1) <- temp2

temp_data %>% pull(MGTG_MG132)->temp3
temp_data %>% pull(gene)->temp4
names(temp3) <- temp4

gsePathway(
  geneList = temp1,
  pvalueCutoff = 1
) -> gse_result_reactome

gse_result_reactome@result %>% 
  tibble() %>% 
  arrange(
    pvalue
  ) %>% 
  slice_head(n=10) %T>% 
  write_tsv(
    "./figures/4_12_gsea_reactome_tgovermg.tsv"
  ) %>% 
  ggplot(
    aes(
      x=NES,
      y=reorder(Description,NES),
      fill = NES
    )
  )+
  geom_bar(
    stat = "identity"
  )+
  scale_fill_gradient2(
    high = muted("red"),
    mid = "white",
    low = muted("blue"),
  )+
  labs(
    x="NES (MGTG/MG132)",
    y="Reactome"
  )+
  theme_bw()+
  theme(
    axis.text.x = element_text(color = "black",size= 8),
    axis.text.y =element_text(color = "black",size= 7),
    axis.title = element_text(color = "black",size= 8),
    plot.title = element_text(color = "black",size= 8),
    legend.position = "none",
    axis.ticks = element_line(color = "black"),
    legend.title = element_text(color = "black",size= 8),
    legend.text = element_text(color = "black",size= 8)
  )
ggsave(
  "./figures/4_12_gsea_reactome_tgovermg.png",height = 5, width =7,dpi = 600,units = "cm"
)
```


#Supplement Fig. 12b
```{r}

go_enriched_all %>% 
  select(ONTOLOGY,ID,Description,experiment,qvalue,fold_enrich) %>% 
  arrange(qvalue) %>% 
  filter(
    qvalue <0.01
  ) %>% 
  pull(ID) -> go_enriched_all_fdr001

go_enriched_all %>% 
  select(ONTOLOGY,ID,Description,experiment,qvalue,fold_enrich) %>% 
  arrange(qvalue) %>% 
  filter(
    ID %in% go_enriched_all_fdr001
  ) %>% 
  pivot_wider(
    id_cols = c(ONTOLOGY,ID,Description),
    names_from = experiment,
    values_from = qvalue
  ) %>%   mutate(truncated_desc = paste0(ID," ",str_sub(Description,1,30))) -> go_enriched_all_fig3
  

go_enriched_all_fig3 %>% 
  pivot_longer(
    MOCK:MGTG
  ) %>% 
  arrange(value) %T>% 
  write_tsv(
    "./figures/4_09_tile_GO_all.tsv"
  ) %>% 
  ggplot(
    aes(x=fct(name,levels=c("MOCK","MG132","MGTG")),y=fct(truncated_desc,levels = go_enriched_all_fig3 %>% pull(truncated_desc) %>% unique() %>% rev()),fill = -log(value,10))
  )+
  geom_tile(
    #width = 0.1
  )+
  scale_fill_distiller(
    palette = "YlOrRd",
    direction = 1,
    na.value = "grey80"
  )+
  labs(
    x="Experiment",
    y="GO description",
    fill = "Q value"
  )+
  theme_bw()+
  theme(
    axis.text.x = element_text(color = "black",size= 8,angle = 45, hjust=1),
    axis.text.y =element_text(color = "black",size= 8),
    axis.title = element_text(color = "black",size= 8),
    plot.title = element_text(color = "black",size= 8),
    legend.position = "none",
    axis.ticks = element_line(color = "black"),
    legend.title = element_text(color = "black",size= 8),
    legend.text = element_text(color = "black",size= 8)
  )
ggsave(
  "./figures/4_09_tile_GO_all_rev.png",height = 18, width =9,dpi = 600,units = "cm"
)

#for a legend
go_enriched_all_fig3 %>% 
  pivot_longer(
    MOCK:MGTG
  ) %>% 
  arrange(value) %T>% 
  write_tsv(
    "./figures/4_09_tile_GO_all.tsv"
  ) %>% 
  ggplot(
    aes(x=fct(name,levels=c("MOCK","MG132","MGTG")),y=fct(truncated_desc,levels = go_enriched_all_fig3 %>% pull(truncated_desc) %>% unique() %>% rev()),fill = -log(value,10))
  )+
  geom_tile(
    #width = 0.1
  )+
  scale_fill_distiller(
    palette = "YlOrRd",
    direction = 1,
    na.value = "grey80"
  )+
  labs(
    x="Experiment",
    y="GO description",
    fill = "Q value"
  )+
  theme_bw()+
  theme(
    axis.text.x = element_text(color = "black",size= 8,angle = 45, hjust=1),
    axis.text.y =element_text(color = "black",size= 8),
    axis.title = element_text(color = "black",size= 8),
    plot.title = element_text(color = "black",size= 8),
    legend.position = "top",
    axis.ticks = element_line(color = "black"),
    legend.title = element_text(color = "black",size= 8),
    legend.text = element_text(color = "black",size= 8)
  )
ggsave(
  "./figures/4_09_tile_GO_all_rev_legend.png",height = 18, width =18,dpi = 600,units = "cm"
)

```

#Supplement Fig. 12c-d
```{r}
#from 1Analysis_240711.R
table_go_cc_reduced_fdr0.05 %>% 
  filter(Count >2) %T>% 
  write_tsv(
    "./figures/4_13_tile_gocc_rev.tsv"
  ) %>% 
  ggplot(
    aes(
      x=fct(experiment,levels = c("MOCK","MG132","MGTG")),
      y=term,
      fill = -log(qvalue,10)
    )
  )+
  geom_tile()+
  scale_fill_distiller(
    palette = "YlOrRd",
    direction = 1,
    na.value = "grey80"
  )+
  labs(
    x="Experiment",
    y="GOCC Terms",
    fill = expression(-Log[10](FDR))
  )+
  theme_classic2()+
  theme(
    axis.text.x = element_text(color = "black",size= 7,angle = 45,hjust = 1),
    axis.text.y =element_text(color = "black",size= 8),
    axis.title = element_text(color = "black",size= 8,face="bold"),
    plot.title = element_text(color = "black",size= 8),
    legend.position = "none",
    axis.ticks = element_line(color = "black"),
    legend.title = element_text(color = "black",size=8),
    legend.text = element_text(color = "black",size= 8)
  )
ggsave(
  "./figures/4_13_tile_gocc_rev.png",height = 6, width =9,dpi = 600,units = "cm"
)

table_go_cc_reduced_fdr0.05 %>% 
  filter(Count >2) %>% 
  ggplot(
    aes(
      x=fct(experiment,levels = c("MOCK","MG132","MGTG")),
      y=term,
      fill = -log(qvalue,10)
    )
  )+
  geom_tile()+
  scale_fill_distiller(
    palette = "YlOrRd",
    direction = 1,
    na.value = "grey80"
  )+
  labs(
    x="Experiment",
    y="GOCC Terms",
    fill = expression(-Log[10](FDR))
  )+
  theme_classic2()+
  theme(
    axis.text.x = element_text(color = "black",size= 7,angle = 45,hjust = 1),
    axis.text.y =element_text(color = "black",size= 8),
    axis.title = element_text(color = "black",size= 8,face="bold"),
    plot.title = element_text(color = "black",size= 8),
    legend.position = "top",
    legend.location = "plot",
    axis.ticks = element_line(color = "black"),
    legend.title = element_text(color = "black",size=8),
    legend.text = element_text(color = "black",size= 8)
  )
ggsave(
  "./figures/4_13_tile_gocc_rev_legend.png",height = 6, width =9,dpi = 600,units = "cm"
)

table_go_cc_reduced_fdr0.05 %>% 
  filter(Count >2) %T>% 
  write_tsv(
    "./figures/4_13_tile_gocc_count_rev.tsv"
  ) %>% 
  ggplot(
    aes(
      x=fct(experiment,levels = c("MOCK","MG132","MGTG")),
      y=term,
      fill = Count
    )
  )+
  geom_tile()+
  scale_fill_distiller(
    palette = "YlOrRd",
    direction = 1,
    na.value = "grey80"
  )+
  labs(
    x="Experiment",
    y="GOCC Terms",
    fill = "Gene Count"
  )+
  theme_classic2()+
  theme(
    axis.text.x = element_text(color = "black",size= 7,angle = 45,hjust = 1),
    axis.text.y =element_text(color = "black",size= 8),
    axis.title = element_text(color = "black",size= 8,face="bold"),
    plot.title = element_text(color = "black",size= 8),
    legend.position = "none",
    axis.ticks = element_line(color = "black"),
    legend.title = element_text(color = "black",size=8),
    legend.text = element_text(color = "black",size= 8)
  )
ggsave(
  "./figures/4_13_tile_gocc_count_rev.png",height = 6, width =9,dpi = 600,units = "cm"
)

table_go_cc_reduced_fdr0.05 %>% 
  filter(Count >2) %T>% 
  write_tsv(
    "./figures/4_13_tile_gocc_count_rev.tsv"
  ) %>% 
  ggplot(
    aes(
      x=fct(experiment,levels = c("MOCK","MG132","MGTG")),
      y=term,
      fill = Count
    )
  )+
  geom_tile()+
  scale_fill_distiller(
    palette = "YlOrRd",
    direction = 1,
    na.value = "grey80"
  )+
  labs(
    x="Experiment",
    y="GOCC Terms",
    fill = "Gene Count"
  )+
  theme_classic2()+
  theme(
    axis.text.x = element_text(color = "black",size= 7,angle = 45,hjust = 1),
    axis.text.y =element_text(color = "black",size= 8),
    axis.title = element_text(color = "black",size= 8,face="bold"),
    plot.title = element_text(color = "black",size= 8),
    legend.position = "top",
    legend.location = "plot",
    axis.ticks = element_line(color = "black"),
    legend.title = element_text(color = "black",size=8),
    legend.text = element_text(color = "black",size= 8)
  )
ggsave(
  "./figures/4_13_tile_gocc_count_rev_legend.png",height = 6, width =9,dpi = 600,units = "cm"
)
```

#Supplement Fig. 13
```{r}
arginylome_validation_matrix3_sequence_distinct_trinity %>% 
  filter(
    MOCK >0
  ) %>%
  distinct(gene_position) %>% 
  mutate(
    gene_position = str_replace_all(gene_position,"\\|","_")
  ) %>% 
  pull(gene_position) ->gene_pos_mock_only

#a
peptide_lfq_trinity %>% 
  pivot_longer(MG132_1_Free:MOCK_2_Arg) %>% 
  drop_na(value) %>% 
  filter(
    gene_position %in% gene_pos_mock_only
  ) %>% 
  mutate(
    experiment = str_split_i(name,"_",1),
    arg = str_split_i(name,"_",3)
  ) %>% 
  ggplot(
    aes(x= factor(experiment, levels = c("MOCK","MG132","MGTG")), y = value, fill = factor(experiment, levels = c("MOCK","MG132","MGTG")))
  )+
  geom_violin(linewidth = 0.2,scale="width")+
  geom_boxplot(width = 0.1,linewidth = 0.2,outlier.size = 0)+
  labs(x="Experiments", y="Z-score",fill="name")+
  stat_compare_means(
    comparisons = list(c("MOCK","MG132"),c("MOCK","MGTG"),c("MG132","MGTG")),
    label = "p.format",
    method="t.test",
    label.y = c(4,4.8,4.3),
    size = 3
  )+
  scale_fill_manual(
    values =c(wesanderson::wes_palette(5,name="Zissou1",type="discrete")[c(1,3,5)]),
    labels = c("MOCK","MG132","MGTG")
  )+
  lims(
    y=c(-3.1,5.5)
  )+
  theme_classic2()+
  theme(
    legend.position = "none",
    # legend.title = element_blank(),
    # legend.text = element_text(size = 8,color="black"),
    # legend.key.width = unit(0.2,"cm"),
    # legend.key.height = unit(0.2,"cm"),
    # legend.margin = margin(t = 0, unit="cm"),
    # legend.box.margin = margin(t = 0, unit="cm"),
    # legend.box.spacing = unit(2, "pt"),
    #axis.ticks.x = element_blank(),
    #axis.text.x = element_blank(),
    axis.text = element_text(size = 8,color="black"),
    axis.title = element_text(size = 8,color="black"),
    strip.text= element_text(size = 8,color="black"),
    axis.title.x = element_blank(),
    axis.ticks = element_line(color = "black")
  )
ggsave(
  "./figures/4_08_mock_only_violin.png",height = 5, width =5,dpi = 600,units = "cm"
)

#b
arginylome_validation_matrix3_sequence_distinct_trinity %>% 
  filter(
    MOCK >0
  ) %>% 
  select(
    gene_position,MOCK,MG132,MGTG
  ) %>% 
  arrange(
    desc(gene_position)
  ) %>% 
  pivot_longer(MOCK:MGTG) %>% 
  mutate(
    value = na_if(value, 0)
  ) %>% 
  ggplot(
    aes(y=fct(name,levels=c("MGTG","MG132","MOCK")), x= fct(gene_position,levels = unique(gene_position)), fill = value)
  )+
  geom_tile()+
  geom_text(
    aes(label = value)
  )+
  scale_fill_distiller(
    palette = "YlOrRd",
    direction = 1,
    na.value = "grey80"
  )+
  labs(
    y="Experiment",
    x="Arginylated Sites only identified in MOCK",
    fill = "#PSMs"
  )+
  theme_bw()+
  theme(
    axis.text.x = element_text(color = "black",size= 7,angle = 45,hjust = 1),
    axis.text.y =element_text(color = "black",size= 8),
    axis.title = element_text(color = "black",size= 8),
    plot.title = element_text(color = "black",size= 8),
    legend.position = "right",
    axis.ticks = element_line(color = "black"),
    legend.title = element_text(color = "black",size= 8),
    legend.text = element_text(color = "black",size= 8)
  )+
  guides(
    fill=guide_colourbar(barwidth=0.5, barheight = 4,label.position="right")
  )
ggsave(
  "./figures/4_08_tile_mock.png",height = 5, width =12,dpi = 600,units = "cm"
)

arginylome_validation_matrix3_sequence_distinct_trinity %>% 
  filter(
    MOCK >0
  ) %>% 
  select(
    gene_position,argpair_MOCK,argpair_MG132,argpair_MGTG
  ) %>% 
  arrange(
    desc(gene_position)
  ) %>% 
  pivot_longer(cols=c(argpair_MOCK,argpair_MG132,argpair_MGTG)) %>% 
  mutate(
    value = na_if(value, 0)
  ) %>% 
  ggplot(
    aes(y=fct(name,levels=c("argpair_MGTG","argpair_MG132","argpair_MOCK")), x= fct(gene_position,levels = unique(gene_position)), fill = value)
  )+
  geom_tile()+
  geom_text(
    aes(label = value)
  )+
  scale_fill_distiller(
    palette = "YlOrRd",
    direction = 1,
    na.value = "grey80"
  )+
  scale_y_discrete(
    label = c("MGTG","MG132","MOCK")
  )+
  labs(
    y="Experiment",
    x="Arginylated Sites only identified in MOCK",
    fill = "#PSMs"
  )+
  theme_bw()+
  theme(
    axis.text.x = element_text(color = "black",size= 7,angle = 45,hjust = 1),
    axis.text.y =element_text(color = "black",size= 8),
    axis.title = element_text(color = "black",size= 8),
    plot.title = element_text(color = "black",size= 8),
    legend.position = "right",
    axis.ticks = element_line(color = "black"),
    legend.title = element_text(color = "black",size= 8),
    legend.text = element_text(color = "black",size= 8)
  )+
  guides(
    fill=guide_colourbar(barwidth=0.5, barheight = 4,label.position="right")
  )
ggsave(
  "./figures/4_08_tile_mock_free.png",height = 5, width =12,dpi = 600,units = "cm"
)


#c
arginylome_validation_matrix3_sequence_distinct_trinity %>% 
  left_join(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
    distinct(
      Sequence,p5p5prime
    )
  ) %>% 
  filter(
    MOCK >0 
  ) %>%
  # mutate(
  #   p5p5prime = str_replace(p5p5prime,"(?<=.....).","X")
  # ) %T>% 
  write_tsv(
    "./figures/sfig13_logo.tsv"
  ) %>% 
  pull(p5p5prime) %>% 
  ggseqlogo(
  )+
  theme(
    legend.position = "none"
  ) -> fig_logo
  
  fig_logo$scales$scales[[1]]$labels <- c("P5","P4","P3","P2","P1","P1'","P2'","P3'","P4'","P5'")
  fig_logo
  ggsave("./figures/sfig13_logo.png",width = 8,height = 8, units = "cm", dpi = 600)
```


#Supplement Fig. 14
```{r}

#a
arginylome_validation_matrix3_sequence_distinct_trinity %>% 
  left_join(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
    distinct(
      Sequence,p5p5prime
    )
  ) %>% 
  filter(
    MOCK >0 
  ) %>% 
  select(
    gene_position,Sequence, MOCK:MGTG, p5p5prime
  ) %T>%
  # mutate(
  #   p5p5prime = str_replace(p5p5prime,"(?<=.....).","X")
  # ) %T>% 
  write_tsv(
    "./figures/sfig14_mock.tsv"
  ) %>% 
  pull(p5p5prime) %>% 
  ggseqlogo(
  )+
  theme(
    legend.position = "none"
  ) -> fig_logo
  
  fig_logo$scales$scales[[1]]$labels <- c("P5","P4","P3","P2","P1","P1'","P2'","P3'","P4'","P5'")
  fig_logo
  ggsave("./figures/sfig14_mock.png",width = 8,height = 4, units = "cm", dpi = 600)
  
arginylome_validation_matrix3_sequence_distinct_trinity %>% 
  left_join(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      distinct(
        Sequence,p5p5prime
      )
  ) %>% 
  filter(
    MG132 >0 
  ) %>% 
  select(
    gene_position,Sequence, MOCK:MGTG, p5p5prime
  ) %T>%
  write_tsv(
    "./figures/sfig14_mg132.tsv"
  ) %>% 
  pull(p5p5prime) %>% 
  ggseqlogo(
  )+
  theme(
    legend.position = "none"
  ) -> fig_logo

fig_logo$scales$scales[[1]]$labels <- c("P5","P4","P3","P2","P1","P1'","P2'","P3'","P4'","P5'")
fig_logo
ggsave("./figures/sfig14_mg132.png",width = 8,height = 4, units = "cm", dpi = 600)

arginylome_validation_matrix3_sequence_distinct_trinity %>% 
  left_join(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      distinct(
        Sequence,p5p5prime
      )
  ) %>% 
  filter(
    MGTG >0 
  ) %>% 
  select(
    gene_position,Sequence, MOCK:MGTG, p5p5prime
  ) %T>%
  write_tsv(
    "./figures/sfig14_mgtg.tsv"
  ) %>% 
  pull(p5p5prime) %>% 
  ggseqlogo(
  )+
  theme(
    legend.position = "none"
  ) -> fig_logo

fig_logo$scales$scales[[1]]$labels <- c("P5","P4","P3","P2","P1","P1'","P2'","P3'","P4'","P5'")
fig_logo
ggsave("./figures/sfig14_mgtg.png",width = 8,height = 4, units = "cm", dpi = 600)

#d signal 
arginylome_validation_matrix3_sequence_distinct_trinity %>% 
  left_join(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      distinct(
        Sequence,p5p5prime
      )
  ) %>% 
  filter(cleavage_type=="SP") %>% 
  select(gene_position,Sequence,p5p5prime,cleavage_type,cleavage_score,source_cleavage) %T>% 
  write_tsv(
    "./figures/3_05_logo_trinity_signal.tsv"
  ) %>% 
  select(p5p5prime) -> logo_data


ggplot()+geom_logo(data = logo_data)+
  theme_logo()+
  theme(
    legend.position = "none"
  )->fig_logo

fig_logo$scales$scales[[1]]$labels <- c("P5","P4","P3","P2","P1","P1'","P2'","P3'","P4'","P5'")

fig_logo
ggsave("./figures/3_05_logo_trinity_signal.png",width=10,height=10,dpi = 600,units="cm")

##e transit

{
  arginylome_validation_matrix3_sequence_distinct_trinity %>% 
    left_join(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      distinct(
        Sequence,p5p5prime
      )
  ) %>% 
  filter(cleavage_type=="mTP") %>% 
  select(gene_position,Sequence,p5p5prime,cleavage_type,cleavage_score,source_cleavage) %T>% 
  write_tsv(
    "./figures/3_05_logo_trinity_transit.tsv"
  ) %>% 
  select(p5p5prime) -> logo_data
  
  ggplot()+geom_logo(data = logo_data)+
    theme_logo()+
    theme(
      legend.position = "none"
    )->fig_logo
  
  fig_logo$scales$scales[[1]]$labels <- c("P5","P4","P3","P2","P1","P1'","P2'","P3'","P4'","P5'")
  
  fig_logo
  ggsave("./figures/3_05_logo_trinity_transit.png",width=10,height=10,dpi = 600,units="cm")
}
##f NA

{
  arginylome_validation_matrix3_sequence_distinct_trinity %>% 
    left_join(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      distinct(
        Sequence,p5p5prime
      )
  ) %>% 
  filter(is.na(cleavage_type)) %>% 
  select(gene_position,Sequence,p5p5prime,cleavage_type,cleavage_score,source_cleavage) %T>% 
  write_tsv(
    "./figures/3_05_logo_trinity_cleavage_na.tsv"
  ) %>% 
  ggplot()+geom_logo(data = logo_data)+
    theme_logo()+
    theme(
      legend.position = "none"
    )->fig_logo
  
  fig_logo$scales$scales[[1]]$labels <- c("P5","P4","P3","P2","P1","P1'","P2'","P3'","P4'","P5'")
  
  fig_logo
  ggsave("./figures/3_05_logo_trinity_NA.png",width=10,height=10,dpi = 600,units="cm")
}


##g  caspase3

{
  arginylome_validation_matrix3_sequence_distinct_trinity %>% 
    left_join(
    summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
      distinct(
        Sequence,p5p5prime
      )
  ) %>% 
  filter(protease=="caspase-3") %>% 
  select(gene_position,Sequence,p5p5prime,cleavage_type,cleavage_score,source_cleavage) %T>% 
  write_tsv(
    "./figures/3_05_logo_trinity_caspase3.tsv"
  ) %>% 
  select(p5p5prime) -> logo_data
  
  ggplot()+geom_logo(data = logo_data)+
    theme_logo()+
    theme(
      legend.position = "none"
    )->fig_logo
  
  fig_logo$scales$scales[[1]]$labels <- c("P5","P4","P3","P2","P1","P1'","P2'","P3'","P4'","P5'")
  
  fig_logo
  ggsave("./figures/3_05_logo_trinity_caspase3.png",width=10,height=10,dpi = 600,units="cm")
}



```

#Supplement Fig. 15
```{r}
arginylome_validation_matrix3_sequence_distinct %>%  
  mutate(
    subloc=str_split_i(Localizations,"\\|",1),
    ml_filtered = if_else(score_sum ==3, "Passed","Failed")
  ) %>%
  select(
    prot_pos_reposition,Sequence,subloc,ml_filtered,MOCK,MG132,MGTG
  ) %>% 
  write_tsv(
    "./figures/sfig15.tsv"
  )


#a

arginylome_validation_matrix3_sequence_distinct %>% 
  mutate(
    subloc=str_split_i(Localizations,"\\|",1)
  ) %>%
  summarise(
    .by=c(subloc,trinity),
    count =n()
  ) %>% 
  pivot_wider(names_from = trinity,id_cols = subloc,values_from = count) %>% 
  mutate(
    subloc = fct(subloc,level = c("Extracellular","Cell membrane","Lysosome/Vacuole","Golgi apparatus","Endoplasmic reticulum","Cytoplasm","Nucleus","Mitochondrion")),
    Failed = replace_na(Failed,0),
    sum = Failed+Passed,
    perc = percent(Passed/sum,accuracy=1),
    text = paste0(perc)
  ) %>% arrange(subloc) %>% .$text -> fig_3_02_text

arginylome_validation_matrix3_sequence_distinct %>% 
  mutate(
    subloc=str_split_i(Localizations,"\\|",1),
    ml_filtered = if_else(score_sum ==3, "Passed","Failed")
  ) %>%
  summarise(
    .by=c(subloc,ml_filtered),
    count =n()
  ) %T>% 
  write_tsv(
    "./figures/3_02_removed_arg_subloc.tsv"
  ) %>% 
  ggplot(
    aes(x=fct(subloc,level = c("Extracellular","Cell membrane","Lysosome/Vacuole","Golgi apparatus","Endoplasmic reticulum","Cytoplasm","Nucleus","Mitochondrion")),y=count,fill=ml_filtered)
  )+
  geom_bar(stat="identity",color="black",linewidth = 0.1)+
  annotate(
    geom = "text",
    x=1:8,
    y=220,
    label = fig_3_02_text,
    size = 3
  )+
  #geom_text(aes(label=count),position = position_stack(vjust=0.5),size=3)+
  scale_fill_manual(
    values = c(wesanderson::wes_palette("Royal1")[2],wesanderson::wes_palette("Royal1")[3])
  )+
  labs(x="Subcellular Localization",y="Site Count",fill="TrinityNmod")+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.text = element_text(color="black",size=8),
    axis.text.x = element_text(angle=45,hjust=1),
    axis.title = element_text(color="black",size = 10)
  )
ggsave("./figures/3_02_removed_arg_subloc.png",width=8,height=8, units = "cm",dpi = 600)


#b
arginylome_validation_matrix3_sequence_distinct %>% 
  filter(MOCK>0) %>% 
  mutate(
    subloc=str_split_i(Localizations,"\\|",1)
  ) %>%
  summarise(
    .by=c(subloc,trinity),
    count =n()
  ) %>% 
  pivot_wider(names_from = trinity,id_cols = subloc,values_from = count) %>% 
  mutate(
    subloc = fct(subloc,level = c("Extracellular","Cell membrane","Lysosome/Vacuole","Golgi apparatus","Endoplasmic reticulum","Cytoplasm","Nucleus","Mitochondrion")),
    Failed = replace_na(Failed,0),
    Passed = replace_na(Passed,0),
    sum = Failed+Passed,
    perc = percent(Passed/sum,accuracy=0.1),
    text = paste0(perc)
  ) %>% arrange(subloc) %>% .$text -> fig_3_02_text_mock

arginylome_validation_matrix3_sequence_distinct %>% 
  filter(MOCK>0) %>% 
  mutate(
    subloc=str_split_i(Localizations,"\\|",1),
    ml_filtered = if_else(score_sum ==3, "Passed","Failed")
  ) %>%
  summarise(
    .by=c(subloc,ml_filtered),
    count =n()
  ) %T>% 
  write_tsv(
    "./figures/3_02_removed_arg_subloc_mock.tsv"
  ) %>% 
  ggplot(
    aes(x=fct(subloc,level = c("Extracellular","Cell membrane","Lysosome/Vacuole","Golgi apparatus","Endoplasmic reticulum","Cytoplasm","Nucleus","Mitochondrion")),y=count,fill=ml_filtered)
  )+
  geom_bar(stat="identity",color="black",linewidth = 0.1)+
  annotate(
    geom = "text",
    x=1:5,
    y=65,
    label = fig_3_02_text_mock,
    size = 2.3
  )+
  #geom_text(aes(label=count),position = position_stack(vjust=0.5),size=3)+
  scale_fill_manual(
    values = c(wesanderson::wes_palette("Royal1")[2],wesanderson::wes_palette("Royal1")[3])
  )+
  labs(x="Subcellular Localization",y="Count",fill="TrinityNmod")+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.text = element_text(color="black",size=8),
    axis.text.x = element_text(angle=45,hjust=1),
    axis.title = element_text(color="black",size = 10)
  )
ggsave("./figures/3_02_removed_arg_subloc_mock.png",width=8,height=8, units = "cm",dpi = 600)

#c
arginylome_validation_matrix3_sequence_distinct %>% 
  filter(MG132>0) %>% 
  mutate(
    subloc=str_split_i(Localizations,"\\|",1)
  ) %>%
  summarise(
    .by=c(subloc,trinity),
    count =n()
  ) %>% 
  pivot_wider(names_from = trinity,id_cols = subloc,values_from = count) %>% 
  mutate(
    subloc = fct(subloc,level = c("Extracellular","Cell membrane","Lysosome/Vacuole","Golgi apparatus","Endoplasmic reticulum","Cytoplasm","Nucleus","Mitochondrion")),
    Failed = replace_na(Failed,0),
    Passed = replace_na(Passed,0),
    sum = Failed+Passed,
    perc = percent(Passed/sum,accuracy=0.1),
    text = paste0(perc)
  ) %>% arrange(subloc) %>% .$text -> fig_3_02_text_mg132

arginylome_validation_matrix3_sequence_distinct %>% 
  filter(MG132>0) %>% 
  mutate(
    subloc=str_split_i(Localizations,"\\|",1),
    ml_filtered = if_else(score_sum ==3, "Passed","Failed")
  ) %>%
  summarise(
    .by=c(subloc,ml_filtered),
    count =n()
  ) %T>% 
  write_tsv(
    "./figures/3_02_removed_arg_subloc_mg132.tsv"
  ) %>% 
  ggplot(
    aes(x=fct(subloc,level = c("Extracellular","Cell membrane","Lysosome/Vacuole","Golgi apparatus","Endoplasmic reticulum","Cytoplasm","Nucleus","Mitochondrion")),y=count,fill=ml_filtered)
  )+
  geom_bar(stat="identity",color="black",linewidth = 0.1)+
  annotate(
    geom = "text",
    x=1:8,
    y=90,
    label = fig_3_02_text_mg132,
    size = 2.3
  )+
  #geom_text(aes(label=count),position = position_stack(vjust=0.5),size=3)+
  scale_fill_manual(
    values = c(wesanderson::wes_palette("Royal1")[2],wesanderson::wes_palette("Royal1")[3])
  )+
  labs(x="Subcellular Localization",y="Count",fill="TrinityNmod")+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.text = element_text(color="black",size=8),
    axis.text.x = element_text(angle=45,hjust=1),
    axis.title = element_text(color="black",size = 10)
  )
ggsave("./figures/3_02_removed_arg_subloc_mg132.png",width=8,height=8, units = "cm",dpi = 600)

#d
arginylome_validation_matrix3_sequence_distinct %>% 
  filter(MGTG>0) %>% 
  mutate(
    subloc=str_split_i(Localizations,"\\|",1)
  ) %>%
  summarise(
    .by=c(subloc,trinity),
    count =n()
  ) %>% 
  pivot_wider(names_from = trinity,id_cols = subloc,values_from = count) %>% 
  mutate(
    subloc = fct(subloc,level = c("Extracellular","Cell membrane","Lysosome/Vacuole","Golgi apparatus","Endoplasmic reticulum","Cytoplasm","Nucleus","Mitochondrion")),
    Failed = replace_na(Failed,0),
    Passed = replace_na(Passed,0),
    sum = Failed+Passed,
    perc = percent(Passed/sum,accuracy=0.1),
    text = paste0(perc)
  ) %>% arrange(subloc) %>% .$text -> fig_3_02_text_mgtg

arginylome_validation_matrix3_sequence_distinct %>% 
  filter(MGTG>0) %>% 
  mutate(
    subloc=str_split_i(Localizations,"\\|",1),
    ml_filtered = if_else(score_sum ==3, "Passed","Failed")
  ) %>%
  summarise(
    .by=c(subloc,ml_filtered),
    count =n()
  ) %T>% 
  write_tsv(
    "./figures/3_02_removed_arg_subloc_mgtg.tsv"
  ) %>% 
  ggplot(
    aes(x=fct(subloc,level = c("Extracellular","Cell membrane","Lysosome/Vacuole","Golgi apparatus","Endoplasmic reticulum","Cytoplasm","Nucleus","Mitochondrion")),y=count,fill=ml_filtered)
  )+
  geom_bar(stat="identity",color="black",linewidth = 0.1)+
  annotate(
    geom = "text",
    x=1:7,
    y=125,
    label = fig_3_02_text_mgtg,
    size = 2.3
  )+
  #geom_text(aes(label=count),position = position_stack(vjust=0.5),size=3)+
  scale_fill_manual(
    values = c(wesanderson::wes_palette("Royal1")[2],wesanderson::wes_palette("Royal1")[3])
  )+
  labs(x="Subcellular Localization",y="Count",fill="TrinityNmod")+
  theme_classic2()+
  theme(
    legend.position = "none",
    axis.text = element_text(color="black",size=8),
    axis.text.x = element_text(angle=45,hjust=1),
    axis.title = element_text(color="black",size = 10)
  )
ggsave("./figures/3_02_removed_arg_subloc_mgtg.png",width=8,height=8, units = "cm",dpi = 600)

```

#rev2.2
```{r}
read_tsv(
      "C:/Users/admin/alphapeptdeep/project_backup/folder/alphapeptdeep/inrich/output/output_metrics_pretrained_model_trypsin_231206.tsv"
    ) %>% 
      mutate(
        model = "pretrained"
      ) %>% 
      bind_rows(
        read_tsv(
          "C:/Users/admin/alphapeptdeep/project_backup/folder/alphapeptdeep/inrich/output/output_metrics_built_model_trypsin_231206.tsv"
        ) %>% 
          mutate(
            model = "built"
          )
      ) %>% 
      bind_rows(
        read_tsv(
          "C:/Users/admin/alphapeptdeep/project_backup/folder/alphapeptdeep/inrich/output/output_metrics_describ_for_311547_trypsin_231130.tsv"
        ) %>% 
          mutate(
            model = "finetuned"
          )
      ) %>% 
      bind_rows(
        read_tsv(
          "C:/Users/admin/alphapeptdeep/project_backup/folder/alphapeptdeep/inrich/output/output_metrics_describ_for_311547_wo_arg_trypsin_231213.tsv"
        ) %>% 
          mutate(
            model = "finetunedwoarg"
          )
      )-> output_prediction_comparison_trypsin_for_rev22

output_prediction_comparison_trypsin_for_rev22 %>%
      mutate(
        model = fct(model,levels=c("pretrained","built","finetuned","finetunedwoarg"))
      ) %>% 
  filter(
    str_detect(mods,"Acetyl\\@Any")
  ) %T>% 
  write_tsv(
    "./figures/rev22_result.tsv"
  ) %>% 
      ggplot(aes(x=model,y=PCC))+
      geom_violin(aes(fill = model),linewidth = 0.1,scale = "width")+
      labs(y="PCC")+
      geom_boxplot(width = 0.1,outlier.shape = NA,linewidth = 0.1)+
      scale_x_discrete(labels =c("Pretrained","From scratch","Fine-tuned","Fine-tuned w/o\nArg-starting peptides"))+
      scale_fill_manual(
        values = c("#4DAF4A","#377EB8","#E41A1C","#984EA3")
      )+
      scale_y_continuous(
        limits=c(0,1)
      )+
      theme_classic2()+
      theme(
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_text(color = "black",size = 7),
        axis.text.x = element_text(size=5),
        axis.text.y = element_text(color = "black",size = 7)
      )
    ggsave("./figures/rev22_result.png",width =15, height = 10,dpi = 600,units = "cm")
    
output_prediction_comparison_trypsin_for_rev22 %>%
  mutate(
    model = fct(model,levels=c("pretrained","built","finetuned","finetunedwoarg"))
  ) %>% 
  filter(
    str_detect(mods,"Acetyl\\@Any")
  ) %>% 
  summarize(
    .by = model,
    median(PCC)
  )
```

#rev2.7
```{r}
arginylome_validation_matrix3_sequence_distinct_trinity %>% 
        distinct(Sequence) %>% pull(Sequence)

peptide_lfq_all %>% 
  filter(
    Sequence %in% c(arginylome_validation_matrix3_sequence_distinct_trinity %>% 
        distinct(Sequence) %>% pull(Sequence))
  ) %>% 
  pivot_longer(
    MG132_1_Acetyl:MOCK_2_Arg
  ) %>% 
  drop_na(value) %>% 
  mutate(
    value = log(value,10),
    type = case_when(
      str_detect(name,"Arg")~"Arg",
      str_detect(name,"Acetyl")~"Acetyl",
      str_detect(name,"Free")~"Unmodified"
    ),
    data_name = str_extract(name,"^[A-Z0-9]+\\_[1-2]"),
    data_name = fct(data_name,levels = c("MOCK_1","MOCK_2","MG132_1","MG132_2","MGTG_1","MGTG_2"))
  ) %T>% 
  write_tsv(
    "./figures/reviewer2_7.tsv"
  ) %>%
  ggplot(
    aes(x=data_name,y=value,fill=type)
  )+
  geom_boxplot()+
  labs(
    y="Log10 LFQ Intensity",
    x="Experiments (Treatment_Replicate)"
  )
ggsave("./figures/reviewer2_7.png",width = 20,height = 12, units = "cm", dpi = 600)
  
peptide_lfq_all %>% 
  filter(
    Sequence %in% c(
      arginylome_validation_matrix3_sequence_distinct_trinity %>% 
        filter(str_detect(protease,"caspase")) %>% 
        distinct(Sequence) %>% 
        pull(Sequence)
    )
  ) %>% 
  pivot_longer(
    MG132_1_Acetyl:MOCK_2_Arg
  ) %>% 
  drop_na(value) %>% 
  mutate(
    value = log(value,10),
    type = case_when(
      str_detect(name,"Arg")~"Arg",
      str_detect(name,"Acetyl")~"Acetyl",
      str_detect(name,"Free")~"Unmodified"
    ),
    data_name = str_extract(name,"^[A-Z0-9]+\\_[1-2]"),
    data_name = fct(data_name,levels = c("MOCK_1","MOCK_2","MG132_1","MG132_2","MGTG_1","MGTG_2"))
  ) %T>% 
  write_tsv(
    "./figures/reviewer2_7_caspase.tsv"
  ) %>% 
  ggplot(
    aes(x=data_name,y=value,fill=type)
  )+
  geom_boxplot()+
  labs(
    y="Log10 LFQ Intensity",
    x="Experiments (Treatment_Replicate)"
  )
ggsave("./figures/reviewer2_7_caspase.png",width = 15,height = 10, units = "cm", dpi = 600)

peptide_lfq_all %>% 
  filter(
    Sequence %in% c(
      arginylome_validation_matrix3_sequence_distinct_trinity %>% 
        filter(str_detect(Localizations,"^Extracellular$")) %>% 
        distinct(Sequence) %>% 
        pull(Sequence)
    )
  ) %>% 
  pivot_longer(
    MG132_1_Acetyl:MOCK_2_Arg
  ) %>% 
  drop_na(value) %>% 
  mutate(
    value = log(value,10),
    type = case_when(
      str_detect(name,"Arg")~"Arg",
      str_detect(name,"Acetyl")~"Acetyl",
      str_detect(name,"Free")~"Unmodified"
    ),
    data_name = str_extract(name,"^[A-Z0-9]+\\_[1-2]"),
    data_name = fct(data_name,levels = c("MOCK_1","MOCK_2","MG132_1","MG132_2","MGTG_1","MGTG_2"))
  ) %T>% 
  write_tsv(
    "./figures/reviewer2_7_secreted.tsv"
  ) %>% 
  ggplot(
    aes(x=data_name,y=value,fill=type)
  )+
  geom_boxplot()+
  labs(
    y="Log10 LFQ Intensity",
    x="Experiments (Treatment_Replicate)"
  )
ggsave("./figures/reviewer2_7_secreted.png",width = 15,height = 10, units = "cm", dpi = 600)

peptide_lfq_all %>% 
  filter(
    Sequence %in% c(
      arginylome_validation_matrix3_sequence_distinct_trinity %>% 
        filter(gene_position %in% c("LSM3|7","EIF4B|46","IGFBP4|22","TMEM59|36","UQCRHL|15")) %>% 
        distinct(Sequence) %>% 
        pull(Sequence)
    )
  ) %>% 
  pivot_longer(
    MG132_1_Acetyl:MOCK_2_Arg
  ) %>% 
  drop_na(value) %>% 
  mutate(
    value = log(value,10),
    type = case_when(
      str_detect(name,"Arg")~"Arg",
      str_detect(name,"Acetyl")~"Acetyl",
      str_detect(name,"Free")~"Unmodified"
    ),
    data_name = str_extract(name,"^[A-Z0-9]+"),
    data_name = fct(data_name,levels = c("MOCK","MG132","MGTG"))
  ) %T>% 
  write_tsv(
    "./figures/reviewer2_7_selectedgene.tsv"
  ) %>% 
  ggplot(
    aes(x=data_name,y=value,fill=type)
  )+
  geom_boxplot()+
  facet_wrap(
    vars(gene),
    ncol = 5
  )+
  labs(
    y="Log10 LFQ Intensity",
    x="Experiments (Treatment)"
  )+
  theme(
    axis.text.x = element_text(angle = 45,hjust = 1)
  )
ggsave("./figures/reviewer2_7_selected_gene.png",width = 15,height = 8, units = "cm", dpi = 600)


```





