---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

#Libraries
```{r}
library(tidyverse)
library(devtools)
library(Biostrings)
library(Peptides)
library(ggpubr)
library(RColorBrewer)
library(ggseqlogo)
library(dagLogo)
library(wesanderson)
library(Rdisop)
library(conflicted)
library(broom)
library(OrgMassSpecR) 
library(scales)
conflict_scout()
conflicts_prefer(dplyr::filter())
conflicts_prefer(dplyr::select())
conflicts_prefer(dplyr::rename())
conflicts_prefer(dplyr::first())
conflicts_prefer(dplyr::desc())
source("G:/Rcheatsheet/functions/FragmentPeptide3.R")
library(tidymodels)
library(ComplexHeatmap)
library(ggpointdensity)
library(viridis)
library(ggVennDiagram)
library(clusterProfiler)
library(org.Hs.eg.db)
Sys.setenv(R_LIBCURL_SSL_REVOKE_BEST_EFFORT=TRUE)
library(ReactomePA)
library(rrvgo)
library(UniProtKeywords)
library(org.Hs.eg.db)
library(ggrepel)
```

#Vectors
```{r}
summaryfolder<-"./Summary/"
peptidefile <- "200821_HELA_MGTG_iNrich_bRP_F_PeptideGroups.txt"
psmfile <- "200821_HELA_MGTG_iNrich_bRP_F_PSMs.txt"
msmsfile <- "200821_HELA_MGTG_iNrich_bRP_F_MSMSSpectrumInfo.txt"
```

#Make up protein Database
```{r}
####DB collection
dbfile <- paste0(summaryfolder,"UP000005640_9606_2302.fasta")
readAAStringSet(dbfile)->db1 ##Biostrings package
protein = names(db1)
sequence = paste(db1)
data.frame(protein,sequence)->dbtable
rm(db1)
dbtable %>% mutate(
  accession = str_extract(protein,"(?<=\\|).+(?=\\|)")
) -> dbtable ##db extraction of accession
dbtable %>% mutate(
  gene = str_extract(protein,"(?<=GN\\=)[a-zA-Z0-9\\-]+")
) %>% 
  mutate(
    prot_name = str_extract(protein,"[A-Z0-9]+\\_HUMAN")
  )-> dbtable ##db extraction of gene



####DB collection
dbfile_1 <- paste0("./db/UP000005640_9606_2302.fasta")
dbfile_2 <- paste0("./db/UP000005640_9606_2302_additional.fasta")
readAAStringSet(dbfile_1)->db1 ##Biostrings package
protein = names(db1)
sequence = paste(db1)
data.frame(protein,sequence)->dbtable1
readAAStringSet(dbfile_2)->db2 ##Biostrings package
protein = names(db2)
sequence = paste(db2)
data.frame(protein,sequence)->dbtable2
bind_rows(dbtable1,dbtable2) -> dbtable_all
rm(db1,db2)


dbtable_all %>% 
  mutate(
    accession = str_extract(protein,"(?<=\\|).+(?=\\|)")
  ) %>% mutate(
    gene = str_extract(protein,"(?<=GN\\=)[a-zA-Z0-9\\-]+")
  ) %>% 
  mutate(
    prot_name = str_extract(protein,"[A-Z0-9]+\\_HUMAN")
  ) -> dbtable_all ##db extraction of gene
  
  rm(dbtable1,dbtable2)
```

#PD output: read peptide result
output object: summaryfile
```{r}
###Read peptide file
  read_tsv(paste0(summaryfolder,peptidefile)) -> summaryfile
  
  summaryfile %>% distinct(Sequence,Modifications) ## check seq+mod uniqueness 
  
  ##N-term peps:: deconvolution of protein accessions 220407
  summaryfile %>% 
    separate_rows(.,`Positions in Master Proteins`,sep = "; ") -> summaryfile ##deconvolution of accessions
  
  summaryfile %>% 
    arrange(Sequence,Modifications,`Positions in Master Proteins`) -> summaryfile #sort by postion with increasing order
  
  summaryfile %>%
    distinct(Sequence,Modifications, .keep_all = TRUE) -> summaryfile #delete redundant pep+mod
  
  
  ##protein accession, separate first only ## deprecated 220407
  ##summaryfile %>% separate(`Master Protein Accessions`,into="Accessions.Single",sep=";",remove=FALSE)-> summaryfile ###delimiter
  
  ##protein position
  #summaryfile %>% separate(`Positions in Master Proteins`, into="Position", sep=";", remove=FALSE)-> summaryfile ###Position string extraction
  
  ##protein position string
  summaryfile %>% mutate(Accessions.Single = str_extract(`Positions in Master Proteins`, "[a-zA-Z0-9]+(?=[:blank:])")) %>%
    mutate(Position.start = str_extract(`Positions in Master Proteins`,"[0-9]+\\-[0-9]+")) %>% 
    separate(`Position.start`, into=c("Position.start","Position.end"), sep="-", remove=FALSE, convert=TRUE)->summaryfile ###position number extraction
  
  ##nmod start
  summaryfile %>% mutate(nmod = str_extract(Modifications,"1x[a-zA-Z0-9\\>\\:\\-\\(\\)\\+]+ \\[N\\-Term\\]"))->summaryfile ###nmod extraction
  summaryfile %>% mutate(nmod = gsub("1xAcetyl [N-Term]","Acetyl", nmod, fixed=TRUE)) %>%
    mutate(nmod = gsub("1xAcetyl:2H(3) [N-Term]","D3Acetyl", nmod, fixed=TRUE)) %>% 
    mutate(nmod = gsub("1xGlu->pyro-Glu [N-Term]","pyroGlu", nmod, fixed=TRUE)) %>%
    #mutate(nmod = gsub("1xMet-loss+AcetylD3 [N-Term]","MetLossD3Acetyl", nmod, fixed=TRUE)) %>%
    mutate(nmod = gsub("1xArgAcetylD3 [N-Term]","D3AcetylArg", nmod, fixed=TRUE)) %>%
    mutate(nmod = gsub("1xArgAcetylD3NQ [N-Term]","D3AcetylArgDeamid", nmod, fixed=TRUE)) ->summaryfile ##unique(summaryfiletemp$nmod) ## simplifying nmods
  #mutate(nmod = gsub("1xMet-LossArgAcD3NQ [N-Term]","MetLossD3AcetylArgDeamid", nmod, fixed=TRUE)) %>%
  #mutate(nmod = gsub("1xMet-lossArgAcD3 [N-Term]","MetLossD3AcetylArg", nmod, fixed=TRUE)) %>%
  #mutate(nmod = gsub("1xMet-loss [N-Term]",NA, nmod, fixed=TRUE))
  
  
  ##filter contaminant & peptide without reference
  summaryfile %>% 
    dplyr::filter(Contaminant == FALSE) %>%
    dplyr::filter(!is.na(`Master Protein Accessions`)) -> summaryfile
  
  ### db integration 
  left_join(
    summaryfile,dbtable,by=c("Accessions.Single"="accession")
  ) ->summaryfile ##db integration
  
  ### XXX addition
  summaryfile %>% 
    mutate(
      sequence2 = paste0("XXXXX",sequence)
    ) %>%
    mutate(
      p5p1 = str_sub(sequence2,Position.start,Position.start+4)
    ) ->summaryfile
```

#PD output: read PSM result, Mod annotations
output object: summaryfile_psm, summaryfile_psm_arg
```{r}
read_tsv(paste0(summaryfolder,psmfile)) -> summaryfile_psm
summaryfile_psm %>% 
  mutate(
    index = seq(1:nrow(summaryfile_psm))
  ) %>% 
  separate(`Master Protein Accessions`,into="Accessions_Single",sep=";",remove=FALSE) %>% 
  mutate(
    nmod = str_extract(
      Modifications,
      "N\\-Term[a-zA-Z0-9\\>\\:\\-\\(\\)\\+]+"
    )
  )->summaryfile_psm ###nmod extraction

summaryfile_psm %>% mutate(
  nmod = gsub("N-Term(Acetyl)","Acetyl", nmod, fixed=TRUE)
) %>% mutate(
  nmod = gsub("N-Term(Acetyl:2H(3))","D3Acetyl", nmod, fixed=TRUE)
) %>% mutate(
  nmod = gsub("N-Term(Glu->pyro-Glu)","pyroGlu", nmod, fixed=TRUE)
) %>% mutate(
  nmod = gsub("N-Term(ArgAcetylD3)","D3AcetylArg", nmod, fixed=TRUE)
) %>% mutate(
  nmod = gsub("N-Term(ArgAcetylD3NQ)","D3AcetylArgDeamid", nmod, fixed=TRUE)
) ->summaryfile_psm ##unique(summaryfiletemp$nmod) ## simplifying nmods

summaryfile_psm %>% 
  select(
    `File ID`,`Spectrum File`
  ) %>% distinct()->file_raw_index

file_raw_index %>% 
  mutate(
    set = str_extract(`File ID`,"^[A-Z0-9]+(?=\\.)")
  ) %>% 
  mutate(
    fraction = str_extract(`File ID`,"(?<=\\.)[A-Z0-9]+") %>% as.integer()
  ) %>% 
  mutate(
    file_name = str_extract(`Spectrum File`,".+(?=.{6}$)")
  ) -> file_raw_index

file_raw_index %>% 
  distinct(set,file_name) %>% 
  bind_cols(
    tibble(
      experiment = c("MGTG","MOCK","MOCK","MG132","MGTG","MG132","MGTG","MOCK","MOCK","MG132","MGTG","MG132")
    )
  ) %>% 
  bind_cols(
    tibble(
      replicate = c("1ST","1ST","2ND","2ND","2ND","1ST","1ST","1ST","2ND","2ND","2ND","1ST")
    )
  ) %>% 
  bind_cols(
    tibble(
      enzyme = c("trypsin","trypsin","trypsin","trypsin","trypsin","trypsin","chymotrypsin","chymotrypsin","chymotrypsin","chymotrypsin","chymotrypsin","chymotrypsin")
    )
  ) -> file_raw_index2
  
file_raw_index %>% 
  left_join(
    file_raw_index2,
    join_by(
      set==set,
      file_name == file_name
    )
  ) %>% 
  select(
    -c(`Spectrum File`,file_name)
  ) ->file_raw_index

summaryfile_psm %>% 
  left_join(
    file_raw_index,
    join_by(
      `File ID` ==`File ID`
    )
  ) -> summaryfile_psm
rm(file_raw_index2)

##make arginylation column
summaryfile_psm %>% mutate(
  arginylation = ifelse(
    grepl("Arg", nmod),
    TRUE,
    FALSE
  )
) -> summaryfile_psm

summaryfile_psm %>% 
  mutate(
    start_with_R = if_else(str_detect(Sequence,"^R"),1,0)
  ) -> summaryfile_psm

summaryfile_psm %>% 
  dplyr::filter(
    arginylation == TRUE
  ) -> summaryfile_psm_arg
```

#Annotations: possible positions for the peptide sequences 
output object: arginylated_peptides_all, reposition_arg, reposition_arg_no_dups
```{r}
summaryfile %>% 
    dplyr::filter(arginylation == TRUE) -> summaryfile_arg
  
  summaryfile_psm %>% dplyr::filter(arginylation==TRUE) %>% .$Sequence %>% unique -> arginylated_peptides_all
  
tibble(
  seq = arginylated_peptides_all
) %>% 
  mutate(
    protein = map(seq,\(x) dbtable_all %>% dplyr::filter(str_detect(sequence,x)),.progress=TRUE)
  ) %>% 
  unnest(protein) %>% 
  mutate(
    position = str_locate(sequence,seq)[,"start"]
  ) %>% 
  arrange(
    seq,position
  )  %>% 
  mutate(
    sequence2=paste0("XXXXX",sequence)
  ) %>% 
  mutate(
    p5p1 = str_sub(sequence2,start=position,end=position+4)
  ) %>% 
  mutate(
    reviewed = str_sub(protein,start=1,end=2)
  ) %>% 
  mutate(
    under100 = if_else(
      position <= 100, 1,0
    )
  ) %>% 
  arrange(
    seq,desc(under100),reviewed,position,accession
  ) %>% 
  mutate(
    count = n(),.by=seq
  ) ->reposition_arg
reposition_arg %>% 
  nest(
    .by=seq
  ) %>% 
  mutate(
    data = map(data,\(x) slice_head(x,n=1))
  ) %>% 
  unnest(data)->reposition_arg_no_dups
  
  
  reposition_arg %>%
    select(-c(sequence,sequence2)) %>% 
    write_tsv("reposition_arg.tsv")
  reposition_arg_no_dups %>%
    select(-c(sequence,sequence2)) %>% 
    write_tsv("reposition_arg_no_dups.tsv")
```

#Training data conversion
##Strings handling from PSM files
output object: summaryfile_psm_for_training
```{r}
summaryfile_psm %>% 
  dplyr::filter(start_with_R==1) %>%
  #dplyr::filter(enzyme == "trypsin") %>% for trypsin only
  #dplyr::filter(specfile %in% c("220621_E_1","220621_E_2","220621_E_3")) %>% for single set only
  dplyr::filter(nmod=="D3Acetyl") -> summaryfile_psm_for_training


summaryfile_psm_for_training %>%   
  mutate(index=1:nrow(.)) %>% 
  separate_longer_delim(Modifications, delim="; ") %>% 
  mutate(
    mods_aa = case_when(
      str_detect(Modifications,"^N\\-Term")~"Any N-term",
      str_detect(Modifications,"^[A-Z]")~str_extract(Modifications,"^[A-Z]"),
      .default = Modifications
    )
  ) %>% 
  mutate(
    mods_name = case_when(
      str_detect(Modifications,"Acetyl\\)")~"Acetyl",
      str_detect(Modifications,"Acetyl\\:2H\\(3\\)")~"Acetyl:2H(3)",
      str_detect(Modifications,"Oxidation")~"Oxidation",
      str_detect(Modifications,"Carbamidomethyl")~"Carbamidomethyl",
      .default = Modifications
    )
  ) %>% 
  mutate(
    mod_sites = case_when(
      str_detect(Modifications,"^N\\-Term")~"0",
      str_detect(Modifications,"^[A-Z]")~str_extract(Modifications,"(?<=^[A-Z])[0-9]+"),
      .default = Modifications
    )
  ) %>% 
  nest(nestedcol = c(Modifications,mods_name,mods_aa,mod_sites)) %>% 
  mutate(
    Modifications = map_chr(nestedcol,\(x) x$Modifications %>% paste(collapse = ";"))
  ) %>% 
  mutate(
    mods = map_chr(nestedcol,\(x) unite(data = x, col = mods, c(mods_name,mods_aa),sep ="@") %>% .$mods %>% paste(collapse = ";"))
  ) %>% 
  mutate(
    mod_sites = map_chr(nestedcol,\(x) x$mod_sites %>% paste(collapse = ";"))
  )%>% 
  mutate(
    nAA = str_length(Sequence),
    nce = as.integer(27),
    instrument = "QE",
    charge = as.integer(Charge)
  )-> summaryfile_psm_for_training
```

##Reading PSM annotations output from Proteome Discoverer
output object: file_index
```{r}
folder_pdspectra <- "./annotation_psm/200821_HELA_MGTG_iNrich_bRP_F_startR/"
  ##read xml
  xml2::read_html(
    paste0(folder_pdspectra,"index.html")
  ) -> file_index
  #from xml object read table
  rvest::html_table(
    file_index,
    header = TRUE
  ) ->file_index
  
  ##table trimming
  file_index[[1]] -> file_index #unlist
  file_index[seq(1,nrow(file_index),by=2),seq(2,ncol(file_index),by=2)] -> file_index ## delete unnessary cols and rows
  colnames(file_index)<- as.vector(file_index[1,]) %>% unlist ## colnames
  file_index[c(-1),] -> file_index
  
  #peak list handling
  readLines(paste0(folder_pdspectra,"index.html"))-> file_index_lines
  
  ##add column of peak list
  file_index %>% 
    bind_cols(tibble(peak_file = str_extract(file_index_lines[str_detect(file_index_lines,"Peak List")],"data\\/.+\\.txt"))) -> file_index
  
  file_index %>% 
    mutate(
      peak_table = map(
        peak_file,\(x) read_tsv(paste0(folder_pdspectra,x),show_col_types = FALSE), .progress = TRUE
      )
    )->file_index2
  file_index2->file_index
  rm(file_index2)
  file_index %>% 
    mutate(
      peak_table_dropna = map(
        peak_table,\(x) drop_na(x)
      )
    ) -> file_index
  #### peak_table_dropna_relative intensity!
  file_index %>% 
    mutate(
      peak_table_dropna_wo_modloss = map(peak_table_dropna,\(x) dplyr::filter(x,!str_detect(matches,"NH3|Ox|H2O")))
    ) %>% 
    mutate(
      peak_table_dropna_wo_modloss = map(peak_table_dropna_wo_modloss, \(x) mutate(x,i_relative=i/max(i)))
    ) -> file_index
```

##PSM annotations into fragment intensity table 
output object: file_index3, file_index4
```{r}
file_index %>% 
  mutate(
    peak_table_alpha_ms2= map(peak_table_dropna_wo_modloss,\(x) mutate(x, series = str_extract(matches,"b|y")))
  ) %>% 
  mutate(
    peak_table_alpha_ms2= map(
      peak_table_alpha_ms2,
      \(x) mutate(x, ion_num = as.integer(str_extract(matches,"(?<=\\()[0-9]+(?=\\))")))
    )
  ) %>%
  mutate(
    peak_table_alpha_ms2= map(
      peak_table_alpha_ms2,
      \(x) mutate(x, charge = as.integer(str_extract(matches,"(?<=\\()[0-9]+(?=\\+\\))")))
    )
  ) %>% 
  mutate(
    peak_table_alpha_ms2 = map(
      peak_table_alpha_ms2,
      \(x) dplyr::filter(x, charge<=2)
    )
  ) %>% 
  mutate(
    peak_table_alpha_ms2 = map(peak_table_alpha_ms2, \(x) mutate(x,i_relative=i/max(i)))
  ) %>% 
  mutate(
    strip_seq=str_to_upper(str_extract(Sequence,"(?<=\\.)[:alpha:]+(?=\\.)"))
  ) %>% 
  mutate(
    seq_len = str_length(strip_seq)
  ) %>% 
  mutate(
    peak_table_alpha_ms2 = map2(
      peak_table_alpha_ms2,
      seq_len,
      \(x,y) mutate(x,seq_len = y)
    )
  ) %>% 
  mutate(
    peak_table_alpha_ms2 = map(
      peak_table_alpha_ms2,
      \(x) mutate(x,ion_num2 = if_else(series == "y",seq_len - ion_num,ion_num))
    )
  )%>%
  mutate(
    peak_table_alpha_ms2 = map(
      peak_table_alpha_ms2,
      \(x) mutate(x,alpha_col = str_c(series,"_","z",charge))
    )
  ) %>% 
  mutate(
    fragment_inten_df = map(
      peak_table_alpha_ms2,
      \(x) pivot_wider(x,id_cols = ion_num2,names_from = alpha_col,values_from = i_relative)
    )
  ) %>% 
  mutate(
    fragment_inten_df2 = map(seq_len,\(x) tibble(ion_num2=seq(1,x-1)))
  ) %>% 
  mutate(
    fragment_inten_df3 = map2(
      fragment_inten_df,
      fragment_inten_df2,
      \(x,y) full_join(x,y,by=c("ion_num2"="ion_num2"))
    )
  )-> file_index3

colnames(file_index3)
colnames(file_index3)[16] <-"scan_num"
colnames(file_index3)
file_index3 %>% 
  mutate(
    scan_num = as.integer(scan_num)
  ) %>% 
  mutate(
    charge = as.integer(Charge)
  ) %>% 
  mutate(
    XCorr = as.numeric(XCorr)
  ) %>% 
  mutate(
    `Percolator SVMScore` = as.numeric(`Percolator SVMScore`)
  ) ->file_index3

file_index3 %>% 
  mutate(
    Modifications = str_replace_all(Modifications,"[:blank:]","")
  ) -> file_index3

file_index3 %>% 
  distinct(
    strip_seq,scan_num,charge,XCorr,
    .keep_all = TRUE
  ) -> file_index3

file_index3 %>% 
  unnest(fragment_inten_df3) %>% 
  dplyr::rename(percol_svm = `Percolator SVMScore`) %>% 
  select(strip_seq,Modifications,scan_num,XCorr,percol_svm,charge,ion_num2,b_z1,b_z2,y_z1,y_z2) %>%
  mutate(
    across(
      .cols = c(b_z1,b_z2,y_z1,y_z2),
      .fns = \(x) if_else(is.na(x),0,x)
    )
  ) -> file_index4
##now strip_seq + scan_num + XCorr + charge
```

##Training data export for AlphaPeptDeep inputs
output object: summaryfile_psm_for_training2, summaryfile_psm_for_training3, summaryfile_psm_for_training4, 
output files: precursor_df.tsv, frag_intensity_df.tsv
```{r}
# summaryfile_psm_for_training %>% 
  #   select(Sequence,nAA) %>% print(n=Inf)
  summaryfile_psm_for_training %>% 
    select(-c(nestedcol)) %>% 
    mutate(
      scan_num = as.integer(`First Scan`)
    ) %>% distinct(
      Sequence,scan_num,charge,XCorr,
      .keep_all = TRUE
    ) %>% 
    inner_join(
      file_index4,
      by=join_by(
        Sequence == strip_seq,
        scan_num==scan_num,
        charge==charge,
        XCorr==XCorr
      )
    ) ->summaryfile_psm_for_training2
  # summaryfile_psm_for_training2 %>% 
  #   select(Sequence,nAA) %>% dplyr::filter(nAA==7) %>% print(n=Inf)
  summaryfile_psm_for_training2 %>% 
    arrange(
      index,ion_num2
    ) %>% 
    mutate(
      frag_index = seq(0,nrow(summaryfile_psm_for_training2)-1)
    ) %>%
    nest(frag_df= c(frag_index,ion_num2,b_z1,b_z2,y_z1,y_z2)) -> summaryfile_psm_for_training3 
  
  
  # ###summaryfile_psm_for_training3 is the final table ##dont change it!
  summaryfile_psm_for_training3 %>% 
    mutate(
      index= seq(1,nrow(summaryfile_psm_for_training3))
    ) %>% 
    mutate(
      frag_start_idx = map_dbl(frag_df,\(x) min(x$frag_index))
    ) %>% 
    mutate(
      frag_stop_idx = map_dbl(frag_df,\(x) max(x$frag_index)+1)
    ) %>% 
    dplyr::rename(
      spec_idx = index,
      irt = `RT in min` 
    ) %>% 
    select(
      Sequence,charge,spec_idx,irt,mods,mod_sites,nAA,frag_start_idx,frag_stop_idx,nce,instrument
    ) %>% 
    dplyr::rename(
      sequence = Sequence
    ) -> summaryfile_psm_for_training4
  summaryfile_psm_for_training4 %>% 
    write_tsv(
      "C:/Users/admin/alphapeptdeep/project/folder/alphapeptdeep/precursor_df.tsv"
    )
  ### create frag_intensity_df
  summaryfile_psm_for_training3 %>% 
    select(frag_df) %>% 
    unnest(frag_df) %>% 
    select(
      b_z1,b_z2,y_z1,y_z2
    ) %>% 
    write_tsv(
      "C:/Users/admin/alphapeptdeep/project/folder/alphapeptdeep/frag_intensity_df.tsv"
    )
```

# Training set
## Retry: New training set data using full enzymatic search
output object: psm_563516, psm_311547_trypsin, psm_251969_chymo
```{r}
readRDS("./export/psm_563516.rds") -> psm_563516

psm_563516 %>% 
  filter(
    enzyme == "trypsin"
  ) -> psm_311547_trypsin

psm_563516 %>% 
  filter(
    enzyme == "chymotrypsin"
  ) -> psm_251969_chymo
```

## Training set for trypsin
output file: precursor_df_311547.tsv, precursor_df_311547_fragdf.tsv
```{r}
psm_311547_trypsin %>% 
  unnest(fragment_inten_df3) %>% 
  arrange(
    index,ion_num2
  ) %>% 
  mutate(
    frag_index = seq(0,nrow(.)-1)
  ) %>% 
  nest(frag_df= c(frag_index,ion_num2,b_z1,b_z2,y_z1,y_z2)) %>% 
  mutate(
    frag_start_idx = map_dbl(frag_df,\(x) min(x$frag_index))
  ) %>% 
  mutate(
    frag_stop_idx = map_dbl(frag_df,\(x) max(x$frag_index)+1)
  ) %>% 
  dplyr::rename(
    spec_idx = index,
    irt = `RT in min`,
    sequence = strip_seq
  ) -> psm_311547_trypsin

psm_311547_trypsin %>% 
  select(
    sequence,charge,spec_idx,mods,mod_sites,nAA,frag_start_idx,frag_stop_idx,nce,instrument
  ) %>% 
  write_tsv(
    "C:/Users/admin/alphapeptdeep/project/folder/alphapeptdeep/precursor_df_311547.tsv"
  )
psm_311547_trypsin %>% 
  select(frag_df) %>% 
  unnest(frag_df) %>% 
  select(
    b_z1,b_z2,y_z1,y_z2
  ) %>% 
  mutate(
    across(everything(),\(x) replace_na(x,0))
  ) %>% 
  write_tsv(
    "C:/Users/admin/alphapeptdeep/project/folder/alphapeptdeep/precursor_df_311547_fragdf.tsv"
  )
```

## Training set for chymotrypsin
output file: psm_251969_chymo.tsv, psm_251969_chymo_fragdf.tsv
```{r}
psm_251969_chymo %>% 
  unnest(fragment_inten_df3) %>% 
  arrange(
    index,ion_num2
  ) %>% 
  mutate(
    frag_index = seq(0,nrow(.)-1)
  ) %>% 
  nest(frag_df= c(frag_index,ion_num2,b_z1,b_z2,y_z1,y_z2)) %>% 
  mutate(
    frag_start_idx = map_dbl(frag_df,\(x) min(x$frag_index))
  ) %>% 
  mutate(
    frag_stop_idx = map_dbl(frag_df,\(x) max(x$frag_index)+1)
  ) %>% 
  dplyr::rename(
    spec_idx = index,
    irt = `RT in min`,
    sequence = strip_seq
  ) -> psm_251969_chymo

psm_251969_chymo %>% 
  select(
    sequence,charge,spec_idx,mods,mod_sites,nAA,frag_start_idx,frag_stop_idx,nce,instrument
  ) %>% 
  write_tsv(
    "C:/Users/admin/alphapeptdeep/project/folder/alphapeptdeep/psm_251969_chymo.tsv"
  )
psm_251969_chymo %>% 
  select(frag_df) %>% 
  unnest(frag_df) %>% 
  select(
    b_z1,b_z2,y_z1,y_z2
  ) %>% 
  mutate(
    across(everything(),\(x) replace_na(x,0))
  ) %>% 
  write_tsv(
    "C:/Users/admin/alphapeptdeep/project/folder/alphapeptdeep/psm_251969_chymo_fragdf.tsv"
  )
```


#Test set for prediciton
## Making up Nt-arg Data to predict 
output object: summaryfile_psm_for_testing
output files: input_testing.tsv
```{r}
summaryfile_psm %>% 
    dplyr::filter(
      arginylation == TRUE
    ) -> summaryfile_psm_for_testing
  
  
  summaryfile_psm_for_testing %>%   
    mutate(index=1:nrow(.)) %>% 
    separate_longer_delim(Modifications, delim="; ") %>% 
    mutate(
      mods_aa = case_when(
        str_detect(Modifications,"^N\\-Term")~"Any N-term",
        str_detect(Modifications,"^[A-Z]")~str_extract(Modifications,"^[A-Z]"),
        .default = Modifications
      )
    ) %>% 
    mutate(
      mods_name = case_when(
        str_detect(Modifications,"Acetyl\\)")~"Acetyl",
        str_detect(Modifications,"Acetyl\\:2H\\(3\\)")~"Acetyl:2H(3)",
        str_detect(Modifications,"Oxidation")~"Oxidation",
        str_detect(Modifications,"Carbamidomethyl")~"Carbamidomethyl",
        .default = Modifications
      )
    ) %>% 
    mutate(
      mod_sites = case_when(
        str_detect(Modifications,"^N\\-Term")~"0",
        str_detect(Modifications,"^[A-Z]")~str_extract(Modifications,"(?<=^[A-Z])[0-9]+"),
        .default = Modifications
      )
    ) %>% 
    nest(nestedcol = c(Modifications,mods_name,mods_aa,mod_sites)) %>% 
    mutate(
      Modifications = map_chr(nestedcol,\(x) x$Modifications %>% paste(collapse = ";"))
    ) %>% 
    mutate(
      mods = map_chr(nestedcol,\(x) unite(data = x, col = mods, c(mods_name,mods_aa),sep ="@") %>% .$mods %>% paste(collapse = ";"))
    ) %>% 
    mutate(
      mod_sites = map_chr(nestedcol,\(x) x$mod_sites %>% paste(collapse = ";"))
    )%>% 
    mutate(
      nAA = str_length(Sequence),
      nce = as.integer(27),
      instrument = "QE",
      charge = as.integer(Charge)
    )-> summaryfile_psm_for_testing
  summaryfile_psm_for_testing %>% 
    separate_rows(mod_sites,sep=";") %>% 
    mutate(
      mod_sites = as.integer(mod_sites)
    ) %>%
    mutate(
      mod_sites = case_when(
        mod_sites > 0 ~ mod_sites+1,
        .default = mod_sites
      )
    ) %>%
    mutate(
      nAA = nAA+1
    ) %>%
    nest(
      mod_sites=mod_sites
    ) %>% 
    mutate(
      mod_sites = map_chr(mod_sites,\(x) x$mod_sites %>%  paste(collapse = ";"))
    ) %>% 
    mutate(
      sequence = case_when(
        str_detect(Sequence,"^N") ~ str_replace(Sequence,"^N","RD"),
        str_detect(Sequence,"^Q") ~ str_replace(Sequence,"^Q","RE"),
        str_detect(Sequence,"^E") ~ str_replace(Sequence,"^E","RE"),
        str_detect(Sequence,"^D") ~ str_replace(Sequence,"^D","RD")
      )
    ) %>% 
    mutate(
      irt = `RT in min`
    ) %>% 
    mutate(
      mods = case_when(
        str_detect(mods, "N\\-Term\\(ArgAcetylD3NQ\\)") ~ str_replace(mods,"N\\-Term\\(ArgAcetylD3NQ\\)","Acetyl:2H(3)"),
        str_detect(mods, "N\\-Term\\(ArgAcetylD3\\)") ~ str_replace(mods,"N\\-Term\\(ArgAcetylD3\\)","Acetyl:2H(3)")
      )
    ) -> summaryfile_psm_for_testing
  summaryfile_psm_for_testing %>% 
    dplyr::select(
      sequence,charge,index,mods,mod_sites,nAA,irt
    ) %>% 
    write_tsv(
      "C:/Users/admin/alphapeptdeep/project/folder/alphapeptdeep/input_testing.tsv"
    ) ###this is the testing data
```

## PSM annotation integration and strings handling + MET
output object: file_index_arg, file_index_arg2, file_index_arg3, file_index_arg4, file_index_arg5, file_index_arg6_ttest
```{r}
folder_pdspectra_arg <- "./annotation_psm/200821_HELA_MGTG_iNrich_bRP_F_arg/"
  ##read xml
  xml2::read_html(
    paste0(folder_pdspectra_arg,"index.html")
  ) -> file_index_arg
  #from xml object read table
  rvest::html_table(
    file_index_arg,
    header = TRUE
  ) ->file_index_arg
  
  ##table trimming
  file_index_arg[[1]] -> file_index_arg #unlist
  file_index_arg[seq(1,nrow(file_index_arg),by=2),seq(2,ncol(file_index_arg),by=2)] -> file_index_arg ## delete unnessary cols and rows
  colnames(file_index_arg)<- as.vector(file_index_arg[1,]) %>% unlist ## colnames
  file_index_arg[c(-1),] -> file_index_arg
  
  #peak list handling
  readLines(paste0(folder_pdspectra_arg,"index.html"))-> file_index_lines_arg
  
  ##add column of peak list
  file_index_arg %>% 
    bind_cols(
      tibble(peak_file = str_extract(file_index_lines_arg[str_detect(file_index_lines_arg,"Peak List")],"data\\/.+\\.txt"))
    ) %>% 
    mutate(
      peak_table = map(
        peak_file,\(x) read_tsv(paste0(folder_pdspectra_arg,x),show_col_types = FALSE), .progress = TRUE
      )
    )-> file_index_arg
  
  ###diagnostic ion b (0) (1+)
  # file_index_arg2 %>% 
  #   mutate(
  #     peak_table = map(
  #       peak_table, \(x) mutate(x,matches = if_else(`m/z` < 202.138331+0.005 & `m/z` > 202.138331-0.005, "b (0) (1+)", matches))
  #     )
  #   ) -> file_index_arg3
  
  file_index_arg %>% 
    mutate(
      diagnostic_ion_mz = map(peak_table, \(x) x$`m/z`[str_which(x$matches, "b[:blank:]\\(0")] )
    ) %>% 
    mutate(
      diagnostic_ion_mz = map_dbl(diagnostic_ion_mz,\(x) ifelse(length(x)>0,x,NA))
    ) %>%  
    mutate(
      peak_table_dropna = map(
        peak_table,\(x) drop_na(x)
      )
    ) %>%
    mutate(
      peak_table_dropna_wo_modloss = map(peak_table_dropna,\(x) dplyr::filter(x,!str_detect(matches,"NH3|Ox|H2O")))
    ) %>% 
    mutate(
      peak_table_dropna_wo_modloss = map(peak_table_dropna_wo_modloss, \(x) mutate(x,i_relative=i/max(i)))
    ) %>% 
    mutate(
      peak_table_alpha_ms2= map(peak_table_dropna_wo_modloss,\(x) mutate(x, series = str_extract(matches,"b|y")))
    ) %>% 
    mutate(
      peak_table_alpha_ms2= map(
        peak_table_alpha_ms2,
        \(x) mutate(x, ion_num = as.integer(str_extract(matches,"(?<=\\()[0-9]+(?=\\))")))
      )
    ) %>% ###b ion +1 because of modification! 
    mutate(
      peak_table_alpha_ms2= map(
        peak_table_alpha_ms2,
        \(x) mutate(x, ion_num = if_else(series == "b",ion_num +1,ion_num))
      )
    ) %>% 
    mutate(
      peak_table_alpha_ms2= map(
        peak_table_alpha_ms2,
        \(x) mutate(x, charge = as.integer(str_extract(matches,"(?<=\\()[0-9]+(?=\\+\\))")))
      )
    ) %>% 
    mutate(
      peak_table_alpha_ms2 = map(
        peak_table_alpha_ms2,
        \(x) dplyr::filter(x, charge<=2)
      )
    ) %>% 
    mutate(
      peak_table_alpha_ms2 = map(peak_table_alpha_ms2, \(x) mutate(x,i_relative=i/max(i)))
    ) %>% 
    mutate(
      strip_seq=str_to_upper(str_extract(Sequence,"(?<=\\.)[:alpha:]+(?=\\.)"))
    ) %>% ##strip seq add r
    mutate(
      strip_seq = paste0("R",strip_seq)
    ) %>% 
    mutate(
      seq_len = str_length(strip_seq) ###modification of R! +1!
    ) %>% 
    mutate(
      peak_table_alpha_ms2 = map2(
        peak_table_alpha_ms2,
        seq_len,
        \(x,y) mutate(x,seq_len = y)
      )
    ) %>% 
    mutate(
      peak_table_alpha_ms2 = map(
        peak_table_alpha_ms2,
        \(x) mutate(x,ion_num2 = if_else(series == "y",seq_len - ion_num,ion_num))
      )
    )%>%
    mutate(
      peak_table_alpha_ms2 = map(
        peak_table_alpha_ms2,
        \(x) mutate(x,alpha_col = str_c(series,"_","z",charge))
      )
    ) %>% 
    mutate(
      fragment_inten_df = map(
        peak_table_alpha_ms2,
        \(x) pivot_wider(x,id_cols = ion_num2,names_from = alpha_col,values_from = i_relative)
      )
    ) %>% 
    mutate(
      fragment_inten_df2 = map(seq_len,\(x) tibble(ion_num2=seq(1,x-1)))
    ) %>% 
    mutate(
      fragment_inten_df3 = map2(
        fragment_inten_df,
        fragment_inten_df2,
        \(x,y) full_join(x,y,by=c("ion_num2"="ion_num2"))
      )
    )-> file_index_arg2
  
  
  colnames(file_index_arg2)[16] <-"scan_num"
  
  file_index_arg2 %>% 
    mutate(
      scan_num = as.integer(scan_num)
    ) %>% 
    mutate(
      charge = as.integer(Charge)
    ) %>% 
    mutate(
      XCorr = as.numeric(XCorr)
    ) %>% 
    mutate(
      `Percolator SVMScore` = as.numeric(`Percolator SVMScore`)
    ) %>% 
    mutate(
      Modifications = str_replace_all(Modifications,"[:blank:]","")
    ) -> file_index_arg2
  
  # file_index_arg2 %>% 
  #   distinct(
  #     strip_seq,scan_num,charge,XCorr,
  #     .keep_all = TRUE
  #   ) -> file_index_arg3
  # 
  # file_index_arg3 %>% 
  #   mutate(
  #     diagnostic_ion_int_relative = map(peak_table_alpha_ms2, \(x) x$i_relative[str_which(x$matches, "b[:blank:]\\(0")] )
  #   ) %>% 
  #   mutate(
  #     diagnostic_ion_int_relative = map_dbl(diagnostic_ion_int_relative,\(x) ifelse(length(x)>0,x,NA))
  #   ) -> file_index_arg3
  # 
  #FragmentPeptide()
  ### bion yion ttest
  {
    MonoisotopicMass(
      formula = list(C=8, H=11, N=4, O=2, S=0, x= 3),
      isotopes = list(x = 2.01410177812) ##deuterium
    ) -> mass_ntd3arg
    
    MonoisotopicMass(
      formula = list(C=8, H=11, N=2, O=2, S=0, x= 3),
      isotopes = list(x = 2.01410177812) ##deuterium
    ) -> mass_d3k
    
    MonoisotopicMass(
      formula = list(C=5, H=9, N=1, O=2, S=1)
    ) -> mass_met_ox
    
    file_index_arg2 %>% 
      mutate(
        sequence_for_fragspec = str_extract(Sequence,"(?<=\\.).+(?=\\.)")
      ) %>%
      mutate(
        sequence_for_fragspec = str_replace(sequence_for_fragspec,"^n","D"),
        sequence_for_fragspec = str_replace(sequence_for_fragspec,"^q","E"),
        sequence_for_fragspec = str_replace(sequence_for_fragspec,"^d","D"),
        sequence_for_fragspec = str_replace(sequence_for_fragspec,"^e","E"),
        sequence_for_fragspec = str_replace_all(sequence_for_fragspec,"c","C"),
      ) %>%
      mutate(
        sequence_for_fragspec = paste0("r",sequence_for_fragspec)
      ) %>% 
      mutate(
        frag_theo_spec = map(
          sequence_for_fragspec,
          \(x) OrgMassSpecR::FragmentPeptide(
            x,
            fragments = "by",
            IAA = TRUE,
            custom = list(
              code = c("r","k","m"),
              mass = c(mass_ntd3arg,mass_d3k,mass_met_ox)
            )
          )
        )
      ) -> file_index_arg3
  }
  
  file_index_arg3 %>% 
    mutate(
      frag_theo_spec = map(
        frag_theo_spec,
        \(x) mutate(
          x,
          series = str_extract(ms2type,"[by]"),
          ion_num = as.integer(str_extract(ms2type,"(?<=[by])[0-9]+")),
          charge = as.integer(str_extract(ms2type,"[0-9](?=\\+)"))
        )
      )
    ) -> file_index_arg4
  
  file_index_arg4 %>% 
    mutate(
      peak_table_alpha_ms2_vs_theo_spec = map2(
        peak_table_alpha_ms2,
        frag_theo_spec,
        \(x,y) left_join(x,y, join_by(series == series, ion_num == ion_num, charge == charge))
      )
    ) -> file_index_arg4
  
  file_index_arg4 %>% 
    mutate(
      peak_table_alpha_ms2_vs_theo_spec = map(
        peak_table_alpha_ms2_vs_theo_spec,
        \(x) mutate(x,
                    error = `m/z`-ms2mz
        )
      )
    ) -> file_index_arg4
  
  file_index_arg4 %>% 
    mutate(
      b_ion_count = map_int(
        peak_table_alpha_ms2_vs_theo_spec,
        \(x) filter(x, series == "b") %>% nrow()
      ),
      y_ion_count = map_int(
        peak_table_alpha_ms2_vs_theo_spec,
        \(x) filter(x, series == "y") %>% nrow()
      ),
      b_ion_errors = map(
        peak_table_alpha_ms2_vs_theo_spec,
        \(x) filter(x, series == "b") %>% pull(error)
      ),
      y_ion_errors = map(
        peak_table_alpha_ms2_vs_theo_spec,
        \(x) filter(x, series == "y") %>% pull(error)
      )
    )-> file_index_arg4
  
  file_index_arg4 %>%
    mutate(
      peak_table_alpha_ms2_vs_theo_spec = map(
        peak_table_alpha_ms2_vs_theo_spec,
        \(x) mutate(x,
                    error_ppm = (`m/z`-ms2mz)/`m/z`*1e6
        )
      )
    ) -> file_index_arg4
  
  file_index_arg4 %>% 
    mutate(
      b_ion_errors_ppm = map(
        peak_table_alpha_ms2_vs_theo_spec,
        \(x) filter(x, series == "b") %>% pull(error_ppm)
      ),
      y_ion_errors_ppm = map(
        peak_table_alpha_ms2_vs_theo_spec,
        \(x) filter(x, series == "y") %>% pull(error_ppm)
      ),
      b_ion_mz = map(
        peak_table_alpha_ms2_vs_theo_spec,
        \(x) filter(x, series == "b") %>% pull(`m/z`)
      ),
      y_ion_mz = map(
        peak_table_alpha_ms2_vs_theo_spec,
        \(x) filter(x, series == "y") %>% pull(`m/z`)
      )
    ) -> file_index_arg4
  
  
  file_index_arg4 %>% 
    mutate(
      b_y_ttest = map2_dbl(
        b_ion_errors,
        y_ion_errors,
        \(x,y) if(length(x)>1 & length(y)>1){t.test(unlist(x),unlist(y),var.equal = TRUE)$p.value} else{return(NA)}
      ),
      b_y_ttest_ppm = map2_dbl(
        b_ion_errors_ppm,
        y_ion_errors_ppm,
        \(x,y) if(length(x)>1 & length(y)>1){t.test(unlist(x),unlist(y),var.equal = TRUE)$p.value} else{return(NA)}
      ),
      b_y_ttest_mz = map2_dbl(
        b_ion_mz,
        y_ion_mz,
        \(x,y) if(length(x)>1 & length(y)>1){t.test(unlist(x),unlist(y),var.equal = TRUE)$p.value} else{return(NA)}
      ),
      b_y_ttest_mean_diff = map2_dbl(
        b_ion_mz,
        y_ion_mz,
        \(x,y) if(length(x)>1 & length(y)>1){t.test(unlist(x),unlist(y),var.equal = TRUE) %>% tidy %>% .$estimate} else{return(NA)}
      )
    ) -> file_index_arg5
  
  t.test(c(2,2,2),c(4,4,5))$estimate["mean of x"]
  
  diff(4,5)
  
  file_index_arg5 %>% 
    select(
      b_y_ttest_mean_diff,
      b_y_ttest,
      b_y_ttest_ppm
    ) %>% 
    mutate(
      b_y_ttest_sig = if_else(b_y_ttest<0.05,"smert failed","smert succeed"),
      b_y_ttest_ppm_sig = if_else(b_y_ttest_ppm<0.05,1,0)
    ) %>% 
    drop_na() %>% 
    ggplot(
      aes(x=b_y_ttest_mean_diff,fill=b_y_ttest_sig)
    )+
    geom_density(
      alpha = 0.1
    )-> test1
  
  file_index_arg5 %>% 
    select(
      b_y_ttest_mean_diff,
      b_y_ttest,
      b_y_ttest_ppm
    ) %>% 
    mutate(
      b_y_ttest_sig = if_else(b_y_ttest<0.05,"smert failed","smert succeed"),
      b_y_ttest_ppm_sig = if_else(b_y_ttest_ppm<0.05,"smert failed","smert succeed")
    ) %>% 
    drop_na() %>% 
    ggplot(
      aes(x=b_y_ttest_mean_diff,fill=b_y_ttest_ppm_sig)
    )+
    # geom_histogram(
    #   binwidth = 20,
    #   position = "dodge"
    # )+
    geom_density(
      alpha = 0.1
    ) -> test2
  
  ggarrange(test1,test2, ncol = 1)  
  # lims(y=c(0,70))
  
  file_index_arg5 %>% 
    mutate(
      b_y_ttest_sig = if_else(b_y_ttest<0.05,1,0),
      b_y_ttest_ppm_sig = if_else(b_y_ttest_ppm<0.05,1,0),
      b_y_ttest_mz = if_else(b_y_ttest_mz<0.05,1,0)
    ) %>% 
    summarize(
      .by = c(b_y_ttest_ppm_sig,b_y_ttest_mz),
      count = n()
    ) %>% 
    drop_na()
    
  
  file_index_arg5 %>% 
    mutate(
      b_y_ttest_sig = if_else(b_y_ttest<0.05,"blue",NA),
      b_y_ttest_ppm_sig = if_else(b_y_ttest_ppm<0.05,"red",NA)
    ) %>% 
    summarize(
      .by = c(b_y_ttest_sig,b_y_ttest_ppm_sig),
      count = n()
    ) %>% 
    write_tsv(
      "b_y_ttest.tsv"
    )
  file_index_arg5 %>% 
    mutate(
      b_y_ttest_sig = if_else(b_y_ttest<0.05,"blue",NA),
      b_y_ttest_ppm_sig = if_else(b_y_ttest_ppm<0.05,"red",NA)
    ) %>% 
    ggplot(
      aes(x= b_y_ttest, y= b_y_ttest_ppm)
    )+
    geom_point(
      aes(color = b_y_ttest_sig, fill = b_y_ttest_ppm_sig),
      shape=21,
      size = 1,
      stroke = 1
    )+
    scale_fill_manual(values=c("blue", "black")) + 
    scale_color_manual(values=c("red", "black"))+
    theme_bw()
  ggsave(
    paste0("./export/smert_ppm_mda.png"),
    width = 15, height = 12, dpi=600, units = "cm")
  
  file_index_arg5 %>% 
    mutate(
      data = map(
        peak_table_alpha_ms2_vs_theo_spec,
        \(x) x %>% select(`m/z`,error,error_ppm,series)         
      )
    ) %>% 
    select(data) %>% 
    unnest(data) %>% 
    pivot_longer(
      c(error,error_ppm)
    ) %>% 
    ggplot(
      aes(x=`m/z`,y=value)
    )+
    geom_point(
      alpha = 0.5
    )+
    facet_wrap(
      facets = vars(name,series),
      scales = "free"
    )+
    theme_bw()
  
  
  file_index_arg5 %>%   
    mutate(index=1:nrow(.)) %>% 
    separate_longer_delim(Modifications, delim=";") %>% 
    mutate(
      mods_aa = case_when(
        str_detect(Modifications,"^N\\-Term")~"Any N-term",
        str_detect(Modifications,"^[A-Z]")~str_extract(Modifications,"^[A-Z]"),
        .default = Modifications
      )
    ) %>% 
    mutate(
      mods_name = case_when(
        str_detect(Modifications,"Acetyl\\)")~"Acetyl",
        str_detect(Modifications,"Acetyl\\:2H\\(3\\)")~"Acetyl:2H(3)",
        str_detect(Modifications,"Oxidation")~"Oxidation",
        str_detect(Modifications,"Carbamidomethyl")~"Carbamidomethyl",
        .default = Modifications
      )
    ) %>% 
    mutate(
      mod_sites = case_when(
        str_detect(Modifications,"^N\\-Term")~"0",
        str_detect(Modifications,"^[A-Z]")~as.character(as.integer(str_extract(Modifications,"(?<=^[A-Z])[0-9]+"))+1),
        .default = Modifications
      )
    ) %>% 
    nest(nestedcol = c(Modifications,mods_name,mods_aa,mod_sites)) %>% 
    mutate(
      Modifications = map_chr(nestedcol,\(x) x$Modifications %>% paste(collapse = ";"))
    ) %>% 
    mutate(
      mods = map_chr(nestedcol,\(x) unite(data = x, col = mods, c(mods_name,mods_aa),sep ="@") %>% .$mods %>% paste(collapse = ";"))
    ) %>% 
    mutate(
      mod_sites = map_chr(nestedcol,\(x) x$mod_sites %>% paste(collapse = ";"))
    )%>% 
    mutate(
      mods = case_when(
        str_detect(mods, "N\\-Term\\(ArgAcetylD3NQ\\)") ~ str_replace(mods,"N\\-Term\\(ArgAcetylD3NQ\\)","Acetyl:2H(3)"),
        str_detect(mods, "N\\-Term\\(ArgAcetylD3\\)") ~ str_replace(mods,"N\\-Term\\(ArgAcetylD3\\)","Acetyl:2H(3)")
      )
    ) %>% 
    mutate(
      sequence = str_to_upper(sequence_for_fragspec),
      nAA = seq_len,
      nce = as.integer(27),
      instrument = "QE",
      charge = as.integer(Charge)
    )-> file_index_arg6_ttest
  
  ## need to write down more for exporting tsv from file_index_arg6

```

## Test set splitting: for trypsin
output file: precursor_df_arg_1202_trypsin.tsv, precursor_df_arg_1202_trypsin_fragdf.tsv
```{r}
summaryfile_psm_for_testing3 %>%
  select(-enzyme.y) %>% 
  rename(enzyme = enzyme.x) -> summaryfile_psm_for_testing3
  
summaryfile_psm_for_testing3 %>% 
  filter(enzyme == "trypsin") %>%
  unnest(frag_df) %>% 
  arrange(
    index,ion_num2
  ) %>% 
  mutate(
    frag_index = seq(0,nrow(.)-1)
  ) %>% 
  nest(frag_df= c(frag_index,ion_num2,b_z1,b_z2,y_z1,y_z2)) %>% 
  mutate(
    frag_start_idx = map_dbl(frag_df,\(x) min(x$frag_index))
  ) %>% 
  mutate(
    frag_stop_idx = map_dbl(frag_df,\(x) max(x$frag_index)+1)
  ) %>% 
  dplyr::rename(
    spec_idx = index
  ) %>% 
  select(
    sequence,charge,spec_idx,mods,mod_sites,nAA,frag_start_idx,frag_stop_idx,nce,instrument
  ) %>% 
  write_tsv(
    "C:/Users/admin/alphapeptdeep/project/folder/alphapeptdeep/precursor_df_arg_1202_trypsin.tsv"
  )

summaryfile_psm_for_testing3 %>% 
  filter(enzyme == "trypsin") %>%
  unnest(frag_df) %>% 
  arrange(
    index,ion_num2
  ) %>% 
  mutate(
    frag_index = seq(0,nrow(.)-1)
  ) %>% 
  nest(frag_df= c(frag_index,ion_num2,b_z1,b_z2,y_z1,y_z2)) %>% 
  select(frag_df) %>% 
  unnest(frag_df) %>% 
  select(
    b_z1,b_z2,y_z1,y_z2
  ) %>% 
  mutate(
    across(everything(),\(x) replace_na(x,0))
  ) %>% 
  write_tsv(
    "C:/Users/admin/alphapeptdeep/project/folder/alphapeptdeep/precursor_df_arg_1202_trypsin_fragdf.tsv"
  )
```

## Test set splitting: for chymotrypsin
output file: precursor_df_arg_15_chymotrypsin.tsv, precursor_df_arg_15_chymotrypsin_fragdf.tsv
```{r}

summaryfile_psm_for_testing3 %>% 
  filter(enzyme == "chymotrypsin") %>%
  unnest(frag_df) %>% 
  arrange(
    index,ion_num2
  ) %>% 
  mutate(
    frag_index = seq(0,nrow(.)-1)
  ) %>% 
  nest(frag_df= c(frag_index,ion_num2,b_z1,b_z2,y_z1,y_z2)) %>% 
  mutate(
    frag_start_idx = map_dbl(frag_df,\(x) min(x$frag_index))
  ) %>% 
  mutate(
    frag_stop_idx = map_dbl(frag_df,\(x) max(x$frag_index)+1)
  ) %>% 
  dplyr::rename(
    spec_idx = index
  ) %>% 
  select(
    sequence,charge,spec_idx,mods,mod_sites,nAA,frag_start_idx,frag_stop_idx,nce,instrument
  ) %>% 
  write_tsv(
    "C:/Users/admin/alphapeptdeep/project/folder/alphapeptdeep/precursor_df_arg_15_chymotrypsin.tsv"
  )

summaryfile_psm_for_testing3 %>% 
  filter(enzyme == "chymotrypsin") %>%
  unnest(frag_df) %>% 
  arrange(
    index,ion_num2
  ) %>% 
  mutate(
    frag_index = seq(0,nrow(.)-1)
  ) %>% 
  nest(frag_df= c(frag_index,ion_num2,b_z1,b_z2,y_z1,y_z2)) %>% 
  select(frag_df) %>% 
  unnest(frag_df) %>% 
  select(
    b_z1,b_z2,y_z1,y_z2
  ) %>% 
  mutate(
    across(everything(),\(x) replace_na(x,0))
  ) %>% 
  write_tsv(
    "C:/Users/admin/alphapeptdeep/project/folder/alphapeptdeep/precursor_df_arg_15_chymotrypsin_fragdf.tsv"
  )
```

#MS2 Prediction
##AlphaPeptDeep(APD) MS2 Output handling:: Reading apd scoring output (for Figure 2A )
output object: output_prediction_ms2_build, output_prediction_ms2_transfer, output_prediction_ms2_pretrained, output_prediction_ms2_arg (w/o arg), summaryfile_psm_for_training_pcc, summaryfile_psm_for_testing3_pcc
```{r}
{
  folder_alphapeptdeep = "C:/Users/admin/alphapeptdeep/project/folder/alphapeptdeep/"
  
  
  
  output_prediction_ms2_build <- read_tsv(
    paste0(folder_alphapeptdeep,"output_metrics_describ_230610.tsv")
  )[,-1]
  
  output_prediction_ms2_transfer <- read_tsv(
    paste0(folder_alphapeptdeep,"inrich/output_metrics_describ_for_311547_trypsin_231130.tsv")
  )[,-1] %>% 
    bind_rows(
      read_tsv(
        paste0(folder_alphapeptdeep,"inrich/output_metrics_describ_for_251969_chymo_231130.tsv")
      )[,-1]
    )
  
  output_prediction_ms2_pretrained <- read_tsv(
    paste0(folder_alphapeptdeep,"output_metrics_describ4_230610.tsv")
  )[,-1]
  
  output_prediction_ms2_arg <- read_tsv(
    paste0(folder_alphapeptdeep,"inrich/output/output_metrics_describ_for_arg_trypsin_231201.tsv")
  )[,-1] %>% 
    bind_rows(
      read_tsv(
        paste0(folder_alphapeptdeep,"inrich/output/output_metrics_describ_for_arg_chymotrypsin_231201.tsv")
      )[,-1]
    )
  
  summaryfile_psm_for_training3 %>%
    left_join(
      output_prediction_ms2_transfer,
      join_by(
        index==spec_idx
      )
    ) -> summaryfile_psm_for_training_pcc
  
  summaryfile_psm_for_testing3 %>% 
    left_join(
      output_prediction_ms2_arg %>% select(-c(sequence,charge,irt,mods,mod_sites,nAA,nce,instrument,diagnostic_ion_int_relative)),
      join_by(
        index==spec_idx
      )
    ) -> summaryfile_psm_for_testing3_pcc
}
```

## Reading apd prediction spectra output and merging into PSM table
output object: fdr_pcc_arg_set, fdr_pcc_arg_set_fragdf, fdr_pcc_arg_set_preddf, summaryfile_psm_for_testing3_pcc
```{r}
#231027 fragdf, preddf, ms2_prediction result importing

read_tsv(
  paste0(folder_alphapeptdeep,"inrich/output/output_metrics_describ_for_arg_trypsin_231201.tsv")
) %>% 
  select(-...1) %>% 
  mutate(
    false_set = 1
  ) -> fdr_pcc_arg_set

fdr_pcc_arg_set %>% 
  bind_rows(
    read_tsv(
      paste0(folder_alphapeptdeep,"inrich/output/output_metrics_describ_for_arg_chymotrypsin_231201.tsv")
    ) %>% 
      select(-...1) %>% 
      mutate(
        false_set = 1
      )
  ) -> fdr_pcc_arg_set

###Original SPEC
read_tsv(
  paste0(folder_alphapeptdeep,"precursor_df_arg_1202_trypsin_fragdf.tsv")
) %>% 
  bind_rows(
    read_tsv(
      paste0(folder_alphapeptdeep,"precursor_df_arg_15_chymotrypsin_fragdf.tsv")
    )
  )-> fdr_pcc_arg_set_fragdf

read_tsv(
  paste0(folder_alphapeptdeep,"inrich/output/output_arg_ms2_prediction_for_arg_trypsin_231201.tsv")
) %>%
  bind_rows(
    read_tsv(
      paste0(folder_alphapeptdeep,"inrich/output/output_arg_ms2_prediction_for_arg_chymotrypsin_231201.tsv")
    )
  ) %>% 
  select(-c(...1,b_modloss_z1,b_modloss_z2,y_modloss_z1,y_modloss_z2)) %>% 
  rename(
    b_z1_pred = b_z1,
    b_z2_pred = b_z2,
    y_z1_pred = y_z1,
    y_z2_pred = y_z2
  ) -> fdr_pcc_arg_set_preddf

fdr_pcc_arg_set %>% 
  mutate(
    fragindex = map2(frag_start_idx,frag_stop_idx-1,\(x,y) seq(x,y,1))
  ) %>%
  unnest(fragindex) %>% 
  bind_cols(
    fdr_pcc_arg_set_fragdf,
    fdr_pcc_arg_set_preddf
  ) %>% 
  mutate(
    fragindex2=fragindex
  ) %>% 
  nest(
    fragdf = fragindex:y_z2,
    preddf = c(fragindex2,b_z1_pred:y_z2_pred)
  ) -> fdr_pcc_arg_set
fdr_pcc_arg_set %>% 
  mutate(
    fragdf2 = map(fragdf,\(x) mutate(x,across(.cols=c(b_z1:y_z2),.fns=~na_if(.,y=0)))),
    preddf2 = map(preddf,\(x) mutate(x,across(.cols=c(b_z1_pred:y_z2_pred),.fns=~na_if(.,y=0))))
  ) -> fdr_pcc_arg_set

fdr_pcc_arg_set %>% 
  mutate(
    bion_count = map_dbl(fragdf2,\(x) length(na.omit(append(pull(x,b_z1),pull(x,b_z2)))))
  ) -> fdr_pcc_arg_set

fdr_pcc_arg_set %>%
  mutate(
    bion_pcc = map2_dbl(
      fragdf,
      preddf,
      function(x,y) {
        cor(append(pull(x,b_z1),pull(x,b_z2)),append(pull(y,b_z1_pred),pull(y,b_z2_pred)),method = "pearson")
      },
      .progress = TRUE
    )
  ) %>%
  mutate(
    yion_pcc = map2_dbl(
      fragdf,
      preddf,
      function(x,y) {
        cor(append(pull(x,y_z1),pull(x,y_z2)),append(pull(y,y_z1_pred),pull(y,y_z2_pred)),method = "pearson")
      },
      .progress = TRUE
    )
  ) -> fdr_pcc_arg_set

summaryfile_psm_for_testing3 %>% 
  bind_cols(
    fdr_pcc_arg_set %>% select(spec_idx,PCC:yion_pcc)
  ) -> summaryfile_psm_for_testing3_pcc

#summaryfile_psm_for_testing3_pcc
```

## APD prediction spectra handling:: FN, FP, TP, Spec_FPR, SPEC_FNR
output object: summaryfile_psm_for_testing3_pcc
```{r}
summaryfile_psm_for_testing3_pcc %>% 
  mutate(
    fragdf3 = map2(
      fragdf2,
      preddf2,
      \(x,y) left_join(x,y,join_by(fragindex == fragindex2))
    )
  ) -> summaryfile_psm_for_testing3_pcc

summaryfile_psm_for_testing3_pcc %>% 
  mutate(
    fragdf3 = map(
      fragdf3,
      \(x) replace_na(x,list(b_z1=0,b_z2=0,y_z1=0,y_z2=0,b_z1_pred=0,b_z2_pred=0,y_z1_pred=0,y_z2_pred=0))
    )
  ) -> summaryfile_psm_for_testing3_pcc
  
  summaryfile_psm_for_testing3_pcc %>%
    mutate(
      fragdf4 = map(
        fragdf3,
        \(x) mutate(x,
                    b_z1_type = case_when(
                      b_z1 == 0 & b_z1_pred ==0 ~ NA,
                      b_z1 > 0 & b_z1_pred ==0 ~ "FN",
                      b_z1 == 0 & b_z1_pred >0 ~ "FP",
                      b_z1 > 0 & b_z1_pred >0 ~ "TP"
                    ),
                    b_z2_type = case_when(
                      b_z2 == 0 & b_z2_pred ==0 ~ NA,
                      b_z2 > 0 & b_z2_pred ==0 ~ "FN",
                      b_z2 == 0 & b_z2_pred >0 ~ "FP",
                      b_z2 > 0 & b_z2_pred >0 ~ "TP"
                    ),
                    y_z1_type = case_when(
                      y_z1 == 0 & y_z1_pred ==0 ~ NA,
                      y_z1 > 0 & y_z1_pred ==0 ~ "FN",
                      y_z1 == 0 & y_z1_pred >0 ~ "FP",
                      y_z1 > 0 & y_z1_pred >0 ~ "TP"
                    ),
                    y_z2_type = case_when(
                      y_z2 == 0 & y_z2_pred ==0 ~ NA,
                      y_z2 > 0 & y_z2_pred ==0 ~ "FN",
                      y_z2 == 0 & y_z2_pred >0 ~ "FP",
                      y_z2 > 0 & y_z2_pred >0 ~ "TP"
                    )
        ) %>% select(contains("type")) %>% 
          pivot_longer(cols = contains("type"))
      )
    )%>%
    mutate(
      FN = map_dbl(
        fragdf4,
        \(x) sum(pull(x,value) %in% c("FN"))
      )
    ) %>%
    mutate(
      TP = map_dbl(
        fragdf4,
        \(x) sum(pull(x,value) %in% c("TP"))
      )
    ) %>%
    mutate(
      FP = map_dbl(
        fragdf4,
        \(x) sum(pull(x,value) %in% c("FP"))
      )
    ) %>% 
    mutate(
      spec_FDR = FP/(TP+FP),
      spec_FNR = FN/(FN+TP)
    ) -> summaryfile_psm_for_testing3_pcc
```

#FDR rate setting
###from bidding_pcc_fdr.R, best cutoff is cutoff_pcc or 0.868823 PCC
output object: summaryfile_psm_for_testing3_pcc
```{r}
summaryfile_psm_for_testing3_pcc %>% 
  mutate(
    ms2_filter = if_else(PCC > label_pcc_fdr001, 1, 0)
  ) -> summaryfile_psm_for_testing3_pcc

summaryfile_psm_for_testing3_pcc %>% 
  filter(ms2_filter == 1) 
```

#RT Prediction
## Making up training set and test set including GV transformation: gradients,
output object: file_raw_index2, psm_563516
output file: input_rt_training_",i,".tsv; input_rt_testing_",i,".tsv; input_rt_testing_gvtest_",i,".tsv; rt_training_count_renewal.tsv
```{r}
readRDS(file = "./export/psm_563516.rds") -> psm_563516
  
file_raw_index %>% 
  summarize(
    fraction= first(experiment),
    replicate= first(replicate),
    enzyme = first(enzyme),
    .by = set
  ) %>% 
  bind_cols(
    tibble(
      left_time = c(15,15,10,10,10,10,10,10,10,10,10,10), ###fix:: min for each training data
      right_time = c(140,140,158,158,158,158,158,158,158,158,158,158) ##fix:: 110 duration!,
    )
  ) -> file_raw_index2

file_raw_index2 %>% 
  mutate(
    file_series = 1:12
  ) -> file_raw_index2

psm_563516 %>% 
  mutate(
    nt_arg = if_else(!is.na(nmod) & P1prime == "R",1L,0L)
  ) -> psm_563516

psm_563516 %>% summarize(
  .by = nt_arg,
  count = n()
)

unique(psm_563516$file_id_series)
for (i in 1:length(unique(psm_563516$file_id_series))){
  psm_563516 %>% 
    filter(file_id_series == unique(psm_563516$file_id_series)[i]) %>% 
    dplyr::rename(
      spec_idx = index 
    ) %>% 
    select(
      strip_seq,spec_idx,mods,mod_sites,nAA,nce,instrument,rt_norm,left_time,right_time,nt_arg
    ) %>% 
    dplyr::rename(
      sequence = strip_seq
    ) %>%
    write_tsv(
      paste0(folder_alphapeptdeep,"input_rt_training_",i,".tsv")
    )
}
  
#testset
for (i in 1:length(unique(summaryfile_psm_for_testing3$set))){
  summaryfile_psm_for_testing3 %>% 
    filter(set == unique(summaryfile_psm_for_testing3$set)[i]) %>% 
    dplyr::rename(
      spec_idx = index 
    ) %>% 
    select(
      sequence,spec_idx,irt,mods,mod_sites,nAA,nce,instrument,rt_norm
    ) %>%
    mutate(
      state = "genuine"
    ) %>% 
    bind_rows(
      summaryfile_psm_for_training3 %>% 
        filter(set == unique(summaryfile_psm_for_training3$set)[i]) %>% 
        dplyr::rename(
          spec_idx = index 
        ) %>% 
        select(
          Sequence,spec_idx,irt,mods,mod_sites,nAA,nce,instrument,rt_norm
        ) %>% 
        dplyr::rename(
          sequence = Sequence
        ) %>%
        mutate(
          state = "dummy"
        )
    ) %>% 
    write_tsv(
      paste0(folder_alphapeptdeep,"input_rt_testing_",i,".tsv")
    )
}
  
##GV testset
summaryfile_psm_for_testing3_rt_test_gv
for (i in 1:length(unique(summaryfile_psm_for_testing3_rt_test_gv$set))){
  summaryfile_psm_for_testing3_rt_test_gv %>% 
    filter(set == unique(summaryfile_psm_for_testing3_rt_test_gv$set)[i]) %>% 
    mutate(
      sequence = paste0("GV",Sequence)
    ) %>% 
    mutate(
      nAA = nAA+1
    ) %>% 
    dplyr::rename(
      spec_idx = index 
    ) %>% 
    select(
      sequence,spec_idx,irt,mods,gv_mod_sites,nAA,nce,instrument,rt_norm
    ) %>%
    rename(mod_sites = gv_mod_sites) %>% 
    mutate(
      state = "genuine"
    ) %>% 
    bind_rows(
      summaryfile_psm_for_training3 %>% 
        filter(set == unique(summaryfile_psm_for_training3$set)[i]) %>% 
        dplyr::rename(
          spec_idx = index 
        ) %>% 
        select(
          Sequence,spec_idx,irt,mods,mod_sites,nAA,nce,instrument,rt_norm
        ) %>% 
        dplyr::rename(
          sequence = Sequence
        ) %>%
        mutate(
          state = "dummy"
        )
    ) %>% 
    write_tsv(
      paste0(folder_alphapeptdeep,"input_rt_testing_gvtest_",i,".tsv")
    )
}

psm_563516 %>% 
  mutate(
    nt_arg = as.character(nt_arg)
  ) %>% 
  summarize(
    count = n(),
    experiment=dplyr::first(fraction),
    enzyme=dplyr::first(enzyme),
    replicate = first(replicate),
    .by = c(file_id_series,nt_arg)
  ) %>% write_tsv("./figures/rt/rt_training_count_renewal.tsv")
```

## APD RT Output handling: Reading apd prediction rt output, Linear model fitting, R2, MAE, t95
output object: output_prediction_rt_train_result, output_prediction_rt_test_result, summary_rtprediction
output file: rt_t95.tsv, summary_rtprediction.tsv
```{r}
folder_alphapeptdeep
i=1
output_prediction_rt_train_result <- tibble()
output_prediction_rt_test_result <- tibble()
for (i in 1:12){
  output_prediction_rt_training <- read_tsv(
    paste0(folder_alphapeptdeep,"output_rt_training_",i,".tsv")
  )[,-1] %>% 
    arrange(rt_norm) %>% 
    mutate(file_series= i) %>% 
    filter(nt_arg == 1)
  
  output_prediction_rt_test <- read_tsv(
    paste0(folder_alphapeptdeep,"output_rt_testing_",i,".tsv")
  )[,-1] %>% 
    arrange(rt_norm) %>%
    filter(
      state == "genuine"
    ) %>% 
    mutate(file_series = i)
  
  fit_rt_training <- lm(rt_norm ~ rt_pred, data =output_prediction_rt_training)
  
  output_prediction_rt_training %>%
    bind_cols(
      predict(fit_rt_training, interval = "prediction", level =0.95, newdata = output_prediction_rt_training)
    )->output_prediction_rt_training
  
  
  output_prediction_rt_test %>% 
    bind_cols(
      predict(fit_rt_training, interval = "prediction", level =0.95, newdata = output_prediction_rt_test)
    )->output_prediction_rt_test
  
  
  output_prediction_rt_train_result %>% 
    bind_rows(
      output_prediction_rt_training
    ) -> output_prediction_rt_train_result
  
  output_prediction_rt_test_result %>% 
    bind_rows(
      output_prediction_rt_test
    ) -> output_prediction_rt_test_result
}
output_prediction_rt_train_result %>% 
  arrange(
    spec_idx
  ) ->output_prediction_rt_train_result

output_prediction_rt_test_result %>% 
  arrange(
    spec_idx
  ) ->output_prediction_rt_test_result

output_prediction_rt_test_result %>% 
  mutate(
    rt_test = if_else(rt_norm > lwr & rt_norm < upr, 1, 0)
  ) ->output_prediction_rt_test_result

output_prediction_rt_train_result %>% 
  left_join(
    file_raw_index2 %>% select(-c(left_time,right_time)),
    join_by(file_series)
  ) -> output_prediction_rt_train_result

output_prediction_rt_train_result %>% 
  mutate(
    rt_observed = rt_norm*(right_time-left_time)+left_time,
    rt_predicted = rt_pred*(right_time-left_time)+left_time,
    rt_fit = fit*(right_time-left_time)+left_time,
    rt_lwr = lwr*(right_time-left_time)+left_time,
    rt_upr = upr*(right_time-left_time)+left_time
  ) -> output_prediction_rt_train_result

output_prediction_rt_test_result %>% 
  left_join(
    file_raw_index2,
    join_by(file_series)
  ) ->output_prediction_rt_test_result

output_prediction_rt_test_result %>% 
  mutate(
    rt_observed = rt_norm*(right_time-left_time)+left_time,
    rt_predicted = rt_pred*(right_time-left_time)+left_time,
    rt_fit = fit*(right_time-left_time)+left_time,
    rt_lwr = lwr*(right_time-left_time)+left_time,
    rt_upr = upr*(right_time-left_time)+left_time
  ) ->output_prediction_rt_test_result


output_prediction_rt_train_result
output_prediction_rt_test_result


##R, MAE, T90
{
  
  output_prediction_rt_train_result 
  output_prediction_rt_test_result 
  
  
  output_prediction_rt_train_result %>% 
    filter(file_series==1)
  
  fit_rt_training <- lm(
    rt_observed~ rt_predicted, 
    data =output_prediction_rt_train_result %>% 
      filter(file_series==1))
  
  fit_rt_training %>% tidy()
  
  output_prediction_rt_train_result %>% 
    mutate(t95=rt_upr-rt_lwr) %>% 
    summarise(
      .by = c(set,file_series),
      t95_mean = mean(t95)
    ) -> summary_rtprediction_t95
  summary_rtprediction_t95 %>% write_tsv(
    "./figures/rt/rt_t95.tsv"
  )
  
  summary_rtprediction <- tibble()
  for (i in 1L:12L){
    summary_rtprediction %>% 
      bind_rows(
        output_prediction_rt_train_result %>% 
          filter(file_series==i) %>% 
          metrics(
            truth = rt_observed, estimate = rt_predicted
          ) %>% 
          mutate(
            file_series =i
          )
      )->summary_rtprediction
  }
  summary_rtprediction %>% write_tsv("./figures/rt/summary_rtprediction.tsv")
  
  output_prediction_rt_train_result %>% 
    filter(file_series==i) %>% 
    metrics(
      truth = rt_observed, estimate = rt_predicted
    ) %>% 
    mutate(
      file_series =i
    )
  
}
```

## APD RT: Result of GV transformation 
output object: output_prediction_rt_gvtest_result
output file: output_rt_testing_gvtest_",i,".tsv
```{r}
output_prediction_rt_gvtest_result <- tibble()
  for (i in 1:12){
    bind_rows(
      output_prediction_rt_gvtest_result,
      read_tsv(
        paste0(folder_alphapeptdeep,"output_rt_testing_gvtest_",i,".tsv")
      )[,-1] %>% 
        arrange(rt_norm) %>%
        filter(
          state == "genuine"
        ) %>% 
        mutate(file_series = i)
    )->output_prediction_rt_gvtest_result
      
  }
  
  output_prediction_rt_gvtest_result %>% 
    left_join(
      output_prediction_rt_test_result %>% select(spec_idx,rt_pred) %>% 
        rename(rt_pred_original = rt_pred),
      join_by(
        spec_idx
      )
    )-> output_prediction_rt_gvtest_result
```

## APD RT: merge summaryfile_psm_for_testing_pcc+rt_prediction+reposition_arg_no_dups 
output object: summaryfile_psm_for_testing3_pcc_rt
output file: summaryfile_psm_for_testing3_pcc_rt_231201.tsv
```{r}
output_prediction_rt_test_result
  
  summaryfile_psm_for_testing3_pcc %>% colnames()
  summaryfile_psm_for_testing3_pcc %>% 
    left_join(
      output_prediction_rt_test_result %>% select(spec_idx,rt_pred,fit,lwr,upr,rt_test),
      join_by(
        index == spec_idx
      )
    ) %>% 
    left_join(
      dbtable %>% rename(prot_seq_master=sequence) %>% select(accession,prot_seq_master),
      join_by(
        Accessions_Single == accession
      )
    ) %>% 
    rename(accession_master = Accessions_Single) %>% 
    mutate(
      position_master = str_locate(prot_seq_master,Sequence)[,"start"]
    ) %>% mutate(
      prot_pos_master = paste0(accession_master,"|",position_master)
    ) %>% 
    left_join(
      reposition_arg_no_dups %>%
        mutate(
          prot_name = str_extract(protein,"(?<=\\|)[A-Z0-9]+\\_HUMAN")
        ) %>% 
        select(seq,gene,prot_name,accession,position,p5p1,reviewed,under100),
      join_by(
        Sequence == seq
      )
    ) %>% 
    mutate(
      p1 = str_sub(p5p1,start=5,end=5)
    ) %>% 
    mutate(
      p2 = str_sub(p5p1,start=4,end=5)
    ) %>% 
    mutate(
      p3 = str_sub(p5p1,start=3,end=5)
    ) %>%
    mutate(
      prot_pos_reposition = paste0(gene,"|",accession,"|",prot_name,"|",position)
    ) %>% 
    select(-prot_seq_master)-> summaryfile_psm_for_testing3_pcc_rt
  
  summaryfile_psm_for_testing3_pcc_rt %>% 
    relocate(
      rt_norm, .before = rt_pred
    ) -> summaryfile_psm_for_testing3_pcc_rt
  
  summaryfile_psm_for_testing3_pcc_rt %>% write_tsv("./export/summaryfile_psm_for_testing3_pcc_rt_231201.tsv")
```

#MET integration
output object: summaryfile_psm_for_testing3_pcc_rt_hfsm
```{r}
  summaryfile_psm_for_testing3_pcc_rt %>% 
    bind_cols(
      file_index_arg6_ttest %>% 
        select(sequence_for_fragspec:b_y_ttest)
    ) -> summaryfile_psm_for_testing3_pcc_rt_hfsm
  summaryfile_psm_for_testing3_pcc_rt_hfsm %>% 
    mutate(b_y_ttest = replace_na(b_y_ttest,0)) -> summaryfile_psm_for_testing3_pcc_rt_hfsm
```

#Validation
##Data Preparation
output object: summaryfile_psm_for_testing3_pcc_rt_hfsm2, arginylome_validation_matrix0, arginylome_validation_matrix1, arginylome_validation_matrix2
```{r}

##finalcheck
summaryfile_psm_for_testing3_pcc_rt_hfsm %>%
  mutate(
    pcc_check = if_else(PCC>cutoff_pcc,1,0),###PCC cutoff
    rt_check = rt_test,
    b_y_ttest_check = if_else(b_y_ttest>=0.05,1,0),
    #diagnostic_ion_check = if_else(!is.na(diagnostic_ion_int_relative),1,0),
    p2gv_check = if_else(p2 == "GV" | p2 == "VG",1,0),
    p1r_check = if_else(p1 == "R",1,0),
  ) -> summaryfile_psm_for_testing3_pcc_rt_hfsm

summaryfile_psm_for_testing3_pcc_rt_hfsm %>% 
  write_tsv("./export/summaryfile_psm_for_testing3_pcc_rt_hfsm_231201.tsv")

summaryfile_psm_for_testing3_pcc_rt_hfsm %>% 
  select(prot_pos_master,prot_pos_reposition,sequence,pcc_check,rt_check,b_y_ttest_check,p2gv_check,p1r_check) -> arginylome_validation_matrix0

summaryfile_psm_for_testing3_pcc_rt_hfsm %>%
  mutate(
    prot_pos_new = paste0(accession,"|",position)
  ) %>%
  left_join(
    output_cleavage %>% 
      rename(
        cleavage_name = name,
        cleavage_score = score,
        cleavage_type = type
      ) %>% 
      distinct(value,.keep_all=TRUE), ### 
    join_by(
      prot_pos_master == value
    )
  ) -> summaryfile_psm_for_testing3_pcc_rt_hfsm2

summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  mutate(
    dl_score = pcc_check+rt_check+b_y_ttest_check
  )-> summaryfile_psm_for_testing3_pcc_rt_hfsm2

summaryfile_psm_for_testing3_pcc_rt_hfsm2 %>% 
  select(prot_pos_master,prot_pos_reposition,sequence,pcc_check,rt_check,b_y_ttest_check,p2gv_check,p1r_check) -> arginylome_validation_matrix0

arginylome_validation_matrix0 %>% 
  mutate(
    score_sum = pcc_check+rt_check+b_y_ttest_check#+diagnostic_ion_check
  ) %>% 
  arrange(desc(score_sum)) %>% 
  distinct(prot_pos_master,.keep_all = TRUE) -> arginylome_validation_matrix0

arginylome_validation_matrix0 %>% 
  dplyr::filter(p1r_check == 0) -> arginylome_validation_matrix1

arginylome_validation_matrix1 %>% 
  dplyr::filter(p2gv_check !=1) -> arginylome_validation_matrix2

```

